\prayersection{For Times of Birth}
\prayertitle{For Babies About to Be Born}
\label{prayer:babies_about_to_be_born}
Heavenly Father, from the moment these children were conceived, You knew their names.
In the silent first hours of their lives, as cells divided and their living flesh quickened, Your Love breathed deep within and they began to grow in Your Image and Likeness.
May our prayers be accompanied by choirs of angels as we await their births.
We ask this through Your Child Who was formed in the Virgin's womb and Who lived and died for us, Lord, forever and ever. Amen.

\prayertitle{Thanksgiving for a Newborn or Newly Adopted Infant}
\label{prayer:thanksgiving_newborn}
God, our Creator, cherish this child.
Jesus, our Savior; protect him/her.
Holy Spirit, our comforter, strengthen him/her.

Source of all blessings, protector of infants, look with favor on this child, \insertname.

Hold him/her gently in your hands.
When he/she is reborn of water and the Holy Spirit, bring him/her into the Church, there to share in your kingdom and with us to bless Your Name forever.
We ask this through Christ our Lord.

\response Amen.

\instruction{The parents trace the sign of the cross on the child's forehead.}

\insertname, may the Lord Jesus, Who loved children, bless you and keep you in His love, now and forever.

\response Amen.

\prayertitle{Prayer on Bringing a Child into the Home}
\label{prayer:bringing_child_into_home}
Good Lord, You have tenderly loved us, and given us this home and good friends.
May we make a true home for this child, where he/she will learn trust in us and in You.
May his/her brothers and sisters rejoice in their own growing up as they help to care for this child.
We ask this through Christ our Lord.

\response Amen.