\prayersection{Blessings}
\note{Blessings for children may be said by the parent at various times, such as when a child is going to play or to school, but especially when the child is going to bed each night.
The parent makes the sign of the cross on the child's forehead or heart and says the blessing.}

\prayertitle{Blessing of a Child}
\label{prayer:blessing_child}
May almighty God, Father, Son, and Holy Spirit, bless you, my child, for time and eternity, and may this blessing remain forever with you.

\prayertitle{Blessing of the Patriarchs}
\label{prayer:blessing_patriarchs}
\note{From Numbers 6:24-26.}
The Lord bless you and keep you;
the Lord make His face to shine upon you, and be gracious to you;
the Lord lift up His countenance upon you, and give you peace.

\prayertitle{Blessing on a Child's Birthday}
\label{prayer:blessing_child_birthday}
\note{From Jeremiah 1:5.}
The Lord said to Jeremiah:
Before I formed you in the womb I knew you, before you were born I dedicated you.

May God, in whose presence our ancestors walked, bless you.

\response Amen.

May God, Who has been your shepherd from birth until now, keep you.

\response Amen.

May God, Who saves you from all harm, give you peace.

\response Amen.
\newpage
\prayertitle{House Blessing for Epiphany}
\note{Gather at the main door into the house and use blessed chalk to inscribe the year along with the initials of the Magi (Caspar, Melchior, and Balthasar) above the door(s) into the house. The format is ``20 + CMB + xy'', where ``xy'' is the year number. The numbers ask the Lord's blessing on the year and the crosses ask the Lord's blessing on those coming and going through the door. After making the inscription read the following blessing.}
Heavenly Father, bless this home, all who dwell here and all who visit here.
As the Magi found Christ on their arrival, may all our guests see Christ in us and in the life we share.
Be our protector as we leave this house and our comfort and joy as we return.
We ask this through Christ our Lord, the Word made flesh, Who lives forever and ever. Amen.

\response (All pray the Our Father.)

\prayertitle{Travel Blessing}
\label{prayer:travel_blessing}
\note{Based on Tobit's blessing of Tobias (Tobit 5).}
May God in heaven bring you safely there and return you in good health;
and may His angel accompany you for your safety.

\prayertitle{Blessing of Parents Before the Birth of Their Child}
\label{prayer:parents_before_birth_of_child}
Gracious Father, Your Word, spoken in love, created the human family and, in the fullness of time, Your Son, conceived in love, restored it to Your friendship.
Hear the prayers of parents awaiting the birth of a child, calm their fears when they are anxious.
Watch over and support these parents and bring their child into this world safely and in good health, so that as members of Your family they may praise You and glorify You through Your Son, our Lord Jesus Christ, now and forever.
Amen.

\prayertitle{Blessing of a Mother Before Childbirth}
\label{prayer:mother_before_childbirth}
God has brought gladness and light to the world through the Virgin Mary's delivery of her child.
May Christ fill your heart with His holy joy and keep you and your baby safe from harm. 
In the Name of the Father, and of the Son, and of the Holy Spirit.

\newpage