\prayersection{Prayers of the Saints and Religious}
\prayertitle{The Universal Prayer (Pope Clement XI)}
% My Prayer Book, pp. 281-283
Lord, I believe in You: increase my faith.
I  trust in You: strengthen my trust.
I love You: let me love You more and more.
I am sorry for my sins: deepen my sorrow.

I worship You as my first beginning, I long for You as my last end, I praise You as my constant helper, and call on You as my loving protector.

Guide me by Your Wisdom,
correct me with Your Justice,
comfort me with Your Mercy,
protect me with Your Power.

I offer You, Lord, my thoughts: to be fixed on You;
my words: to have You for their theme;
my actions: to reflect my love for You;
my sufferings: to be endured for Your greater Glory.

I want to do what You ask of me:
in the way You ask,
for as long as You ask,
because You ask it.

Lord, enlighten my understanding,
strengthen my will,
purify my heart,
and make me holy.

Help me to repent of my past sins and to resist temptation in the future.
Help me to rise above my human weaknesses and to grow stronger as a Christian.

Let me love You, my Lord and my God, and see myself as I really am:
a pilgrim in this world,
a Christian called to respect and love all whose lives I touch,
those in authority over me or those under my authority,
my friends and my enemies.

Help me to conquer anger with gentleness,
greed by generosity,
apathy by favor.
Help me to forget myself and reach out toward others.
Make me prudent in planning, courageous in taking risks.
Make me patient in suffering, unassuming in prosperity.

Keep me, Lord, attentive at prayer,
temperate in food and drink,
diligent in my work,
firm in my good intentions.

Let my conscience be clear,
my conduct without fault,
my speech blameless,
my life well-ordered.
Put me on guard against my human weaknesses.
Let me cherish Your Love for me,
keep Your Law,
and come at last to Your salvation.

Teach me to realize that this world is passing,
that my true future is the happiness of heaven,
that life on earth is short,
and the life to come is eternal.

Help me to prepare for death with a proper fear of judgment, but a greater trust in Your Goodness.
Lead me safely through death to the endless joy of heaven.

Grant this through Christ our Lord. Amen.

\prayertitle{Thomas Merton}
% https://www.goodreads.com/quotes/80913-my-lord-god-i-have-no-idea-where-i-am
My Lord God, I have no idea where I am going. 
I do not see the road ahead of me.
I cannot know for certain where it will end.
Nor do I really know myself,  and the fact that I think that I am following Your Will does not mean that I am actually doing so.

But I believe that the desire to please You does in fact please You. 
And I hope I have that desire in all that I am doing. 
I hope that I will never do anything apart from that desire. 
And I know that if I do this, You will lead me by the right road though I may know nothing about it.

Therefore will I trust You always though I may seem to be lost and in the shadow of death.
I will not fear, for You are ever with me, and You will never leave me to face my perils alone. 
Amen.  

\prayertitle{St. Th\'{e}r\`{e}se of Lisieux}
% My Prayer Book, p. 280
O my God, I ask of You for myself and for those whom I hold dear, the grace to fulfill perfectly Your holy Will, to accept for love of You the joys and sorrows of this passing life, so that we may one day be united in Heaven for all eternity.

\prayertitle{St. Francis of Assisi}
% My Prayer Book, p. 275
Lord, make me an instrument of Your Peace.
Where there is hatred, let me sow love;
where there is injury, pardon;
where there is doubt, faith;
where there is despair, hope;
where there is darkness, light;
and where there is sadness, joy.

O Divine Master, grant that I may not so much seek to be consoled as to console, to be understood as to understand, to be loved as to love.

For it is in giving that we receive, it is in pardoning that we are pardoned, and it is in dying that we are born to eternal life.

\prayertitle{St. Gemma Galgani}
% http://www.stgemmagalgani.com/2008/09/prayer-of-st-gemma-galgani-to-obtain.html
O my crucified God, behold me at Your Feet;
do not cast me out, now that I appear before You as a sinner.
I have offended You exceedingly in the past, my Jesus, but it shall be so no longer.
Before You, O Lord, I place all my sins;
I have now considered Your own sufferings and see how great is the worth of that Precious Blood that flows from Your Veins.
O my God, at this hour close Your Eyes to my want of merit, and since You have been pleased to die for my sins, grant me forgiveness for them all, that I may no longer feel the burden of my sins, for this burden, dear Jesus, oppresses me beyond measure.
Assist me, my Jesus, for I desire to become good whatsoever it may cost;
take away, destroy, utterly root out all that You find in me contrary to Your holy Will.
At the same time, I pray to You, Lord Jesus, to enlighten me that I may be able to walk in Your holy Light.
Amen.

\prayertitle{St. Gemma Galgani (to obtain a desired grace)}
% http://www.stgemmagalgani.com/2008/09/prayer-of-st-gemma-galgani-to-obtain.html
Behold me at Your most holy Feet, O dear Jesus, to manifest to You my gratitude for the continual favors which You have bestowed upon me, and still wish to bestow upon me.
As many times as I have invoked You, O Jesus, You have made me content;
I have often had recourse to You and You have always consoled me.
How shall I express myself to You, dear Jesus?
I thank You!
Yet one more grace I desire of You, O my God, if it would be pleasing to You: \ldots


If You were not omnipotent, I would not make this request.
O Jesus, have pity on me.
May Your most holy Will be done in all things.

\prayertitle{St. Ephrem the Syrian \#1}
% My Prayer Book, p. 279
Have mercy on me:
I am a sinner, I am weak.
Be gracious, O God, to my weakness;
grant strength to me to pray a prayer that will be pleasing to Your Will.

\prayertitle{St. Ephrem the Syrian \#2}
\label{prayer:StEphrem2}
Lord Jesus Christ, King of Kings, You have power over life and death.
You know what is secret and hidden, and neither our thoughts nor our feelings are concealed from You.
Cure me of duplicity;
I have done evil before You.
Now my life declines from day to day and my sins increase.
O Lord, God of souls and bodies, You know the extreme frailty of
my soul and my flesh.
Grant me strength in my weakness, O Lord, and sustain me in my misery.
Give me a grateful soul that I may never cease to recall Your benefits, O Lord most bountiful.
Be not mindful of my many sins, but forgive me all my misdeeds.
O Lord, disdain not my prayer --- the prayer of a wretched sinner;
sustain me with Your Grace until the end, that it may protect me as in the past.
It is Your Grace which has taught me wisdom;
blessed are they who follow her ways, for they shall receive the crown of glory.
In spite of my unworthiness, I praise You and I glorify You, O Lord, for Your Mercy to me is without limit.
You have been my help and my protection.
May the Name of Your Majesty be praised forever. 
To You, our God, be glory.
Amen.

\prayertitle{St. Augustine}
% My Prayer Book, p. 276
Breathe in me, Holy Spirit, that all my thoughts may be holy.
Act in me, Holy Spirit, that my work too may be holy.
Draw my heart, Holy Spirit, that I may love only what is holy.
Strengthen me, Holy Spirit, to defend all that is holy.
Guard me, Holy Spirit, that I may always be holy.

\prayertitle{St. Thomas Aquinas}
Grant me, O Lord my God,
a mind to know You,
a heart to seek You,
wisdom to find You,
conduct pleasing to You,
faithful perseverance in waiting for You,
and a hope of finally embracing You.

\prayertitle{St. Ignatius Loyola}
% My Prayer Book, p. 278
Teach us, good Lord, to serve You as You deserve:
to give and not to count the cost;
to fight and not to heed the wounds;
to toil and not to seek for rest;
to labor and not ask for any reward save that of knowing that we do Your Will.

\prayertitle{Simon Patrick}
% My Prayer Book, p. 279
O Lord, endow me with more contentedness in what is present, and less solicitude about what is future;
with a patient mind to submit to any loss of what I have, or to  any disappointment of what I expect.

\prayertitle{St. Thomas More}
% My Prayer Book, pp]. 278-279
Good Lord, give me the grace so to spend my life, that when the day of my death shall come, though I feel pain in my body, I may feel comfort in soul;
and with faithful hope of Your Mercy, in due love towards You and charity towards the world, I may, through Your Grace, part hence into Your Glory.

\prayertitle{St. John Baptist de La Salle}
% My Prayer Book, p. 277
O my God, I beg of You to grant me peace with my neighbor, for I cannot enjoy Your favor if I do not live in union with my brothers and sisters.
I can preserve this union by mildness and patience.
Give me, then, I beseech You, these two virtues, and grant that I may always speak and act kindly to all;
that I may suffer patiently for love of You whatever wrongs, injuries, or insults may be done me;
that not only I may not be angered or displeased with anything but that I may patiently suffer all that happens to me from others.

\prayertitle{Sister Consolata Betrone}
% https://en.wikipedia.org/wiki/Consolata_Betrone
Jesus, Mary, I love you: Save souls.

\prayertitle{St. Elizabeth Ann Seton}
% My Prayer Book, p. 276
From eternity to eternity, You are my God.
All shall perish and pass away, but You remain forever.

\prayertitle{Columba Marmion}
% My Prayer Book, p. 278
Behold me, O my God, I give myself to You, to Your good pleasure.
Because I love You, I will give You the homage of submitting my whole being to Your Will, whatever it may be.

\prayertitle{St. Francis de Sales}
% My Prayer Book, p. 277
O God, You are my God, in You will I hope!
You will be my help and my refuge.
I shall not fear, for not only are You with me but You are in me and I in You.

\prayertitle{Bl. Jan Van Ruysbroeck}
% My Prayer Book, p. 276
Lord, I am willing to be poor in all those things of which I have been deprived as I am ready to be rich, O Lord, if it be Your Will and to Your Glory;
not my will according to nature, O Lord, but Your Will and my will according to spirit be done.

\newpage