\prayersection{For the Church}
\prayertitle{For the Church Under Persecution}
% My Prayer Book, p. 259
Father, in the mystery of Your Providence the Church was to share in the sufferings of Christ Your Son.
Give those who suffer persecution for their faith a share also in the Patience and Love of Your Son, that they may be true and faithful witnesses to His promise of resurrection and eternal life.
Amen.

\prayertitle{For the Church}
% My Prayer Book, p. 258
Father, in the new covenant instituted by Christ Your Son, You gather Your people in the unity of Your Spirit from all the nations of the earth.
Keep Your Church faithful to her mission as a leaven in the world, renewing all peoples in Christ and transforming them into Your own family.
Amen.

\prayertitle{For our Parish}
O God, You have made us the Church of Your dear Son.
Make our parish a family of one heart and mind in love toward You.
Grant that our common life and world may be an example to all about us.
Guide our pastor and his assistants in their work.
Acknowledge the intercessions of our patron; and keep us secure in Your Love.
Amen.

\prayertitle{For the Pope}
% My Prayer Book, p. 258
Father, as successor to the Apostle Peter You have chosen Your servant \insertname\ to be the vicar of Christ on earth and shepherd of the whole flock.
May he strengthen his brothers, and may the whole Church be in communion with him in the bond of unity, love, and peace, that all men may receive from You, the shepherd and bishop of their souls, truth and eternal life.
Amen.
\newpage
\prayertitle{For the Bishop}
% My Prayer Book, p. 260
God our Father, You have entrusted to Your servant \insertname, as a successor to the Apostles, the care of the diocese of \insertname.
Give him Your Spirit of wisdom and courage, of understanding and love.
Keep him faithful to his mission that he may build up Your Church, the universal sacrament of salvation.
Amen.

\prayertitle{For Priests}
% http://www.catholicdigest.com/faith/spirituality/five-prayers-for-priests/
\note{By St. Th\'{e}r\`{e}se of Lisieux}
O Jesus, I pray for Your faithful and fervent priests;
for Your unfaithful and tepid priests;
for Your priests laboring at home or abroad in distant mission fields;
for Your tempted priests;
for Your lonely and desolate priests;
for Your young priests;
for Your dying priests;
for the souls of Your priests in purgatory.

But above all, I recommend to You the priests dearest to me:
the priest who baptized me;
the priests who absolved me from my sins;
the priests at whose Masses I assisted and who gave me Your Body and Blood in Holy Communion;
the priests who taught and instructed me;
all the priests to whom I am indebted in any other way (especially\ldots).

O Jesus, keep them all close to Your heart,
and bless them abundantly in time and in eternity.

Amen.

\prayertitle{For Priests \#2}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-priests.cfm
Gracious and loving God, we thank You for the gift of our priests.
Through them, we experience Your Presence in the sacraments.

Help our priests to be strong in their vocation.
Set their souls on fire with love for Your people.

Grant them the wisdom, understanding, and strength they need to follow in the footsteps of Jesus.
Inspire them with the vision of Your Kingdom.

Give them the words they need to spread the Gospel.
Allow them to experience joy in their ministry.

Help them to become instruments of Your divine Grace.

We ask this through Jesus Christ, Who lives and reigns as our Eternal Priest.
Amen.

\prayertitle{For Priests \#3}
% My Prayer Book, p. 260
Father, You appointed Your only Son as the eternal high priest.
Grant that those He has chosen to be ministers of word and sacrament may be faithful in their ministry until the day of His coming.
Amen.

\prayertitle{For Religious}
% My Prayer Book, p. 261
Father, every good intention has its origin and fulfillment in You.
Guide Your people along the path of salvation and look kindly on those who have left all things to follow Christ in chastity, poverty, and obedience, and to consecrate themselves to You.
In their service to You, Father, and to all their brothers and sisters, may they give faithful witness to Christ.
Amen.

\prayertitle{For Vocations}
% http://www.usccb.org/beliefs-and-teachings/vocations/upload/Prayer-for-Vocations-Card-2014.pdf
God our Father, we thank You for calling men and women to serve in Your Son's Kingdom as priests, deacons, and consecrated persons.
Send Your Holy Spirit to help others to respond generously and courageously to Your call.
May our community of faith support vocations of sacrificial love in our youth and young adults.
Through our Lord Jesus Christ, Who lives and reigns with You in the unity of the Holy
Spirit, one God, forever and ever.
Amen.

\newpage