\prayersection{Sacrament of Holy Communion}
% My Prayer book, p. 78
\prayertitle{Prayer of St. Thomas Aquinas before Holy Communion}
Almighty and ever-living God, I approach the sacrament of Your only-begotten Son, our Lord Jesus Christ.

I come sick to the doctor of life, unclean to the foundation of mercy, blind to the radiance of eternal light, and poor and needy to the Lord of heaven and earth.

Lord, in Your great Generosity, heal my sickness, wash away my defilement, enlighten my blindness, enrich my poverty, and clothe my nakedness.

May I receive the bread of angels, the King of Kings and Lord of Lords, with humble reverence, with the purity and faith, the repentance and love, and the determined purpose that will help to bring me to salvation.

May I receive the sacrament of the Lord's Body and Blood, and its reality and power.

Kind God, may I receive the body of Your only begotten Son, our Lord Jesus Christ, born from the womb of the Virgin Mary, and so be received into His mystical body and numbered among His members.

Loving Father, as on my earthly pilgrimage I now receive Your beloved Son under the veil of a sacrament, may I one day see Him face to face in glory, Who lives and reigns with You for ever.
Amen.

% My Prayer book, p. 80
%\begin{minipage}{\textwidth}
\prayertitle{Prayer of St. Ambrose before Holy Communion}
Lord Jesus Christ, I approach Your banquet table in fear and trembling, for I am a sinner, and dare not rely on my own worth but only on Your Goodness and Mercy.

I am defiled by many sins in body and soul, and by my unguarded thoughts and words.

Gracious God of majesty and awe, I seek Your Protection, I look for Your healing.

Poor troubled sinner that I am, I appeal to You, the fountain of all mercy.

I cannot bear Your Judgment, but I trust in Your salvation.

Lord, I show my wounds to You and uncover my shame before You.

I know my sins are many and great, and they fill me with fear, but I hope in Your Mercies, for they cannot be numbered.

Lord Jesus Christ, eternal King, God and man, crucified for mankind, look upon me with mercy and hear my prayer, for I trust in You.

Have mercy on me, full of sorrow and sin, for the depth of Your Compassion never ends.

Praise to You, saving sacrifice, offered on the wood of the cross for me and for all mankind.

Praise to the noble and precious Blood, flowing from the Wounds of my crucified Lord Jesus Christ and washing away the sins of the whole world.

Remember, Lord, Your creature, whom You have redeemed with Your Blood.

I repent my sins, and I long to put right what I have done.

Merciful Father, take away all my offenses and sins;
purify me in body and soul, and make me worthy to taste the holy of holies.

May Your Body and Blood, which I intend to receive, although I am unworthy, be for me the remission of my sins, the washing away of my guilt, the end of my evil thoughts, and the rebirth of my better instincts.

May it incite me to do the works pleasing to You and profitable to my health in body and soul, and be a firm defense against the wiles of my enemies.
Amen.

\prayertitle{Prayer of St. John Chrysostom before Holy Communion}
% https://orthodoxprayer.org/Communion_Prayers.html
Lord, Jesus Christ my God, forgive the faults and sins which I, Your unworthy servant, have committed from my youth to this day and hour, whether knowingly or in ignorance, whether by words, deeds, intentions, or thoughts, and whether by habit or through any of my senses.
By the prayers of Your pure and Virgin Mother, make me worthy without condemnation to receive Your precious, immortal, and life-giving Mysteries for the forgiveness of sins and eternal life.
May the Eucharist sanctify, enlighten, strengthen, and heal my soul and body and thus destroy my evil thoughts, intentions, and prejudices.
For Yours, Christ our God, is the Kingdom, the power, the glory, the honor, and worship with the Father and the Holy Spirit, now and forever and ever.
Amen.

\indulgencedprayertitle{\foreign{Anima Christi}}
\linkednote{grant8}{A partial indulgence is granted for making an act of thanksgiving after Communion using this prayer.}
Soul of Christ, sanctify me.
Body of Christ, save me.
Blood of Christ, inebriate me.
Water from the Side of Christ, wash me.
Passion of Christ, strengthen me.
O good Jesus, hear me.
Within Thy Wounds hide me.
Suffer me not to be separated from Thee.
From the malicious enemy defend me.
In the hour of my death call me.
And bid me come to Thee,
that with Thy saints I may praise Thee for ever and ever.
Amen.

\indulgencedprayertitle{\foreign{En ego, O bone et dulcissime Iesu}}
\linkednote{grant8}{A plenary indulgence is granted for devoutly reciting this prayer after Communion on any of the Fridays in Lent. A partial indulgence is granted for making an act of thanksgiving after Communion using this prayer.}
Behold, O kind and most sweet Jesus, I cast myself upon my knees in Thy Sight, and with the most fervent desire of my soul, I pray and beseech Thee that Thou wouldst impress upon my heart lively sentiments of faith, hope, and charity, with true contrition for my sins and a firm purpose of amendment;
while with deep affection and grief of soul I ponder within myself and mentally contemplate Thy five Wounds, having before my eyes the words which David the prophet put on Thy Lips concerning Thee:
``My Hands and My Feet they have pierced, they have numbered all My Bones.''

% My Prayer book, p. 86
\prayertitle{Prayer of St. Thomas Aquinas after Holy Communion}
Lord, Father all-powerful and ever-living God,

I thank You, for even though I am a sinner, Your unprofitable servant, not because of my worth but in the Kindness of Your Mercy, You have fed me with the precious Body and Blood of Your Son, our Lord Jesus Christ.

I pray that this holy communion may not bring me condemnation and punishment but forgiveness and salvation.

May it be a helmet of faith and a shield of good will.

May it purify me from evil ways and put an end to my evil passions.

May it bring me charity and patience, humility and obedience, and growth in the power to do good.

May it be my strong defense against all my enemies, visible and invisible, and the perfect calming of all my evil impulses, bodily and spiritual.

May it unite me more closely to You, the one true God, and lead me safely through death to everlasting happiness with You.

And I pray that You will lead me, a sinner, to the banquet where You, with Your Son and Holy Spirit, are true and perfect light, total fulfillment, everlasting joy, gladness without end, and perfect happiness to Your saints.

Grant this through Christ our Lord. Amen.

\prayertitle{To our Redeemer after Holy Communion}
% My Prayer Book, p. 84
Jesus, may all that is You flow into me.
May Your Body and Blood be my food and drink.
May Your Passion and death be my strength and life.
Jesus, with You by my side enough has been given.
May the shelter I seek be the shadow of Your cross.
Let me not run from the love which You offer, but hold me safe from the forces of evil.
On each of my dyings shed Your Light and Your Love.
Keep calling to me until that day comes when, with Your saints, I may praise You for ever.
Amen.

\prayertitle{Act of Thanksgiving after Holy Communion}
% My Prayer Book, p. 87-89
From the depths of my heart I thank You, Lord, for Your infinite Kindness in coming to me.
How good You are to me!
With Your most holy Mother and all the angels, I praise Your Mercy and Generosity toward me.
I thank You for nourishing my soul with Your Sacred Body and Precious Blood.
I will try to show my gratitude to You in the Sacrament of Your Love, by loving obedience to Your holy commandments, by fidelity to my duties, by kindness to my neighbor, and by an earnest endeavor to become more like You in my daily conduct.

Grant that I may spend the hours of the day gladly working with You according to Your Will.

May I not lose my enthusiasm in serving You.
May my conversations be occasions of charity.
May I be patient with myself and those around me in the day's disappointments.
May I be mindful of others rather than myself in moments of fatigue and illness.
May I be generous and faithful so that when this day is over I may feel that life is really meaningful and peaceful, for it has been spent in Your loving company.
Amen.

\newpage