\prayersection{For the Deceased}
\linkednote{grant29}{A plenary indulgence, applicable only to the souls in purgatory, is granted on any and each day from November 1 to 8 for devoutly visiting a cemetary and praying, if only mentally, for the departed.
A partial indulgence, applicable only to the souls in purgatory, is granted for devoutly visiting a cemetary and at least mentally praying for the dead.}
\prayertitle{For Departed Loved Ones}
% Laudate app, which cites ``Prayers for Today'', published by Leaflet Missal Co. Also can be found online, e.g. at https://www.catholicdoors.com/prayers/english3/p02468.htm.
Almighty God, Who by the love which You have for men, have willed to take our humanity, to live a life of hard work, to suffer a most cruel Passion, and finally to die on the Cross, I beseech You, by the infinite merits purchased for us with Your Precious Blood, look mercifully on the suffering  which is endured by the holy souls in Purgatory. 
Accept, O merciful God, the prayers which I offer for them, and call them to the glory of Heaven. 
I recommend to You the souls of my relatives, friends, and benefactors, and in a special manner of those to whom I may have been an occasion of sin by my bad example. 
Most Holy Virgin, Mother of Mercy, Comforter of the afflicted, intercede for those souls, that, by your powerful intercession, they may be admitted to enjoy that Kingdom which is prepared for them.

\prayertitle{\foreign{Requiem aeternam}}
\linkednote{grant29}{A partial indulgence, applicable only to the souls in purgatory, is granted for devoutly reciting this prayer.}
Eternal rest grant unto them, O Lord, and let perpetual light shine upon them.
May they rest in peace.

\prayertitle{For a Man Deceased}
% My Prayer Book, p. 267
Incline Your Ear, O Lord, to our prayers in which we humbly pray that You show Your Mercy to the soul of Your servant \insertname, whom You commanded to leave this world.
Place him in the region of peace and light and bid him share the company of Your saints.
Through Christ our Lord. Amen.

\prayertitle{For a Woman Deceased}
% My Prayer Book, p. 267
O Lord, we beg of You, through Your loving Kindness, have mercy on the soul of Your servant \insertname, and now that she is set free from the defilements of this mortal flesh, restore her to her heritage of everlasting salvation.
Through Christ our Lord. Amen.

\indulgencedprayertitle{Prayer for the Faithful Departed}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Byzantine Tradition.}
God of the spirits and of all flesh, Who have destroyed death and annihilated the devil
and given life to Your world, may You Yourself, O Lord, grant to the soul of Your
deceased servant \insertname\ rest in a place of light, a verdant place, a place of freshness, from where suffering, pain, and cries are far removed.
Do You, O good and compassionate God, forgive every fault committed by him in word, work, or thought;
because there is no man who lives and does not sin.
You alone are without sin and Your Justice is justice throughout the ages and Your Word is truth.
Since You, O Christ our God, are the resurrection, the life, and the repose of Your
deceased servant \insertname, we give You glory together with Your un-begotten Father with
Your most holy, good, and vivifying Spirit, now and always and for ever and ever.

\indulgencedprayertitle{Intercession for the Deceased from the Liturgy of St. James}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Syro-Antiochian Tradition.}
Lord, O Lord, God of the pure spirits and of every flesh, be mindful of us all, of those we have remembered and of all we have not remembered and who have left this world with glorious faith.
Give repose to their souls, to their bodies, to their spirits.
Save them from future damnation and make them worthy of the joy, which is in the bosom of Abraham, Isaac, and Jacob, where the light of Your Countenance shines, where pain, anguish, and cries are banished.
Do not impute to them any fault;
do not enter into judgment with Your servants, because no living being is justified in Your Sight and because no man on earth is immune from sin and pure of every filth except for our Lord Jesus Christ, Your Son, through Whom we, too, hope to obtain mercy and the pardon of our sins and of those of our deceased.

Give rest to their souls;
cancel our faults and their faults committed before You willingly or unwillingly, consciously or unconsciously.

Grant them rest.
Forgive, O God, and pardon the voluntary and involuntary sins committed consciously or unconsciously by word, work, or omissions, by secret thoughts or publicly, deliberately or through error and which Your holy Name knows.
Grant us a Christian ending without sin and unite us at the feet of Your elect when You Will, where You Will, and how You Will, without us having to blush for our sins because in this as in all things Your holy and blessed Name, the Name of our Lord Jesus Christ and of the Holy Spirit, be praised and glorified now and for all ages. Amen.

\prayertitle{For the Dead}
\label{prayer:dead}
In Your Hands, O Lord, we humbly entrust our brothers and sisters.
In this life You embraced them with Your tender Love;
deliver them now from every evil and bid them eternal rest.

The old order has passed away:
welcome them into paradise, where there will be no sorrow, no weeping, or pain,
but fullness of peace and joy with Your Son and the Holy Spirit forever and ever.
Amen.

\prayertitle{For Deceased Parents}
O God, Who has commanded us to honor our father and our mother, in Your Mercy have pity on the souls of my father and mother, and forgive them their trespasses, and make me to see them again in the joy of everlasting brightness. Through Christ our Lord. Amen.

\prayertitle{For Mourners}
\label{prayer:mourners}
Lord God, You are attentive to the voice of our pleading.
Let us find in Your Son comfort in our sadness, certainty in our doubt, and courage to live through this hour.
Make our faith strong through Christ our Lord.

Lord, \insertname\ are gone now from this earthly dwelling, and have left behind those who mourn their absence.
Grant that we may hold their memory dear, never bitter for what we have lost
nor in regret for the past, but always in hope of the eternal Kingdom where You will bring us together again.

May the Love of God and the Peace of the Lord Jesus Christ bless and console us and gently wipe every tear from our eyes:
in the Name of the Father, and of the Son, and of the Holy Spirit.
Amen.

\prayertitle{For the Poor Souls in Purgatory}
\label{prayer:poor_souls_purgatory}
My Jesus, by the sorrows You suffered in Your agony in the Garden, in Your scourging and crowning with thorns, in Your journey to Calvary, in Your crucifixion and death, have mercy on the souls in purgatory, and especially on those who are most forsaken;
deliver them from the torments they endure;
call them and admit them to Your most sweet embrace in Paradise, where You live with the Father and the Holy Spirit, one God, for ever and ever.

Merciful Father, hear our prayers and console us, as we renew our faith in Your Son Whom You raised from the dead, strengthen our hope that all our departed brothers and sisters will share in His resurrection, Who lives and reigns with You and the Holy Spirit, one God for ever and ever.
Amen.

\prayertitle{For the Most Neglected and Most in Need in Purgatory}
\label{prayer:most_neglected_purgatory}
Lord, Almighty God, through the Sacred Blood which Your Divine Son shed in the Garden of Gethsemane and at the painful Crowning of Thorns, I ask You to free the souls in Purgatory, in particular those who are most neglected and those in most need of our intercession.
Please do not let them wait any longer in Purgatory, and lead them into Your Glory so that they may praise and glorify You throughout eternity.
Amen.

\prayertitle{For those in Purgatory Closest to the Entrance of Heaven}
\label{prayer:purgatory_closest_heaven}
Lord, Almighty God, through the Sacred Blood which Your Divine Son shed during the cruel Scourging, I ask You to free the Souls in Purgatory, in particular those who stand the closest to the entrance of Your Delight.
Let them begin to praise and glorify You from now throughout eternity.
Amen.

\prayertitle{Prayer at Graveside}
\label{prayer:graveside}
Lord Jesus Christ, by Your own three days in the tomb, You hallowed the graves of all who believe in You and so made the grave a sign of hope that promises resurrection even as it claims our mortal bodies.

Grant that our brother/sister, \insertname, may sleep here in peace until You awaken him/her to glory, for You are the resurrection and the life.
Then he/she will see You face to face and in Your Light will see light and know the splendor of God, for You live and reign forever and ever.
Amen.

\newpage