\prayersection{For Times of Death}
\prayertitle{Prayer for the Terminally Ill}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Lord Jesus Christ, Who suffered and died for our sins that we may live, if during our life we have sinned in word, deed, or thought forgive us in Your Goodness and Love.
All our hope we put in You;
protect your servant \insertname from all evil.
We submit to Your Will and into Your Hands we commend our souls and bodies.
For a Christian end to our lives, peaceful, without shame and suffering, and for a good account before the awesome judgment seat of Christ, we pray to You O Lord.
Bless us, be merciful to us, and grant us life eternal.
Amen.

\prayertitle{For All about to Die}
% http://www.usccb.org/issues-and-action/human-life-and-dignity/assisted-suicide/to-live-each-day/upload/prayer-resources.pdf
Lord Jesus Christ, as You stood by the bed of good Saint Joseph and gently led him home to heaven, so shepherd every soul about to die to a paradise of perfect peace.
Let the tears we shed upon their passing stand witness to our love for them and the depth of our thanksgiving for the gift of their lives and the grace of a good death.
For You are Lord, forever and ever.
Amen.

\prayertitle{Prayer of Commendation}
% http://www.usccb.org/prayer-and-worship/bereavement-and-funerals/prayers-for-death-and-dying.cfm
\note{Said as the time of death approaches.}
Go forth, Christian soul, from this world in the Name of God the almighty Father, Who created you, in the Name of Jesus Christ, Son of the living God, Who suffered for you, in the Name of the Holy Spirit, Who was poured out upon you, go forth, faithful Christian.

May you live in peace this day, may your home be with God in Zion, with Mary, the Virgin Mother of God, with Joseph, and all the Angels and Saints.

\prayertitle{Aspiration of the Dying}
% https://www.ourcatholicprayers.com/aspirations-for-the-dying.html. Also from the Laudate app under ``Aspirations for the Dying''
Good Jesus, give me a deep love for You, that nothing may be too hard for me to bear from You.

You know Lord, that I am all weakness; teach me to bear my cross.
Bear it for me, bear it in me.

O Good Jesus, my God and my All, keep me ever near You, let nothing for a moment separate me from You

Good Jesus, to You I flee;
hide me in Your sacred Side.

O Good Jesus, shelter me from the evil one, shed Your dew upon me to calm my soul, and dwell in me fully, that I may wholly love You.

Good Jesus, Who has borne so patiently with me;
make me wholly patient for love of You.

Good Jesus, lead me that I may follow You; hold me that I may cling fast to You;
teach me, that I may choose You alone; keep me that I may be Yours for ever.

\prayertitle{Prayer of Those in Their Last Agony}
% https://www.ourcatholicprayers.com/aspirations-for-the-dying.html. Also from the Laudate app under ``Aspirations for the Dying''
Jesus, Mary, and Joseph, I give you my heart and my soul.
Jesus, Mary, and Joseph, assist me in my last agony.
Jesus, Mary, and Joseph, may I breathe forth my soul in peace with you.

Into Your Hands, O Lord, I commend my spirit.
O Lord Jesus Christ, receive my spirit.

Holy Mary, pray for me.
O Mary, mother of grace, mother of mercy, protect me from the enemy, and receive me at the hour of death.

St. Joseph, pray for me.
St. Joseph, with the Blessed Virgin, your Spouse, open to me the bosom of divine Mercy.

\prayertitle{Prayer for a Stillborn Child}
% https://www.catholicdoors.com/prayers/english5/p03282.htm
Lord God, ever caring and gentle, we commit to Your Love this little one, quickened to life for so short a time.
Enfold him/her in eternal life.
We pray for his/her parents who are saddened by the loss of their child.
Give them courage and help them in their pain and grief.
May they all meet one day in the joy and peace of Your Kingdom.
We ask this through Christ our Lord.
Amen.