\prayersection{Eucharistic Adoration}
\indulgencedprayertitle{\foreign{O sacrum convivium}}
\linkednote{grant7}{A partial indulgence is granted for offering this prayer to Jesus present in the Blessed Sacrament.}
O sacred banquet, in which Christ is received, the memory of His Passion is renewed, the mind is filled with grace, and a pledge of future glory is given to us.

\indulgencedprayertitle{\foreign{Tantum ergo}}
\linkednote{grant7}{A plenary indulgence is granted for piously reciting the verses of this prayer after the Mass of the Lord's Supper on Holy Thursday during the solemn reposition of the Most Blessed Sacrament.
A partial indulgence is granted for offering this prayer to Jesus present in the Blessed Sacrament.}
Down in adoration falling,
Lo! the sacred Host we hail;
Lo! o'er ancient forms departing,
newer rites of grace prevail;
Faith for all defects supplying,
where the feeble senses fail.
To the everlasting Father,
and the Son Who reigns on high,
with the Holy Spirit proceeding
forth from each eternally
be salvation, honor, blessing,
might and endless majesty.
Amen.

\versicle\ You have given them bread from heaven,

\response\ Having all delight within it.

\versicle\ Let us pray.
O God, Who in this wonderful Sacrament left us a memorial of Your Passion:
grant, we implore You, that we may so venerate the sacred mysteries of Your Body and Blood, as always to be conscious of the fruit of Your Redemption.
You Who live and reign forever and ever.

\response\ Amen.

\prayertitle{Aspirations to Our Lord in the Blessed Sacrament}
% https://www.ourcatholicprayers.com/aspirations.html. Also in Laudate app under the same name.
Jesus, my God, here present in the Sacrament of Your Love, I adore You. 
O Jesus in the Blessed Sacrament, have mercy on us. 
O Jesus, in the most holy Sacrament, have mercy on us. 
Praised and adored forever be the most holy Sacrament. 
We adore You, true Bread of angels. 

\newpage