\prayersection{For the Family}
\indulgencedprayertitle{\foreign{Exaudi Nos}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Hear us, Lord, holy Father, almighty and eternal God;
and graciously send Your holy angel from heaven to watch over, to cherish, to protect, to abide with, and to defend all who dwell in this house.
Through Christ our Lord. Amen.

\indulgencedprayertitle{\foreign{Visita, quaesumus, Domine}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Visit, we beg You, O Lord, this dwelling, and drive from it all snares of the enemy:
let Your holy Angels dwell herein, to keep us in peace;
and let Your blessing be always upon us.
Through Christ our Lord.
Amen.

\prayertitle{For our Family}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-families.cfm which cites Catholic Household Blessings and Prayers
We bless Your Name, O Lord, for sending Your own incarnate Son, to become part of a family, so that, as He lived its life, He would experience its worries and its joys.

We ask You, Lord, to protect and watch over this family, so that in the strength of Your Grace its members may enjoy prosperity, possess the priceless gift of Your Peace, and, as the Church alive in the home, bear witness in this world to Your Glory.

We ask this through Christ our Lord.
Amen.
\newpage
\prayertitle{For Charity in the Family}
% My Prayer Book, p. 264
O Lord, our God, we offer You our hearts united in the strongest and most sincere love of brotherhood.
We pray that Jesus may be the daily food of our souls and bodies and that He may be the center of our affections even as He was for Mary and Joseph.
Finally, O Lord, may sin never disturb our union on earth.
May we be eternally united in heaven with You and Mary and Joseph and all Your saints.
Amen.

\prayertitle{For Children, Relatives, and Friends}
% https://orthodoxprayer.org/Family_Prayers.html
O God, our heavenly Father, Who loves mankind and is a most merciful and compassionate God, have mercy upon Your servants \insertname for whom I humbly pray to You to care for and protect.
O God, be their guide and guardian in all their endeavors, lead them in the path of Your Truth, and draw them nearer to You, so that they may lead a godly and righteous life in Your Love as they do Your Will in all things.
Give them Your Grace and Mercy so that they may be patient, hard working, tireless, devout, and charitable.
Defend them against the assaults of the enemy, and grant them wisdom and strength to resist all temptation and corruption, and direct them in the way of Salvation, through the Goodness of Your Son, our Savior Jesus Christ, and the prayers of His Holy Mother and the blessed saints.
Amen.

\prayertitle{Parents' Thanksgiving}
O God, we give You thanks for \insertname, whom You have welcomed into our family.
Bless this family.
Confirm a lively sense of Your Presence with us, and grant us patience and wisdom, that our lives may show forth the Love of Christ, as we bring \insertname\ up to love all that is good.
We ask this through Christ our Lord.
Amen.

\prayertitle{For Safety for Children}
\label{prayer:safety_children}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-safety.cfm from Catholic Household Blessings and Prayers
Strong and faithful God, keep our children safe from injury and harm and make them blessings to all they meet today.

\prayertitle{A Parent's Prayer}
\label{prayer:parent}
Loving God, You are the giver of all we possess, the source of all of our blessings.
We thank and praise You.

Thank You for the gift of our children.

Help us to set boundaries for them, and yet encourage them to explore.
Give us the strength and courage to treat each day as a fresh start.

May our children come to know You, the one true God, and Jesus Christ, Whom You have sent.

May Your Holy Spirit help them to grow in faith, hope, and love, so they may know peace, truth, and goodness.

May their ears hear Your Voice.
May their eyes see Your Presence in all things.
May their lips proclaim Your Word.
May their hearts be Your dwelling place.
May their hands do works of charity.
May their feet walk in the way of Jesus Christ, Your Son and our Lord.
Amen.

\prayertitle{For One's Parents}
% https://orthodoxprayer.org/Family_Prayers.html
Lord and Savior, You have taught us to honor our fathers and mothers, and to show love and obedience toward them.
From the depth of my heart I fervently pray to You, Jesus, my God: hear my prayer.
Bless my parents who have raised me up with the help of Your Grace.
Protect them from evil, harm, and sickness.
Grant them faith, health, and joy.
Bless all their works that they may give You honor and glory all the days of their lives.
Amen.

\prayertitle{Prayer of a Married Person}
% https://orthodoxprayer.org/Family_Prayers.html
Lord Jesus Christ, by Your Presence You blessed the wedding in Cana and showed us that You are the true priest of mystical and pure marriage.
We thank You for the day on which by Your heavenly Blessing You joined us in the sacrament of marriage.
Lord, continue to bless and enrich our marriage in love, companionship, mutual support, oneness of heart, and progress in faith and life.
Protect our Holy wedlock from sin, evil, and danger.
Nurture between us the spirit of understanding, the spirit of forgiveness, and the spirit of peace, that no resentment, quarrel, or other problem may cause us to stumble and fall.
Grant us to see our own faults and not to judge each other.
Keep our bond of love always new.
Gladden our lives with the joys of marriage, that with one heart we may praise and glorify You.
Amen.

\prayertitle{Husband's Prayer for his Wife}
% My Prayer Book, p. 266
Lord Jesus, in the heart of my heart You know my desire is for my wife's happiness.
You know also I want her to share her love with me and I want to share my love with her.
May the good Grace of Your Spirit guide my uncertain ways that I may be the instrument of my wife's happiness.
Help me to express my love in big and little ways.
Help us to rejoice in each other, to be helpful and thoughtful, always to be aware of the mystery of each other's personality.
I believe we are joined to each other in You.
Show us Your favor, Lord Jesus.
Amen.

\prayertitle{Prayer in Defense of Marriage}
\label{prayer:defense_marriage}
God our Father, we give You thanks for the gift of marriage:
the bond of life and love, and the font of the family. 
The love of husband and wife enriches Your Church with children, fills the world with a multitude of spiritual fruitfulness and service,
and is the sign of the Love of Your Son, Jesus Christ, for His Church.

The Grace of Jesus flowed forth at Cana at the request of the Blessed Mother.
May Your Son, through the intercession of Mary, pour out upon us a new measure of the Gifts of the Holy Spirit as we join with all people of good will to promote and protect the unique beauty of marriage.

May Your Holy Spirit enlighten our society to treasure the heroic love of husband and wife, and guide our leaders to sustain and protect
the singular place of mothers and fathers in the lives of their children.

Father, we ask that our prayers be joined to those of the Virgin Mary, that Your Word may transform our service so as to safeguard the incomparable splendor of marriage.
We ask all these things through Christ our Lord,
Amen.

Saints Joachim and Anne, pray for us.

% \prayertitle{Prayer of a Widow or Widower}
% % https://orthodoxprayer.org/Family_Prayers.html
% Lord Jesus Christ, Who through your mercy resurrected the only son of the widow in Nain:
% I pray to You in need and all alone, putting my hope in God and asking for help.
% O You who fulfill our every need and complete everything we lack, grant me faith, courage, love, and understanding of Your Will.
% Remember Your Servant \insertname in Your Kingdom, always now and forever.
% Amen.

\newpage