\prayersection{General Prayers}
\prayertitle{Jesus Prayer}
\label{prayer:Jesus}
Lord Jesus Christ, Son of God, have mercy on me, a sinner.

\prayertitle{The Grail Prayer}
% Given by many sources on the Internet, also listed as a ``Morning Prayer'' in the Laudate app.
Lord Jesus,
I give You my hands to do Your work.
I give You my feet to go Your way.
I give You my eyes to see as You do.
I give You my tongue to speak Your words.
I give You my mind that You may think in me.
I give You my spirit that You may pray in me.
Above all, I give You my heart that You may love in me Your Father and all mankind.
I give You my whole self that You may grow in me, so that it is You, Lord Jesus,
Who live and work and pray in me.

\prayertitle{\foreign{Aufer a me cor lapideum}}
\label{prayer:take_heart_of_stone}
O Lord, take away my heart of stone, my hardened heart, my uncircumcised heart and grant to me a new heart, a heart of flesh, a clean heart!
O You Who purify the heart and love the clean heart, possess my heart and dwell in it, containing it and filling it, higher than my highest and more intimate than my most intimate thoughts.
You Who are the Image of all beauty and the seal of all holiness, seal my heart in Your Image and seal my heart in Your Mercy, O God of my heart and the God of my portion in eternity.
Amen.

\prayertitle{Prayer for Goodness}
% My Prayer Book, p. 104
O Holy Spirit of God, take me as Your disciple.
Guide me, illuminate me, sanctify me.
Bind my hands that they may do no evil;
cover my eyes that they may see it no more;
sanctify my heart that evil may not dwell within me.
Be my guide;
wherever You lead me, I will go;
whatever You forbid me, I will renounce;
and whatever You command me in Your Strength, I will do.
Lead me then to the fullness of Your Truth.
Amen.

\prayertitle{Prayer for Love of God}
% My Prayer Book, p. 90
O great Lord of heaven and earth, infinite good and majesty, You Who have loved men so tenderly, how is it that You are despised by so many human beings?
You have loved me in a special manner and have bestowed many wonderful graces on me.
Yet I, too, have despised You by every sin through which I have turned against Your Law.
I resolve this day to love You with my whole heart and to love nothing unless it can be loved in You.
Grant me this gift of love:
a fervent love that will make me reject the appeal of sinful creatures;
a strong love that will make me conquer all difficulties to please You;
a persevering love that will never be dissolved.
Amen.

\prayertitle{Prayer for Grace}
\label{prayer:grace}
Oh my God, You know my weakness and failings, and that without Your help I can accomplish nothing for the good of souls, my own and others'.
Grant me, therefore, the help of Your Grace.
Grant it according to my particular needs this day.
Enable me to see the task You will set before me in the daily routine of my life, and help me work hard at my appointed tasks.
Teach me to bear patiently all the trials of suffering or failure that may come to me today. Amen.

\prayertitle{\foreign{Domine Iesu, noverim me}}
\label{prayer:noverim_me}
Lord Jesus, let me know myself and know You,
and desire nothing save only You.
Let me hate myself and love You.
Let me do everything for the sake of You.

Let me humble myself and exalt You.
Let me think of nothing except You.
Let me die to myself and live in You.
Let me accept whatever happens as from You.

Let me banish self and follow You,
and ever desire to follow You.
Let me fly from myself and take refuge in You,
that I may deserve to be defended by You.

Let me fear for myself, let me fear You,
and let me be among those who are chosen by You.
Let me distrust myself and put my trust in You.
Let me be willing to obey for the sake of You.

Let me cling to nothing save only to You,
and let me be poor because of You.
Look upon me, that I may love You.
Call me that I may see You,
and forever enjoy You.
Amen.

\prayertitle{Prayer of Resolution}
\label{prayer:resolution}
Adorable Jesus, my Savior and Master, model of all perfection, I resolve --- and will try this day \textemdash{} to imitate Your example, to be like You, mild, humble, chaste, zealous, charitable, and resigned.
I will redouble my efforts to see Your Image in all those I meet and deal with this day, and to be as helpful to them as I would be to You.
I resolve to avoid this day all those sins which I have committed heretofore and which I now sincerely desire to give up forever. Amen.

\prayertitle{\foreign{Pietate tua}}
\label{prayer:pietate_tua}
Of Your Tender Mercy, we beseech You, O Lord, loose the bonds of our sins, and through the intercession of Mary, the blessed and ever-Virgin Mother of God, together with that of Saint Joseph and Your blessed Apostles Peter and Paul, and of all Your Saints, keep us Your servants and our dwelling places in all holiness;
cleanse from sin and endow with virtue all those who are joined to us by kindred, affinity, and friendship;
grant to us peace and safety;
remove far from us our enemies, both visible and invisible;
repress all our carnal desires;
grant us wholesome air;
bestow Your Charity upon our friends and enemies;
guard Your city;
preserve our Pontiff \insertname;
defend all prelates and princes and Your entire Christian people from every adversity.
Let Your blessing be ever upon us, and grant to all the faithful departed rest everlasting.
Amen.

\indulgencedprayertitle{An Act of Faith}
\label{prayer:act_of_faith}
\linkednote{grant28}{A partial indulgence is granted for reciting an Act of Faith, Hope, and Charity.}
O God,
I firmly believe all the truths that You have revealed and that You teach us through Your Church, for You are truth itself and can neither deceive nor be deceived.

\indulgencedprayertitle{An Act of Hope}
\linkednote{grant28}{A partial indulgence is granted for reciting an Act of Faith, Hope, and Charity.}
O God,
I hope with complete trust that You will give me, through the merits of Jesus Christ, all the necessary grace in this world and everlasting life in the world to come, for this is what You have promised and You always keep Your promises.

\indulgencedprayertitle{An Act of Charity}
\linkednote{grant28}{A partial indulgence is granted for reciting an Act of Faith, Hope, and Charity.}
O God,
I love You with my whole heart above all things, because You are infinitely good; and for Your sake I love my neighbor as I love myself.

\indulgencedprayertitle{An Act of Spiritual Communion}
\linkednote{grant8}{A partial indulgence is granted for reciting this prayer.}
My Jesus, I believe that You are in the Blessed Sacrament.
I love You above all things, and I long for You in my soul.
Since I cannot now receive You sacramentally, come at least spiritually into my heart.
As though You have already come, I embrace You and unite myself entirely to You;
never permit me to be separated from You.
Amen.

% Is this indulgenced, too? See above.
\prayertitle{An Act of Spiritual Communion \#2}
% My Prayer Book, pp. 111-112
Jesus, my Savior and my God!
I am not worthy to be before You, for I am a poor sinner;
yet I approach You with confidence, for You have said, ``Come to Me, all you that labor and are heavy-laden, and I will refresh you.''
You will not despise a contrite and humble heart.
I am truly sorry for my sins, because by them I have offended You Who are infinitely good.
Whatever may have been my foolish transgressions in the past, I love You now above all things, and with all my heart.

Come, my Lord, my God, and my all!
Come to me, and let me never again be separated from You by sin.
Teach me Your blessed ways;
help me with Your Grace to imitate Your example;
to practice meekness, humility, charity, and all the virtues of Your Sacred Heart.
My divine Master, my desire is to do Your Will and to love You more and more;
help me that I may be faithful to the end in Your service.
Bless me in life and in death, that I may praise You forever in heaven.
Amen.

\prayertitle{An Act of Humility}
% My Prayer Book, p. 107, which cites "Eleventh-century Missal"
Devoutly kneeling before Your Majesty,
we earnestly pray that, since You see the limits of our human weakness, You would not in anger blame us for our disobedience, but with Your boundless pity cleanse us, teach us, and comfort us;
and since if You do not help us, we cannot do what is well-pleasing in Your Sight, let Your Grace come to help us, that we may live to our own well-being, ever friends with You.

\indulgencedprayertitle{Prayer of the Sanctuary}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Chaldean Tradition.}
Before the tremendous throne of Your Majesty, at the exalted place of Your Divinity, the majestic seat of Your Glory, and the sublime throne of Your Sovereignty, where Your servants the Cherubim continuously sing hymns and where Your glorifiers the Seraphim sing unceasingly the ``Sanctus,'' we bow down with fear, adore with trembling, give thanks, and glorify You without ceasing, at all times, O Lord of the universe, Father, Son, and Holy Spirit, for all ages.

\prayertitle{For the Missions}
% My Prayer Book, p. 262
God of truth, Father, Son, and Holy Spirit, hear our prayer for those who do not know You, that Your Name may be praised among all peoples of the world.
Sustain and inspire Your servants who bring them the Gospel.
Bring fresh vigor to wavering faith; sustain our faith when it is still fragile.
Renew our missionary zeal.
Make us witnesses to Your Goodness, full of love, of strength, and of faith, for Your Glory and for the salvation of the world.
Amen.
\newpage
\prayertitle{For the New Evangelization}
\label{prayer:new_evangelization}
Heavenly Father, stir in my soul the desire to renew my faith and deepen my relationship with Your Son, our Lord Jesus Christ, so that I might truly believe in and live the Good News.   
Open my heart to hear the Gospel and grant me the confidence to proclaim the Good News to others.
Pour out Your Spirit, so that I might be strengthened to go forth and witness to the Gospel in my everyday life through my words and actions.  

In moments of hesitation, remind me:
If not me, then who will proclaim the Gospel?
If not now, then when will the Gospel be proclaimed?
If not the truth of the Gospel, then what shall I proclaim?

God, our Father, I pray that through the Holy Spirit I might hear the call of the New Evangelization to deepen my faith, grow in confidence to proclaim the Gospel and boldly witness to the saving Grace of Your Son, Jesus Christ, Who lives and reigns with You, in the unity of the Holy Spirit, one God, for ever and ever.
Amen.

\prayertitle{For the Sick}
% My Prayer Book, p. 262
Father, Your only Son took upon Himself the sufferings and weakness of all mankind; through His passion and cross He taught us how good can be brought out of suffering.
Look upon our brothers and sisters who are ill.
In the midst of illness and pain, may they be united with Christ, Who heals both body and soul; may they know the consolation promised to those who suffer and be fully restored to health.
Amen.

\prayertitle{For Those Who are Suffering}
% My Prayer Book, p. 263
Father, You are the unfailing refuge of those who suffer.
Bring peace and comfort to the sick and the infirm, to the aged and the dying.
Give all those who look after them knowledge, patience, and compassion.
Inspire them with actions which will bring relief, words which will enlighten, and love which will bring comfort.
We commend to You the disheartened, the rebellious, those torn by temptation or tormented by desire, and those wounded or abused by the ill will of men.
Lord, pour out on us Your Spirit of love, understanding, and sacrifice; may we then give effective help to the suffering we meet on our way.
Help us to answer their cry, for it is our own.
Amen.

\prayertitle{For Those with Profound Disabilities}
\label{prayer:profound_disabilities}
Lord Jesus Christ, 
You know the pain of brokenness, You took our weaknesses upon Your Shoulders and bore them to the wood of the cross.
Hear our prayers for our brothers and sisters whose bodies fail them and whose minds are crippled by the ravages of disease.
Implant a love for them deep within our hearts, that we, disfigured and disabled by our sin, may treasure and nurture the gifts of their lives.
May we find You in their weakness and console You in our care for them, for You are Lord forever and ever.
Amen.

\prayertitle{For the Aged}
% My Prayer Book, p. 264
Eternal Father, unchanged down the changing years, be near to those who are aged.
Even though their bodies weaken, grant that their spirit may be strong; may they bear weariness and affliction with patience, and, at the end, meet death with serenity.
Amen.

\prayertitle{For the Poor}
\label{prayer:poor}
God of Justice, open our eyes to see You in the face of the poor.
Open our ears to hear You in the cries of the exploited.
Open our mouths to defend You in the public squares as well as in private deeds.
Remind us that what we do to the least ones, we do to You.
Amen.

\prayertitle{For the Marginalized}
\label{prayer:marginalized}
Lord, may those who are deprived of their human needs, and their human rights, be given the dignity which You confer on all Your people.
Change our hearts and move us to love as the Image of Christ those who are forgotten or thrown away, and especially the poor, the sick, and the aged.
May Christ lead us to all who are lonely or afraid: teenagers on the street, old people in nursing homes, prisoners with no one to visit them, and all whom the world has forgotten.
May we cherish the gifts God has given those who are mentally disabled,
and in their lives hear the Voice of our loving God.
May we value, as a priceless gift from God, each human life of all who are forgotten or cast off.

\prayertitle{Prayer to End Trafficking}
\label{prayer:trafficking}
Loving Father, we seek Your divine protection for all who are exploited and enslaved.
For those forced into labor, trafficked into sexual slavery, and denied freedom,
we beseech You to release them from their chains.
Grant them protection, safety, and empowerment.
Restore their dignity and provide them a new beginning.
Show us how we might end exploitation by addressing its causes.
Help us reach out in support of victims and survivors of human trafficking.
Make us instruments of Your Spirit for their liberation.
For this we pray through our Lord Jesus Christ, Who lives and reigns with You in the unity of the Holy Spirit, one God, forever and ever.
Amen.

\prayertitle{For Healing Victims of Abuse}
\label{prayer:healing_victims_abuse}
God of endless love, ever caring, ever strong, always present, always just:
You gave Your only Son to save us by the Blood of His cross.

Gentle Jesus, shepherd of peace, join to Your own suffering the pain of all who have been hurt in body, mind, and spirit by those who betrayed the trust placed in them.

Hear the cries of our brothers and sisters who have been gravely harmed, and the cries of those who love them.
Soothe their restless hearts with hope, steady their shaken spirits with faith.
Grant them justice for their cause, enlightened by Your Truth.

Holy Spirit, comforter of hearts, heal Your people's wounds and transform brokenness into wholeness.
Grant us the courage and wisdom, humility and grace, to act with justice.
Breathe wisdom into our prayers and labors.
Grant that all harmed by abuse may find peace in justice.
We ask this through Christ, our Lord. Amen.

\prayertitle{For Charity in Truth}
\label{prayer:charity_truth}
Father, Your Truth is made known in Your Word.
Guide us to seek the truth of the human person.
Teach us the way to love because You are Love.

Jesus, You embody Love and Truth.
Help us to recognize Your Face in the poor.
Enable us to live out our vocation to bring love and justice to Your people.

Holy Spirit, You inspire us to transform our world.
Empower us to seek the common good for all persons.
Give us a spirit of solidarity and make us one human family.

We ask this through Christ our Lord. Amen.

\indulgencedprayertitle{\foreign{Omnipotens et misericors Deus}}
\linkednote{grant11}{A partial indulgence is granted for devoutly reciting this prayer for the unity of Christians.}
Almighty and merciful God, Who wished to gather the scattered nations into one people
through Your Son, grant that those who glory in the name of Christians may put aside
division and become one in truth and charity, and that all men may be illumined by the
true faith and brought together into the fraternal communion of one Church.
Through Christ our Lord. Amen.

\prayertitle{For the Unity of Christians}
% My Prayer Book, p. 261
God our Father, bring the hearts of all believers together in praise of You and in seeking renewal and reconciliation.
May the divisions between Christians be overcome.
Make us one in faith and love as we walk with Christ to the joy of Your eternal kingdom.
Amen.

\prayertitle{For Our Enemies}
% https://orthodoxprayer.org/OtherPrayers.html#trouble
Lord Jesus Christ, in Your great Mercy You prayed for the forgiveness of those who crucified You, and You taught us to love our enemies and to pray for those who persecute us.
Lord, I pray that You forgive those who treat me unjustly and speak out against me, and that You bless them and guide them according to Your Will.
Take away any bitterness I may have in my heart against them.
Lord, may Your Forgiveness, Goodness, and Love be revealed in all of us, to Your praise and glory.
Amen.

\prayertitle{Prayer to Overcome Indifference}
\label{prayer:indifference}
All too often, Lord, we turn away from the world's many problems, which seem too big, too complex, or too far away.
Forgive us our indifference.

It is easier, Lord, to see only what is around us:
our lives, our homes, our challenges.
Forgive us our isolation.

Help us to see with Your Eyes:
eyes which notice one another and help us understand.

Help us to dream Your dream:
of communities that reach out and dialogue and where diverse people creatively cooperate.

Help us to be people of solidarity and action, so moved by prayer, encounter, and understanding that peace can become a reality.
Amen.

\prayertitle{For Patience}
% https://www.ourcatholicprayers.com/prayers-for-patience.html
My dearest Jesus, teach me to be patient, when all day long my heart is troubled by little but troublesome crosses.

\prayertitle{Prayer to Live the Gospel}
Loving Father, open our hearts to hidden realities:
Your Love for all people,
Your Presence in the community,
Your call to justice and peace.
May the sacraments stir in us
that same love for those with whom we worship and all members of our human family.

Christ Jesus, help us to imitate Your example:
healing the sick,
welcoming the stranger,
assisting the poor and vulnerable.
May the sacraments remind us
of Your Love and Self-giving,
which we strive to imitate.

Holy Spirit, make visible to our eyes what is invisible:
Your call to Your people,
Your summons to live our faith daily
as witnesses of justice and peace.
May the sacraments move us to engage in love-inspired action that transforms us and the world.
Amen.

\indulgencedprayertitle{\foreign{Retribuere dignare, Domine}}
\linkednote{grant24}{A partial indulgence is granted for devoutly reciting this prayer.}
May it please You, O Lord, to reward with eternal life all those who do good to us for Your Name's sake. Amen.

\indulgencedprayertitle{\foreign{Veni, Sancte Spiritus}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Come, Holy Spirit, fill the hearts of Your faithful and enkindle in them the fire of Your Love.

\indulgencedprayertitle{\foreign{Veni, Creator}}
\linkednote{grant26}{A plenary indulgence is granted for devoutly assisting in the recitation or solemn singing of this prayer on the first day of the year or on the solemnity of Pentecost.
A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Come, Holy Spirit, Creator blest,
and in our souls take up Thy rest;
come with Thy Grace and heavenly aid
to fill the hearts which Thou hast made.

O comforter, to Thee we cry,
O heavenly Gift of God Most High,
O Fount of Life and Fire of Love,
and sweet anointing from above.

Thou in Thy sevenfold gifts are known;
Thou, Finger of God's Hand we own;
Thou, promise of the Father, Thou
Who dost the tongue with power imbue.

Kindle our sense from above,
and make our hearts o'erflow with love;
with patience firm and virtue high
the weakness of our flesh supply.

Far from us drive the foe we dread,
and grant us Thy Peace instead;
so shall we not, with Thee for guide,
turn from the path of life aside.

Oh, may Thy Grace on us bestow
the Father and the Son to know;
and Thee, through endless times confessed,
of both the eternal Spirit blest.

Now to the Father and the Son,
Who rose from death, be glory given,
with Thou, O Holy Comforter,
henceforth by all in earth and heaven.
Amen.

\prayertitle{Prayer to the Holy Spirit}
% https://orthodoxprayer.org/Introductory%20Prayers.html
Heavenly King, Comforter, the Spirit of Truth, present in all places and filling all things, Treasury of Goodness and Giver of life: come and abide in us.
Cleanse us from every stain of sin and save our souls, O Gracious Lord.

\prayertitle{Serenity Prayer}
God, grant me the serenity to accept the things I cannot change,
courage to change the things I can,
and wisdom to know the difference.

\prayertitle{Prayer of Thanksgiving}
% Combined multiple prayers from My Prayer Book, pp. 248-249
Father of all gifts, we praise You, the source of all we have and are.
Teach us to acknowledge always the good things Your infinite Love has given us.
Help us to love You with all our hearts and all our strength as our expression of thanksgiving for Your many blessings.
Fill our hearts with this spirit of gratitude.

Father of Mercy, we thank You for Your Kindness and ask You to free us from all evil that we may serve You with generous hearts and in happiness all our days.
Make us always aware of Your mercies that with truly thankful hearts, we may make known Your praise by giving wholeheartedly of ourselves, and by true holiness of lives all honor and glory will be Yours throughout all ages.

Almighty God, Father of all mercies, we Your unworthy servants give You humble thanks for all Your Goodness and loving Kindness to us and to all men, particularly our families, friends, and loved ones.
We bless You for our creation and all the blessings of this life, but above all, for Your incomparable and undying Love in the redemption of the world by Your Son, our Lord and Savior Jesus Christ.
Amen.

\indulgencedprayertitle{\foreign{Te Deum}}
\linkednote{grant26}{A plenary indulgence is granted for devoutly assisting in the recitation or solemn singing of this prayer on the final day of the year.
A partial indulgence is granted for devoutly offering a prayer of thanksgiving such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
% My Prayer Book, pp. 250-251
O God, we praise You, and acknowledge You to be the supreme Lord.
Everlasting Father, all the earth worships You.
All the angels, the heavens and all angelic powers, all the cherubim and seraphim, continually cry to You:
Holy, holy, holy, Lord God of Hosts!
Heaven and earth are full of the majesty of Your Glory.
The glorious choir of the apostles, the wonderful company of prophets, the white-robed army of martyrs, praise You.
Holy Church throughout the world acknowledges You:
the Father of infinite majesty;
Your adorable, true, and only Son;
also the Holy Spirit, the Comforter.

O Christ, You are the King of Glory!
You are the everlasting Son of the Father.
When You took it upon Yourself to deliver man, You did not disdain the Virgin's womb.
Having overcome the sting of death, You opened the kingdom of heaven to all believers.
You sit at the right Hand of God in the Glory of the Father.
We believe that You will come to be our Judge.
We therefore beg You to help Your servants whom You have redeemed with Your Precious Blood.
Let them be numbered with Your saints in everlasting glory.
Save Your people, O Lord, and bless Your inheritance!
Govern them, and raise them up forever.
Every day we thank You.
And we praise Your Name forever;
yes, forever and ever.

O Lord, deign to keep us from sin this day.
Have mercy on us, O Lord, have mercy on us.
Let Your Mercy, O Lord, be upon us, for we have hoped in You.
O Lord, in You I have put my trust;
let me never be put to shame.

\indulgencedprayertitle{Thanksgiving for the Church}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Armenian Tradition.}
We thank You, Almighty Father, for having prepared the holy Church for us as a haven
of rest, a temple of holiness, where Your Holy Trinity is glorified. Alleluia.

We thank You, Christ our King, for having given us life through Your vivifying Body
and Your holy Blood; grant us expiation and great mercy. Alleluia.

We thank You, true Spirit, for having renewed the holy Church; preserve her immaculate, by means of faith in the Trinity, now and forever. Alleluia.

We thank You, O Christ our God, for having given us such a Food of goodness for
holiness of life.
By means of it preserve us holy and immaculate by living in us with Your divine care.
Lead us to the pastures of Your holy Will, O Effecter of good; by means of it fortify us against every snare of the calumniator.
Make us worthy to listen to Your Voice alone, to follow only You, true and victorious Shepherd, and to receive from You the place You prepared for us in Your heavenly kingdom, O God and Lord Jesus Christ our Savior, Who are blessed with the Father and Your Holy Spirit, now and always for ever and ever.
Amen.

\prayertitle{For Civic Leaders}
\label{prayer:civic-leaders}
God our Father, You guide everything in wisdom and love.
Accept the prayers we offer for our nation.
In Your Goodness, watch over those in authority so that people everywhere may enjoy freedom, security, and peace.
We ask this through Christ our Lord.
Amen.

\prayertitle{Prayer for Basic Rights}
\label{prayer:basic-rights}
Lord of Wisdom, awaken us to our duty to care for the basic needs of all people.
Strengthen with hope people denied their human rights and freedoms.
Provide us all with the voice to cry out for justice for the poor and the oppressed.
Amen.

\prayertitle{Prayer for Peace}
% Combined from multiple prayers in My Prayer Book, pp. 254-255
God, Creator of the world, You established the order which governs all ages.
Hear our prayer and give us peace in our time that we may rejoice in Your Mercy and praise You without end.

God of perfect peace, neither violence nor cruelty can be part of You;
bring peace into the world by bringing Your Peace into the hearts of all men throughout the world.

May those who are at peace with one another hold fast to the good will that unites them.
May those who are enemies forget their hatred and be healed.
Help us to turn away from sin, and to follow You in love and service.

God our Father, You reveal that those who work for peace will be called Your sons.
Help us to work without ceasing for that justice which brings true and everlasting peace.

\prayertitle{A Family's Prayer for World Peace}
% My Prayer Book, pp. 255-256
Lord Jesus Christ, Who said to Your apostles:
``Peace I leave with you, My peace I give to you;
not as the world gives, do I give to you,''
regard not our sins but Your merits.
Grant to all Your servants that they, whom the almighty Father has created and governs, and whom You have redeemed by Your precious Blood and destined for everlasting life, may love one another with all their hearts for Your sake and may be made one in spirit and rejoice in Your perpetual peace.

Lord Jesus Christ, concerning Whom the prophet has said:
``And all kings of the earth shall adore Him, all nations shall serve Him,''
extend Your reign over the whole human race.
Send upon all men the light of Your faith, deliver them from all the snares and bonds of passion and direct them to heavenly things.

Graciously grant that states and nations may be united through Your holy Church and through the intercession of the blessed virgin Mary, queen of peace, that they may serve You in all humility;
and that all tongues and peoples may form one great choir to praise You King and Ruler of the nations, Prince of Peace, immortal King of ages.
Amen.

\prayertitle{Prayer in Times of Seeking God's Will}
% Partially from http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-in-times-of-seeking-the-will-of-god.cfm
Hear, O Lord, the sound of my call;
have pity on me, and answer me.
Of You my heart speaks;
You my glance seeks;
Your Presence, O Lord, I seek.
Hide not Your Face from me; 
do not in anger repel Your servant.
You are my helper: cast me not off;
forsake me not, O God my savior.

\prayertitle{Prayer Toward the Unknown}
% https://orthodoxprayer.org/OtherPrayers.html#unknown
O Lord, You Who steadied the hand of Peter as he began to sink on the stormy sea: if You are with me, no one is against me.
Grant to me the shield of faith and the mighty armor of the Holy Spirit to protect me and guide me to do Your Will.
The future I put into Your Hands, O Lord, and I follow You to a life in Christ.
Amen.

\prayertitle{Act of Resignation to the Divine Will}
% My Prayer Book, p. 270
O Lord, my God, I, now at this moment, readily and willingly accept at Your Hand whatever kind of death it may please You to send me, with all its pains, penalties, and sorrows.
Amen.

\prayertitle{For a Happy Death}
% My Prayer Book, p. 270
Lord Jesus, by Your agony and death, deliver me from a sudden and unexpected death.
I humbly beseech You to never let me die unexpectedly and pass from this life without the Sacraments.
Jesus, my Lord, by all Your labors and sorrows, by Your precious Blood and most holy Wounds, and by Your words on the cross:
``My God, my God, why have You forsaken me?''
and again:
``Father, into Your Hands I commend my spirit'',
I beseech You to save me from an unexpected death.
Give me, most merciful Jesus, time for penance;
and pray that I may pass from this life happily into Your Grace, that I may love You with my whole heart, and bless You for ever and ever.
Amen.

\prayertitle{Self-Dedication to Jesus Christ}
% My Prayer Book, p. 89
Lord Jesus Christ take all my freedom, my memory, my understanding, and my will.
All that I have and cherish You have given me.
I surrender it all to be guided by Your Will.
Your Grace and Your Love are wealth enough for me.
Give me these, Lord Jesus, and I ask for nothing more.

\prayertitle{The Lord's Prayer}
Our Father, Who art in heaven, hallowed be Thy Name.
Thy Kingdom come;
Thy Will be done on earth as it is in heaven.
Give us this day our daily bread;
and forgive us our trespasses, as we forgive those who trespass against us;
and do not let us fall into temptation, but deliver us from evil.

\prayertitle{Gloria (Major Doxology)}
\label{prayer:gloria}
Glory to God in the highest, and peace on earth to men of good will.

We praise You, we bless You, we adore You, we glorify You, we give You thanks for Your great Glory, O Lord God, heavenly King, God the Father Almighty.

O Lord Jesus Christ, only begotten Son, Lord God, Lamb of God, Son of the Father, You Who take away the sins of the world, have mercy on us;
You Who take away the sins of the world, receive our prayer.
You Who sit at the right Hand of the Father, have mercy on us.

For You alone are the Holy One, You alone are the Lord, You alone are the Most High, Jesus Christ, with the Holy Spirit, in the Glory of God the Father.
Amen.

\prayertitle{Glory Be (Minor Doxology)}
\label{prayer:glory_be}
Glory be to the Father, and to the Son, and to the Holy Spirit, as it was in the beginning, is now, and will be forever.
Amen.

\prayertitle{\foreign{Omnipotentia Patris}}
\label{prayer:Omnipotentia_Patris}
Omnipotence of the Father, help my frailty and save me from the depths of misery.
Wisdom of the Son, direct all my thoughts, words, and deeds.
Love of the Holy Spirit, be the source of all the operations of my mind, that they may ever be conformed to God's good pleasure.
Amen.

\prayertitle{\foreign{Adoramus te}}
\label{prayer:adoramus_te}
We adore You, most holy Lord Jesus Christ, here and in all Your churches that are in the whole world, and we bless You;
because by Your Holy Cross You have redeemed the World.
Amen.

\prayertitle{\foreign{Sanctus}}
\label{prayer:sanctus}
Holy, holy, holy, Lord God of hosts.
Heaven and earth are full of Your Glory.
Hosanna in the highest.
Blessed is he who comes in the Name of the Lord.
Hosanna in the highest.

\prayertitle{The Holy Face}
\label{prayer:holy_face}
O Blessed Face of my kind Savior, by the tender love and piercing sorrow of Our Lady as she beheld You in Your cruel Passion, grant us to share in this intense sorrow and love
so as to fulfill the holy Will of God to the utmost of our ability.
Amen.

\prayertitle{The Golden Arrow Prayer}
% https://en.wikipedia.org/wiki/The_Golden_Arrow_prayer
May the Most Holy, Most Sacred, Most Adorable, Most Incomprehensible and Ineffable Name of God
be forever praised, blessed, loved, adored, and glorified in Heaven, on earth, and under the earth, by all the creatures of God, and by the Sacred Heart of Our Lord Jesus Christ, in the Most Holy Sacrament of the Altar.
Amen.

\prayertitle{Short Prayer}
\label{prayer:short}
Lord, help me to remember that nothing is going to happen to me today that You and I together can't handle. Amen.

\indulgencedprayertitle{\foreign{Angele Dei}}
\linkednote{grant18}{A partial indulgence is granted for devoutly invoking the care of one's guardian angel with this prayer.}
Angel of God, my guardian dear, to whom His love entrusts me here, enlighten and guard, rule and guide me. Amen.

\prayertitle{F\'{a}tima Theological Prayer}
% https://en.wikipedia.org/wiki/F%C3%A1tima_prayers
My God, I believe, I adore, I hope, and I love You. I ask pardon for all those who do not believe in You, do not adore You, do not hope in You, and do not love You.

\prayertitle{F\'{a}tima Trinitarian Prayer}
% https://en.wikipedia.org/wiki/F%C3%A1tima_prayers
Most Holy Trinity --- Father, Son, and Holy Spirit --- I adore You profoundly, and I offer You the Most Precious Body, Blood, Soul, and Divinity of Jesus Christ, present in all the tabernacles of the world, in reparation for the outrages, sacrileges, and indifferences by which He is offended.
And by the infinite merits of His most Sacred Heart and the Immaculate Heart of Mary, I beg the conversion of poor sinners.

\prayertitle{F\'{a}tima Rosary Decade Prayer}
% https://en.wikipedia.org/wiki/F%C3%A1tima_prayers
O my Jesus, forgive us our sins and save us from the fires of Hell.
Lead all souls to heaven, especially those in most need of Your Mercy.

\indulgencedprayertitle{Act of Reparation (\foreign{Iesu dulcissime})}
\linkednote{grant3}{A plenary indulgence is granted for publicly reciting this prayer on the solemnity of the Most Sacred Heart of Jesus;
a partial indulgence is granted for its use in other circumstances.}
Most sweet Jesus, whose overflowing charity for men is requited by so much forgetfulness, negligence, and contempt, behold us prostrate before You, eager to repair by a special act of homage the cruel indifference and injuries to which Your loving Heart is everywhere subjected.
Mindful, alas! that we ourselves have had a share in such great indignities, which we now deplore from the depths of our hearts, we humbly ask Your pardon and declare our readiness to atone by voluntary expiation, not only for our own personal offenses, but also for the sins of those who, straying far from the path of salvation, refuse in their obstinate infidelity to follow You, their Shepherd and Leader, or, renouncing the promises of their Baptism, have cast off the sweet yoke of Your Law.

We are now resolved to expiate each and every deplorable outrage committed against You; we are determined to make amends for the manifold offenses against Christian modesty in indecent dress and behavior, for all the foul seductions laid to ensnare the feet of the innocent, for the frequent violations of Sundays and holydays, and for the shocking blasphemies uttered against You and Your Saints.
We wish also to make amends for the insults to which Your Vicar on earth and Your priests are subjected, for the profanation, by conscious neglect or terrible acts of sacrilege, of the very Sacrament of Your divine Love, and lastly for the public crimes of nations who
resist the rights and teaching authority of the Church which You have founded.

Would that we were able to wash away such abominations with our blood.
We now offer, in reparation for these violations of Your divine Honor, the satisfaction You once made to Your Eternal Father on the cross and which You continue to renew daily on our altars;
we offer it in union with the acts of atonement of Your Virgin Mother and all the saints and of the pious faithful on earth;
and we sincerely promise to make recompense, as far as we can with the help of Your Grace, for all neglect of Your great Love and for the sins we and others have committed in the past.
Henceforth, we will live a life of unswerving faith, of purity of conduct, of perfect observance of the precepts of the Gospel and especially that of charity.
We promise to the best of our power to prevent others from offending You and to bring as many as possible to follow You.

O loving Jesus, through the intercession of the Blessed Virgin Mother, our model in reparation, deign to receive the voluntary offering we make of this act of expiation;
and by the crowning gift of perseverance keep us faithful unto death in our duty and the allegiance we owe to You, that we may all one day come to that happy home, where with the Father and the Holy Spirit You live and reign, for ever and ever. Amen.

\indulgencedprayertitle{Act of Dedication of the Human Race to Christ the King (\foreign{Iesu dulcissime, Redemptor})}
\linkednote{grant2}{A plenary indulgence is granted for publicly reciting this prayer on the solemnity of Our Lord Jesus Christ, King of the Universe (on the last Sunday of Ordinary Time, i.e. the Sunday preceding the first Sunday of Advent);
a partial indulgence is granted for its use in other circumstances.}
Most sweet Jesus, Redeemer of the human race, look down upon us humbly prostrate before You.
We are Yours, and Yours we wish to be;
but to be more surely united with You, behold each one of us freely consecrates himself today to Your Most Sacred Heart.
Many indeed have never known You;
many, too, despising Your precepts, have rejected You.
Have mercy on them all, most merciful Jesus, and draw them to Your Sacred Heart.
Be King, O Lord, not only of the faithful who have never forsaken You, but also of the prodigal children who have abandoned You;
grant that they may quickly return to their Father's house, lest they die of wretchedness and hunger.
Be King of those who are deceived by erroneous opinions, or whom discord keeps aloof, and call them back to the harbor of truth and the unity of faith, so that soon there may be but one flock and one Shepherd.
Grant, O Lord, to Your Church assurance of freedom and immunity from harm;
give tranquility of order to all nations;
make the earth resound from pole to pole with one cry:
Praise to the divine Heart that wrought our salvation;
to it be glory and honor for ever.
Amen.

\newpage