\prayersection{General Intercessions}
\indulgencedprayertitle{\foreign{Retribuere dignare, Domine}}
\linkednote{grant24}{A partial indulgence is granted for devoutly reciting this prayer.}
May it please You, O Lord, to reward with eternal life all those who do good to us for Your Name's sake. Amen.

\prayertitle{For the Missions}
% My Prayer Book, p. 262
God of truth, Father, Son, and Holy Spirit, hear our prayer for those who do not know You, that Your Name may be praised among all peoples of the world.
Sustain and inspire Your servants who bring them the Gospel.
Bring fresh vigor to wavering faith; sustain our faith when it is still fragile.
Renew our missionary zeal.
Make us witnesses to Your Goodness, full of love, of strength, and of faith, for Your Glory and for the salvation of the world.
Amen.

\prayertitle{For the Sick}
% My Prayer Book, p. 262
Father, Your only Son took upon Himself the sufferings and weakness of all mankind; through His passion and cross He taught us how good can be brought out of suffering.
Look upon our brothers and sisters who are ill.
In the midst of illness and pain, may they be united with Christ, Who heals both body and soul; may they know the consolation promised to those who suffer and be fully restored to health.
Amen.

\prayertitle{For Those Who are Suffering}
% My Prayer Book, p. 263
Father, You are the unfailing refuge of those who suffer.
Bring peace and comfort to the sick and the infirm, to the aged and the dying.
Give all those who look after them knowledge, patience, and compassion.
Inspire them with actions which will bring relief, words which will enlighten, and love which will bring comfort.
We commend to You the disheartened, the rebellious, those torn by temptation or tormented by desire, and those wounded or abused by the ill will of men.
Lord, pour out on us Your Spirit of love, understanding, and sacrifice; may we then give effective help to the suffering we meet on our way.
Help us to answer their cry, for it is our own.
Amen.

\prayertitle{For Those with Profound Disabilities}
\label{prayer:profound_disabilities}
Lord Jesus Christ, 
You know the pain of brokenness, You took our weaknesses upon Your Shoulders and bore them to the wood of the cross.
Hear our prayers for our brothers and sisters whose bodies fail them and whose minds are crippled by the ravages of disease.
Implant a love for them deep within our hearts, that we, disfigured and disabled by our sin, may treasure and nurture the gifts of their lives.
May we find You in their weakness and console You in our care for them, for You are Lord forever and ever.
Amen.

\prayertitle{For the Aged}
% My Prayer Book, p. 264
Eternal Father, unchanged down the changing years, be near to those who are aged.
Even though their bodies weaken, grant that their spirit may be strong; may they bear weariness and affliction with patience, and, at the end, meet death with serenity.
Amen.

\prayertitle{For the Poor}
\label{prayer:poor}
God of Justice, open our eyes to see You in the face of the poor.
Open our ears to hear You in the cries of the exploited.
Open our mouths to defend You in the public squares as well as in private deeds.
Remind us that what we do to the least ones, we do to You.
Amen.

\prayertitle{For the Marginalized}
\label{prayer:marginalized}
Lord, may those who are deprived of their human needs, and their human rights, be given the dignity which You confer on all Your people.
Change our hearts and move us to love as the Image of Christ those who are forgotten or thrown away, and especially the poor, the sick, and the aged.
May Christ lead us to all who are lonely or afraid: teenagers on the street, old people in nursing homes, prisoners with no one to visit them, and all whom the world has forgotten.
May we cherish the gifts God has given those who are mentally disabled,
and in their lives hear the Voice of our loving God.
May we value, as a priceless gift from God, each human life of all who are forgotten or cast off.

\prayertitle{Prayer to End Trafficking}
\label{prayer:trafficking}
Loving Father, we seek Your divine protection for all who are exploited and enslaved.
For those forced into labor, trafficked into sexual slavery, and denied freedom,
we beseech You to release them from their chains.
Grant them protection, safety, and empowerment.
Restore their dignity and provide them a new beginning.
Show us how we might end exploitation by addressing its causes.
Help us reach out in support of victims and survivors of human trafficking.
Make us instruments of Your Spirit for their liberation.
For this we pray through our Lord Jesus Christ, Who lives and reigns with You in the unity of the Holy Spirit, one God, forever and ever.
Amen.

\prayertitle{For Our Enemies}
% https://orthodoxprayer.org/OtherPrayers.html#trouble
Lord Jesus Christ, in Your great Mercy You prayed for the forgiveness of those who crucified You, and You taught us to love our enemies and to pray for those who persecute us.
Lord, I pray that You forgive those who treat me unjustly and speak out against me, and that You bless them and guide them according to Your Will.
Take away any bitterness I may have in my heart against them.
Lord, may Your Forgiveness, Goodness, and Love be revealed in all of us, to Your praise and glory.
Amen.

\indulgencedprayertitle{\foreign{Omnipotens et misericors Deus}}
\linkednote{grant11}{A partial indulgence is granted for devoutly reciting this prayer for the unity of Christians.}
Almighty and merciful God, Who wished to gather the scattered nations into one people
through Your Son, grant that those who glory in the name of Christians may put aside
division and become one in truth and charity, and that all men may be illumined by the
true faith and brought together into the fraternal communion of one Church.
Through Christ our Lord. Amen.

\prayertitle{For the Unity of Christians}
% My Prayer Book, p. 261
God our Father, bring the hearts of all believers together in praise of You and in seeking renewal and reconciliation.
May the divisions between Christians be overcome.
Make us one in faith and love as we walk with Christ to the joy of Your eternal kingdom.
Amen.

\prayertitle{Prayer for Peace}
% Combined from multiple prayers in My Prayer Book, pp. 254-255
God, Creator of the world, You established the order which governs all ages.
Hear our prayer and give us peace in our time that we may rejoice in Your Mercy and praise You without end.

God of perfect peace, neither violence nor cruelty can be part of You;
bring peace into the world by bringing Your Peace into the hearts of all men throughout the world.

May those who are at peace with one another hold fast to the good will that unites them.
May those who are enemies forget their hatred and be healed.
Help us to turn away from sin, and to follow You in love and service.

God our Father, You reveal that those who work for peace will be called Your sons.
Help us to work without ceasing for that justice which brings true and everlasting peace.

\prayertitle{A Family's Prayer for World Peace}
% My Prayer Book, pp. 255-256
Lord Jesus Christ, Who said to Your apostles:
``Peace I leave with you, My peace I give to you;
not as the world gives, do I give to you,''
regard not our sins but Your merits.
Grant to all Your servants that they, whom the almighty Father has created and governs, and whom You have redeemed by Your precious Blood and destined for everlasting life, may love one another with all their hearts for Your sake and may be made one in spirit and rejoice in Your perpetual peace.

Lord Jesus Christ, concerning Whom the prophet has said:
``And all kings of the earth shall adore Him, all nations shall serve Him,''
extend Your reign over the whole human race.
Send upon all men the light of Your faith, deliver them from all the snares and bonds of passion and direct them to heavenly things.

Graciously grant that states and nations may be united through Your holy Church and through the intercession of the blessed virgin Mary, queen of peace, that they may serve You in all humility;
and that all tongues and peoples may form one great choir to praise You King and Ruler of the nations, Prince of Peace, immortal King of ages.
Amen.

\prayertitle{For Civic Leaders}
\label{prayer:civic-leaders}
God our Father, You guide everything in wisdom and love.
Accept the prayers we offer for our nation.
In Your Goodness, watch over those in authority so that people everywhere may enjoy freedom, security, and peace.
We ask this through Christ our Lord.
Amen.

\prayertitle{Prayer for Basic Rights}
\label{prayer:basic-rights}
Lord of Wisdom, awaken us to our duty to care for the basic needs of all people.
Strengthen with hope people denied their human rights and freedoms.
Provide us all with the voice to cry out for justice for the poor and the oppressed.
Amen.

\prayertitle{For Healing Victims of Abuse}
\label{prayer:healing_victims_abuse}
God of endless love, ever caring, ever strong, always present, always just:
You gave Your only Son to save us by the Blood of His cross.

Gentle Jesus, shepherd of peace, join to Your own suffering the pain of all who have been hurt in body, mind, and spirit by those who betrayed the trust placed in them.

Hear the cries of our brothers and sisters who have been gravely harmed, and the cries of those who love them.
Soothe their restless hearts with hope, steady their shaken spirits with faith.
Grant them justice for their cause, enlightened by Your Truth.

Holy Spirit, comforter of hearts, heal Your people's wounds and transform brokenness into wholeness.
Grant us the courage and wisdom, humility and grace, to act with justice.
Breathe wisdom into our prayers and labors.
Grant that all harmed by abuse may find peace in justice.
We ask this through Christ, our Lord. Amen.

\prayertitle{For Charity in Truth}
\label{prayer:charity_truth}
Father, Your Truth is made known in Your Word.
Guide us to seek the truth of the human person.
Teach us the way to love because You are Love.

Jesus, You embody Love and Truth.
Help us to recognize Your Face in the poor.
Enable us to live out our vocation to bring love and justice to Your people.

Holy Spirit, You inspire us to transform our world.
Empower us to seek the common good for all persons.
Give us a spirit of solidarity and make us one human family.

We ask this through Christ our Lord. Amen.