\prayersection{For Times of Infirmity}
\prayertitle{Prayer of a Sick Person}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Jesus Christ, my Lord and Savior, You became man and died on the cross for our salvation.
You healed people of sickness and affliction through Your Love and Compassion.
Visit me, Lord, and grant me strength to bear this sickness with which I am afflicted, with patience, submission to Your Will, and trust in Your loving care.
I pray that You will bless the means used for my recovery and those who administer them.
Grant that my sickness may be to my spiritual benefit and that I may live the rest of my life more faithfully according to Your Will.
For You are the source of life and healing and to You I give praise and glory, now and forever.
Amen.

\prayertitle{Prayer for a Sick Person}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Heavenly Father, physician of our souls and bodies, Who have sent Your only-begotten Son and our Lord Jesus Christ to heal every sickness and infirmity, visit and heal also Your servant \insertname from all physical and spiritual ailments through the grace of Your Christ.
Grant him/her patience in this sickness, strength of body and spirit, and recovery of health.
Lord, You have taught us through Your Word to pray for each other that we may be healed.
I pray, heal Your servant \insertname and grant to him/her the gift of complete health.
For You are the source of healing and to You I give glory, Father, Son, and Holy Spirit.
Amen.

\prayertitle{Prayer to St. Peregrine for Those Sick with Cancer}
O great St. Peregrine, you have been called ``The Mighty,'' ``The Wonder-Worker,'' because of the numerous miracles which you have obtained from God for those who have had recourse to you.
For so many years you bore in your own flesh this cancerous disease that destroys the very fiber of our being, and who had recourse to the source of all grace when the power of man could do no more.
You were favored with the vision of Jesus coming down from His Cross to heal your affliction.
Ask of God and Our Lady, the cure of the sick whom we entrust to you: \insertname.
Aided in this way by your powerful intercession, we shall sing to God, now and for all eternity, a song of gratitude for His great Goodness and Mercy.
Amen.

\prayertitle{Prayer to St. Peregrine for Help with Cancer}
St. Peregrine, whom Holy Mother Church has declared Patron of those suffering from cancer, I confidently turn to you for help in my present sickness.
I beg your kind intercession.
Ask God to relieve me of this sickness, if it be His Holy Will.
Plead with the Blessed Virgin Mary, the Mother of Sorrows, whom you loved so tenderly and in union with whom you have suffered the pains of cancer, that she may help me with her powerful prayers and loving consolation.

But if it should be God's Holy Will that I bear this sickness, obtain for me courage and strength to accept these trials from the loving Hand of God with patience and resignation, because He knows what is best for the salvation of my soul.
St. Peregrine, be my friend and patron.
Help me to imitate you in accepting suffering, and to unite myself with Jesus Crucified and the Mother of Sorrows, as you did.
I offer my pains to God with all the love of my heart, for His glory and the salvation of souls, especially my own.
Amen.

\prayertitle{Prayer after an Operation}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Holy Father, the only true Physician of our souls and bodies, who cast down and lift up, accept me as I come in all humility to glorify You and thank You for preserving, by Your Grace, Your servant \insertname through his/her recent operation.
We thank You for blessing the attending physicians and the means employed for his/her cure, and for restoring him/her safe and sound to his/her family and Church, having fended off every danger against his/her body and soul.
Raise him/her speedily, we pray You, from the bed of illness on which he/she lies and return him/her to his/her home and peaceful pursuits.
Grant that the suffering of his/her body may avail for the purifying of his/her soul and may lead him/her to return, in thanksgiving, to the works of his/her hands and to Christ Jesus, the Physician of soul and body.
Through the prayers of our Holy Fathers, Lord Jesus Christ have mercy on us and save us.
Amen.

\prayertitle{Thanksgiving after Recovery}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Almighty God and heavenly Father, You are the fountain of life and healing.
I bless Your Holy Name and offer to You thanks for having delivered me from sickness and restored me to health.
Grant me Your eternal Grace, I pray, that I may live a new life in true obedience to You.
Guide me to do Your Will in all things, devoting my life to Your service.
Thus living for You may I be found worthy of Your kingdom, where You dwell in glory with Your Son and Your Holy Spirit forever.
Amen.