\prayersection{Litanies}
\prayertitle{Litany of St. Joseph}
\linkednote{grant22}{A partial indulgence is granted for devoutly reciting this litany.}
Lord, have mercy. \respond{Lord, have mercy.}\\
Christ, have mercy. \respond{Christ, have mercy.}\\
Lord, have mercy. \respond{Lord, have mercy.}\\
God our Father in heaven, \respond{have mercy on us.}\\
God the Son, Redeemer of the world, \respond{have mercy on us.}\\
God the Holy Spirit, \respond{have mercy on us.}\\
Holy Trinity, one God, \respond{have mercy on us.}\\
Holy Mary, \respond{pray for us.}\\
Saint Joseph, \respond{pray for us.}\\
Noble son of the House of David, \respond{pray for us.}\\
Light of patriarchs, \respond{pray for us.}\\
Husband of the Mother of God, \respond{pray for us.}\\
Guardian of the Virgin, \respond{pray for us.}\\
Foster father of the Son of God, \respond{pray for us.}\\
Faithful guardian of Christ, \respond{pray for us.}\\
Head of the Holy Family, \respond{pray for us.}\\
Joseph, chaste and just, \respond{pray for us.}\\
Joseph, prudent and brave, \respond{pray for us.}\\
Joseph, obedient and loyal, \respond{pray for us.}\\
Pattern of patience, \respond{pray for us.}\\
Lover of poverty, \respond{pray for us.}\\
Model of workers, \respond{pray for us.}\\
Example to parents, \respond{pray for us.}\\
Guardian of virgins, \respond{pray for us.}\\
Pillar of family life, \respond{pray for us.}\\
Comfort of the troubled, \respond{pray for us.}\\
Hope of the sick, \respond{pray for us.}\\
Patron of the dying, \respond{pray for us.}\\
Terror of evil spirits, \respond{pray for us.}\\
Protector of the Church, \respond{pray for us.}\\
Lamb of God, you take away the sins of the world, \respond{have mercy on us.}\\
Lamb of God, you take away the sins of the world, \respond{have mercy on us.}\\
Lamb of God, you take away the sins of the world, \respond{have mercy on us.}\\
God made him master of his household, \respond{and put him in charge of all that he owned.}

Let us pray: Almighty God, in Your infinite Wisdom and Love You chose Joseph to be the husband of Mary, the mother of Your Son. As we enjoy his protection on earth may we have the help of his prayers in heaven. We ask this through Christ our Lord. Amen.

\prayertitle{Litany of Humility}
\label{prayer:litany_of_humility}
O Jesus! meek and humble of heart, hear me.

From the desire of being esteemed, \respond{deliver me, Jesus}.\\
From the desire of being loved\ldots\\
From the desire of being extolled\ldots\\
From the desire of being honored\ldots\\
From the desire of being praised\ldots\\
From the desire of being preferred to others\ldots\\
From the desire of being consulted\ldots\\
From the desire of being approved\ldots\\
From the fear of being humiliated\ldots\\
From the fear of being despised\ldots\\
From the fear of suffering rebukes\ldots\\
From the fear of being calumniated\ldots\\
From the fear of being forgotten\ldots\\
From the fear of being ridiculed\ldots\\
From the fear of being wronged\ldots\\
From the fear of being suspected\ldots

That others may be loved more than I, \respond{Jesus, grant me the grace to desire it}.

That others may be esteemed more than I\ldots\\
That, in the opinion of the world, others may increase and I may decrease\ldots\\
That others may be chosen and I set aside\ldots\\
That others may be praised and I unnoticed\ldots\\
That others may be preferred to me in everything\ldots\\
That others may become holier than I, provided that I may become as holy as I should\ldots\\

\prayertitle{Litany for Life}
\label{prayer:litany_for_life}
\note{Based on 1 Corinthians 12:31-13:8.}
Lord, love is patient.
Give to the mother who is tempted to abort her child the patience to endure the suffering that will bring forth new life.

Lord, love is kind.
Give to the new father whose friends tell him to abort his child the gentleness, compassion, and courage to support his wife and child, protect them from all that could harm them, and sustain them against selfishness and hate.

Lord, love is not jealous.
Remove from all human hearts the temptation to trade human life for advantage, convenience, or personal benefit.
Deliver us from the expediency that values personal gain and pleasure over the dignity of human life.

Lord, love is not pompous.
Deliver us from the arrogance that sees our needs or wants as superior to the rights of others.
Help us to see all our brothers and sisters as worthy of all of our love.

Lord, love is not inflated.
Grant us a share in the Humility of Your Son, Who sought not to be served, but to serve. Help us to see in every human life, rich or poor, young or old, guilty or innocent, a reflection of Your Image and Likeness. 

Lord, love is not rude.
Implant a spirit of gentle compassion in the hearts of each of Your sons and daughters, Lord, that no person may ever be treated as less than the child of God which You have made them, through the Paschal Death and Resurrection of Your only-begotten Son.

Lord, love does not seek its own interests.
Give to all who govern us, Lord, a generous spirit, that our country may not so much seek to be great as to be good, to be rich in possessions as to be rich in mercy, or to be renowned as to be renowned for justice and truth for all.

Lord, love is not quick-tempered.
Grant that by our prudence and patience we might learn to live that sacrificial love by which Your Son died for us on the Cross, that all men and women might know our kindness and willingness to love them unto death after the model of our Lord and Savior.

Lord, love does not brood over injury.
Give us the grace of mercy, Lord, that like Your Son we might forgive those who sin against us, seeking only their redemption and eternal happiness.
Forgive the abortionist who takes the life of an unborn child.
Move his heart, grant him the grace of repentance, and give us a full share in Your Mercy.

Lord, love does not rejoice over wrongdoing.
Help us to seek only the redemption of wrongdoers, Lord, and remove from our hearts all desire for vengeance and hate.
Help us to desire not revenge, even for the horrors of abortion, but the repentance and happiness of all Your children.

Lord, love rejoices with the truth.
Implant deep within our hearts a sense of the joy of the Gospel of Life, and make us joy-filled evangelists of Your great gift of life.

Lord, love bears all things.
When we are insulted or reviled for the sake of the Gospel of Life, give us the courage and the innocence of the children of God.
Help us, Lord, to suffer for the sake of Your Truth, and never to seek our own good, even in the good work we do.

Lord, love believes all things.
Deliver us from every temptation to despair, Lord. When we are discouraged, give us the grace to trust in Your Mercy and to know that Your Love is ever victorious, even in the face of darkness, death, and hate.

Lord, love hopes all things.
As we trust in Your infinite Love, O Lord, give us the trust that comes from the Gospel, and help us to cling to that sure and certain hope that for those who love God all things come to good.

Lord, love endures all things.
In the face of death, destruction, and a culture of death, never let us lose sight of the beauty of the face of Your only-begotten Son, Our Lord, Who suffered the torments of His Passion and Death for the sake of our sins.
Let us trust that through His Passion we will have the strength to do Your Will and to carry each cross that comes our way for the Glory of God and the love of His little ones.

Lord, love never fails.
When the crusade for life seems unending and our latest initiatives have failed, when our hearts are filled with sadness or anger or fear, come to our aid, O Lord, and give us the assurance that You are ever with us, that Your Mercies will not end, and that You, our Creator and our God, will bring victory to all who seek to love as You have commanded them.

\newpage