% TODO Add group prayers. Some prayers suitable for groups are indulgenced (see, e.g., Grant 25).

\prayersection{For Particular Occasions}
\indulgencedprayertitle{\foreign{Adsumus}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering prayer of supplication such as this one when starting and completing work, which is said before a meeting dealing with matters of common interest.}
We have come, O Lord, Holy Spirit, we have come before You, hampered indeed by our many and grievous sins, but for a special purpose gathered together in Your Name.
Come to us, be with us, and enter our hearts.
Teach us what we are to do and what ought to concern us;
show us what we must accomplish, in order that, with Your help, we may be able to please You in all things.
May You alone be the author and the finisher of our judgments, Who alone with God the Father and His Son possess a glorious Name.
Do not allow us to disturb the order of justice, You Who love equity above all things.
Let not ignorance draw us into devious paths.
Let not partiality sway our minds or respect of riches or persons pervert our judgment.
But unite our hearts to You by the gift of Your Grace alone, that we may be one in You and never forsake the truth;
as we are gathered together in Your Name, so may we in all things hold fast to justice tempered by mercy, that in this life our judgment may never be at variance with You and in the life to come we may attain to everlasting rewards for deeds well done.
Amen.

\prayertitle{Prayer of a Couple on the Anniversary of Marriage}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/anniversary-of-marriage.cfm Text adapted from the English translation of The Order of Celebrating Matrimony © 2013, International Commission on English in the Liturgy Corporation. All rights reserved. This form is not approved for liturgical use.
We praise You, O God, we bless You, Creator of all things, Who in the beginning made man and woman that they might form a communion of life and love.

We also give You thanks for graciously blessing our family life so that it might present an Image of Christ's union with the Church.

Therefore look with kindness upon us today, and as You have sustained our communion amid joys and struggles, renew our Marriage covenant each day, increase our charity, and strengthen in us the bond of peace, so that we may for ever enjoy Your blessing.
Through Christ our Lord. Amen.

\prayertitle{For Babies About to Be Born}
\label{prayer:babies_about_to_be_born}
Heavenly Father, from the moment these children were conceived, You knew their names.
In the silent first hours of their lives, as cells divided and their living flesh quickened, Your Love breathed deep within and they began to grow in Your Image and Likeness.
May our prayers be accompanied by choirs of angels as we await their births.
We ask this through Your Child Who was formed in the Virgin's womb and Who lived and died for us, Lord, forever and ever. Amen.

\prayertitle{Thanksgiving for a Newborn or Newly Adopted Young Child}
\label{prayer:thanksgiving_newborn}
God, our Creator, cherish this child.
Jesus, our Savior; protect him/her.
Holy Spirit, our comforter, strengthen him/her.

Source of all blessings, protector of infants, look with favor on this child, \insertname.

Hold him/her gently in your hands.
When he/she is reborn of water and the Holy Spirit, bring him/her into the Church, there to share in your kingdom and with us to bless Your Name forever.
We ask this through Christ our Lord.

\response Amen.

\instruction{The parents trace the sign of the cross on the child's forehead.}

\insertname, may the Lord Jesus, Who loved children, bless you and keep you in His love, now and forever.

\response Amen.

\prayertitle{Prayer on Bringing a Child into the Home}
\label{prayer:bringing_child_into_home}
Good Lord, You have tenderly loved us, and given us this home and good friends.
May we make a true home for this child, where he/she will learn trust in us and in You.
May his/her brothers and sisters rejoice in their own growing up as they help to care for this child.
We ask this through Christ our Lord.

\response Amen.

\prayertitle{Prayer Before Travel}
% https://orthodoxprayer.org/OtherPrayers.html#travel
Lord Jesus, You traveled with the two disciples after the resurrection and set their hearts on fire with Your Grace.
Travel also with me and gladden my heart with Your Presence.
I know, Lord, that I am a pilgrim on this earth, seeking the citizenship which is in heaven.
During my journey surround me with Your holy angels and keep me safe from seen and unseen dangers.
Grant that I may carry out my plans and fulfill my expectations according to Your Will.
Help me to see the beauty of creation and to comprehend the wonder of Your Truth in all things.
For You are the Way, the Truth, and the Life, and to You I give thanks, praise, and glory forever.
Amen.

\prayertitle{For Travelers}
\label{prayer:travelers}
O Almighty and merciful God, Who has commissioned Your angels to guide and protect us, command them to be our assiduous companions from our setting out until our return;
to clothe us with their invisible protection;
to keep from us all danger of collision, of fire, of explosion, of fall and bruises, and finally, having preserved us from all evil, and especially from sin, to guide us to our heavenly home.
Through Jesus Christ, our Lord. Amen.

\prayertitle{For a Safe Flight}
Dear God, please watch over me as I fly out today.
May Your Hand be on the pilot and crew, Your Strength be in the engineers that prepare the plane, and Your Wisdom over the control teams on the ground.

I choose to trust in You, and give You my fears and anxieties.
May I find peace as I travel.
Take my heart on a journey of trust and hope as I look out over the beautiful world You have made.

I travel with You.
Calm me and cover me,
Amen.

\prayertitle{For Times of Trouble}
\label{prayer:times_of_trouble}
Praised be God, the Father of our Lord Jesus Christ, the Father of mercies and the God of all consolation, Who comforts us in all our afflictions.

May God, the source of all patience and encouragement, enable us to live in perfect harmony with one another according to the Spirit of Christ Jesus.

\response Amen.

May the Lord make us overflow with love for one another and for all.
May God strengthen our hearts.

\response Amen

God of all our days: like a parent you forgive us, and like a child you love us.
May we love and forgive one another.

\prayertitle{In Time of Difficulty}
% https://orthodoxprayer.org/OtherPrayers.html#trouble
Almighty God, the Father of mercies and God of all comfort, come to my help and deliver me from this difficulty that besets me.
I believe, Lord, that all trials of life are under Your care and that all things work for the good of those who love You.
Take away from me fear, anxiety, and distress.
Help me to face and endure my difficulty with faith, courage, and wisdom.
Grant that this trial may bring me closer to You, for You are my rock and refuge, my comfort and hope, my delight and joy.
I trust in Your Love and Compassion.
Blessed is Your Name, Father, Son and Holy Spirit, now and forever. Amen.

\prayertitle{In Time of Need}
% https://orthodoxprayer.org/OtherPrayers.html#trouble
O God, our help in time of need, Who are just and merciful, and Who inclines to the supplications of His people:
Look down upon me, have mercy on me,and deliver me from the trouble that now besets me.
Deal with us not according to our iniquities, but according to Your manifold Mercies, for we are the works of Your Hands, and You know our weaknesses.
I pray to You to grant me Your divine helping Grace, and endow me with patience and strength to endure my hardships with complete submission to Your Will.
Only You know our misery and sufferings, and to You, our only hope and refuge, I flee for relief and comfort, trusting in Your infinite Love and Compassion, that in due time, when You know best, You will deliver me from this trouble, and turn my distress into comfort.
We then shall rejoice in Your Mercy, and exalt and praise Your Holy Name, O Father, Son, and Holy Spirit, both now and forever and to the ages of ages.
Amen.

\prayertitle{Thanksgiving After Trouble}
% https://orthodoxprayer.org/OtherPrayers.html
Almighty and merciful God, I most humbly and heartily thank Your divine Majesty for Your loving Kindness and tender Mercies, that You have heard my humble prayer, and graciously granted me deliverance from my trouble and misery.
I pray to You to continue granting Your helping Grace, that I may lead a life pleasing to You, that I may continually offer to You a sacrifice of praise and thanksgiving, O Father, Son, and Holy Spirit.
Amen.

\prayertitle{Prayer of a Sick Person}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Jesus Christ, my Lord and Savior, You became man and died on the cross for our salvation.
You healed people of sickness and affliction through Your Love and Compassion.
Visit me, Lord, and grant me strength to bear this sickness with which I am afflicted, with patience, submission to Your Will, and trust in Your loving care.
I pray that You will bless the means used for my recovery and those who administer them.
Grant that my sickness may be to my spiritual benefit and that I may live the rest of my life more faithfully according to Your Will.
For You are the source of life and healing and to You I give praise and glory, now and forever.
Amen.

\prayertitle{Prayer for a Sick Person}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Heavenly Father, physician of our souls and bodies, Who have sent Your only-begotten Son and our Lord Jesus Christ to heal every sickness and infirmity, visit and heal also Your servant \insertname from all physical and spiritual ailments through the grace of Your Christ.
Grant him/her patience in this sickness, strength of body and spirit, and recovery of health.
Lord, You have taught us through Your Word to pray for each other that we may be healed.
I pray, heal Your servant \insertname and grant to him/her the gift of complete health.
For You are the source of healing and to You I give glory, Father, Son, and Holy Spirit.
Amen.

\prayertitle{Prayer to St. Peregrine for Those Sick with Cancer}
O great St. Peregrine, you have been called ``The Mighty,'' ``The Wonder-Worker,'' because of the numerous miracles which you have obtained from God for those who have had recourse to you.
For so many years you bore in your own flesh this cancerous disease that destroys the very fiber of our being, and who had recourse to the source of all grace when the power of man could do no more.
You were favored with the vision of Jesus coming down from His Cross to heal your affliction.
Ask of God and Our Lady, the cure of the sick whom we entrust to you: \insertname.
Aided in this way by your powerful intercession, we shall sing to God, now and for all eternity, a song of gratitude for His great Goodness and Mercy.
Amen.

\prayertitle{Prayer to St. Peregrine for Help with Cancer}
St. Peregrine, whom Holy Mother Church has declared Patron of those suffering from cancer, I confidently turn to you for help in my present sickness.
I beg your kind intercession.
Ask God to relieve me of this sickness, if it be His Holy Will.
Plead with the Blessed Virgin Mary, the Mother of Sorrows, whom you loved so tenderly and in union with whom you have suffered the pains of cancer, that she may help me with her powerful prayers and loving consolation.

But if it should be God's Holy Will that I bear this sickness, obtain for me courage and strength to accept these trials from the loving Hand of God with patience and resignation, because He knows what is best for the salvation of my soul.
St. Peregrine, be my friend and patron.
Help me to imitate you in accepting suffering, and to unite myself with Jesus Crucified and the Mother of Sorrows, as you did.
I offer my pains to God with all the love of my heart, for His glory and the salvation of souls, especially my own.
Amen.

\prayertitle{Prayer after an Operation}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Holy Father, the only true Physician of our souls and bodies, who cast down and lift up, accept me as I come in all humility to glorify You and thank You for preserving, by Your Grace, Your servant \insertname through his/her recent operation.
We thank You for blessing the attending physicians and the means employed for his/her cure, and for restoring him/her safe and sound to his/her family and Church, having fended off every danger against his/her body and soul.
Raise him/her speedily, we pray You, from the bed of illness on which he/she lies and return him/her to his/her home and peaceful pursuits.
Grant that the suffering of his/her body may avail for the purifying of his/her soul and may lead him/her to return, in thanksgiving, to the works of his/her hands and to Christ Jesus, the Physician of soul and body.
Through the prayers of our Holy Fathers, Lord Jesus Christ have mercy on us and save us.
Amen.

\prayertitle{Thanksgiving after Recovery}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Almighty God and heavenly Father, You are the fountain of life and healing.
I bless Your Holy Name and offer to You thanks for having delivered me from sickness and restored me to health.
Grant me Your eternal Grace, I pray, that I may live a new life in true obedience to You.
Guide me to do Your Will in all things, devoting my life to Your service.
Thus living for You may I be found worthy of Your kingdom, where You dwell in glory with Your Son and Your Holy Spirit forever.
Amen.

\prayertitle{Prayer for the Terminally Ill}
% https://orthodoxprayer.org/OtherPrayers.html#illness
Lord Jesus Christ, Who suffered and died for our sins that we may live, if during our life we have sinned in word, deed, or thought forgive us in Your Goodness and Love.
All our hope we put in You;
protect your servant \insertname from all evil.
We submit to Your Will and into Your Hands we commend our souls and bodies.
For a Christian end to our lives, peaceful, without shame and suffering, and for a good account before the awesome judgment seat of Christ, we pray to You O Lord.
Bless us, be merciful to us, and grant us life eternal.
Amen.

\prayertitle{For All about to Die}
% http://www.usccb.org/issues-and-action/human-life-and-dignity/assisted-suicide/to-live-each-day/upload/prayer-resources.pdf
Lord Jesus Christ, as You stood by the bed of good Saint Joseph and gently led him home to heaven, so shepherd every soul about to die to a paradise of perfect peace.
Let the tears we shed upon their passing stand witness to our love for them and the depth of our thanksgiving for the gift of their lives and the grace of a good death.
For You are Lord, forever and ever.
Amen.

\prayertitle{Prayer of Commendation}
% http://www.usccb.org/prayer-and-worship/bereavement-and-funerals/prayers-for-death-and-dying.cfm
\note{Said as the time of death approaches.}
Go forth, Christian soul, from this world in the Name of God the almighty Father, Who created you, in the Name of Jesus Christ, Son of the living God, Who suffered for you, in the Name of the Holy Spirit, Who was poured out upon you, go forth, faithful Christian.

May you live in peace this day, may your home be with God in Zion, with Mary, the Virgin Mother of God, with Joseph, and all the Angels and Saints.

\prayertitle{Aspiration of the Dying}
% https://www.ourcatholicprayers.com/aspirations-for-the-dying.html. Also from the Laudate app under ``Aspirations for the Dying''
Good Jesus, give me a deep love for You, that nothing may be too hard for me to bear from You.

You know Lord, that I am all weakness; teach me to bear my cross.
Bear it for me, bear it in me.

O Good Jesus, my God and my All, keep me ever near You, let nothing for a moment separate me from You

Good Jesus, to You I flee;
hide me in Your sacred Side.

O Good Jesus, shelter me from the evil one, shed Your dew upon me to calm my soul, and dwell in me fully, that I may wholly love You.

Good Jesus, Who has borne so patiently with me;
make me wholly patient for love of You.

Good Jesus, lead me that I may follow You; hold me that I may cling fast to You;
teach me, that I may choose You alone; keep me that I may be Yours for ever.

\prayertitle{Prayer of Those in Their Last Agony}
% https://www.ourcatholicprayers.com/aspirations-for-the-dying.html. Also from the Laudate app under ``Aspirations for the Dying''
Jesus, Mary, and Joseph, I give you my heart and my soul.
Jesus, Mary, and Joseph, assist me in my last agony.
Jesus, Mary, and Joseph, may I breathe forth my soul in peace with you.

Into Your Hands, O Lord, I commend my spirit.
O Lord Jesus Christ, receive my spirit.

Holy Mary, pray for me.
O Mary, mother of grace, mother of mercy, protect me from the enemy, and receive me at the hour of death.

St. Joseph, pray for me.
St. Joseph, with the Blessed Virgin, your Spouse, open to me the bosom of divine Mercy.

\prayertitle{Prayer for a Stillborn Child}
% https://www.catholicdoors.com/prayers/english5/p03282.htm
Lord God, ever caring and gentle, we commit to Your Love this little one, quickened to life for so short a time.
Enfold him/her in eternal life.
We pray for his/her parents who are saddened by the loss of their child.
Give them courage and help them in their pain and grief.
May they all meet one day in the joy and peace of Your Kingdom.
We ask this through Christ our Lord.
Amen.

% Prayers in times of war: http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-troops.cfm

\newpage