\prayersection{Penitential Psalms}
\linkednote{grant9}{A partial indulgence is granted for devoutly reciting any of the penitential psalms, especially in preparation for sacramental confession.}
% http://www.usccb.org/bible/psalms/6
\indulgencedprayertitle{Psalm 6}
Do not reprove me in Your Anger, Lord,
nor punish me in Your Wrath.
Have pity on me, Lord, for I am weak;
heal me, Lord, for my bones are shuddering.
My soul too is shuddering greatly -- and You, Lord, how long?
Turn back, Lord, rescue my soul;
save me because of Your Mercy.

For in death there is no remembrance of You.
Who praises You in Sheol?

I am wearied with sighing;
all night long I drench my bed with tears;
I soak my couch with weeping.
My eyes are dimmed with sorrow, worn out because of all my foes.

Away from me, all who do evil!
The Lord has heard the sound of my weeping.
The Lord has heard my plea;
the Lord will receive my prayer.
My foes will all be disgraced and will shudder greatly;
they will turn back in sudden disgrace.

% http://www.usccb.org/bible/psalms/32
\indulgencedprayertitle{Psalm 32}
Blessed is the one whose fault is removed, whose sin is forgiven.
Blessed is the man to whom the Lord imputes no guilt, in whose spirit is no deceit.

Because I kept silent, my bones wasted away;
I groaned all day long.
For day and night Your Hand was heavy upon me;
my strength withered as in dry summer heat.

Then I declared my sin to You;
my guilt I did not hide.
I said, ``I confess my transgression to the Lord,'' and You took away the guilt of my sin.

Therefore every loyal person should pray to You in time of distress.
Though flood waters threaten, they will never reach Him.
You are my shelter; You guard me from distress;
with joyful shouts of deliverance You surround me.

I will instruct you and show you the way you should walk, give you counsel with my eye upon you.
Do not be like a horse or mule, without understanding;
with bit and bridle their temper is curbed, else they will not come to you.

Many are the sorrows of the wicked one, but mercy surrounds the one who trusts in the Lord.
Be glad in the Lord and rejoice, you righteous;
exult, all you upright of heart.

% http://www.usccb.org/bible/psalms/38
\indulgencedprayertitle{Psalm 38}
Lord, do not punish me in Your Anger;
in Your Wrath do not chastise me!
Your arrows have sunk deep in me;
Your Hand has come down upon me.
There is no wholesomeness in my flesh because of Your Anger;
there is no health in my bones because of my sin.
My iniquities overwhelm me, a burden too heavy for me.

Foul and festering are my sores because of my folly.
I am stooped and deeply bowed;
every day I go about mourning.
My loins burn with fever;
there is no wholesomeness in my flesh.
I am numb and utterly crushed;
I wail with anguish of heart.
My Lord, my deepest yearning is before You;
my groaning is not hidden from You.
My heart shudders, my strength forsakes me;
the very light of my eyes has failed.
Friends and companions shun my disease;
my neighbors stand far off.

Those who seek my life lay snares for me;
they seek my misfortune, they speak of ruin;
they plot treachery every day.

But I am like the deaf, hearing nothing, like the mute, I do not open my mouth;
I am even like someone who does not hear, who has no answer ready.
Lord, it is for You that I wait;
O Lord, my God, You respond.
For I have said that they would gloat over me, exult over me if I stumble.

I am very near to falling;
my wounds are with me always.
I acknowledge my guilt
and grieve over my sin.
My enemies live and grow strong, those who hate me grow numerous fraudulently.
Repaying me evil for good,
accusing me for pursuing good.
Do not forsake me, O Lord;
my God, be not far from me!
Come quickly to help me, my Lord and my salvation!

% http://www.usccb.org/bible/psalms/51
\indulgencedprayertitle{\foreign{Miserere} (Psalm 51)}
Have mercy on me, God, in accord with Your merciful Love;
in Your abundant Compassion blot out my transgressions.
Thoroughly wash away my guilt;
and from my sin cleanse me.
For I know my transgressions;
my sin is always before me.
Against You, You alone have I sinned;
I have done what is evil in Your Eyes;
so that You are just in Your Word, and without reproach in Your Judgment.
Behold, I was born in guilt, in sin my mother conceived me.
Behold, You desire true sincerity;
and secretly You teach me wisdom.
Cleanse me with hyssop, that I may be pure;
wash me, and I will be whiter than snow.
You will let me hear gladness and joy;
the bones You have crushed will rejoice.

Turn away Your Face from my sins;
blot out all my iniquities.
A clean heart create for me, God;
renew within me a steadfast spirit.
Do not drive me from before Your Face, nor take from me Your Holy Spirit.
Restore to me the gladness of Your salvation;
uphold me with a willing spirit.
I will teach the wicked Your ways, that sinners may return to You.
Rescue me from violent bloodshed, God, my saving God, and my tongue will sing joyfully of Your Justice.
Lord, You will open my lips;
and my mouth will proclaim Your praise.
For You do not desire sacrifice or I would give it;
a burnt offering You would not accept.
My sacrifice, O God, is a contrite spirit;
a contrite, humbled heart, O God, You will not scorn.

% http://www.usccb.org/bible/psalms/102
\indulgencedprayertitle{Psalm 102}
Lord, hear my prayer;
let my cry come to You.
Do not hide Your Face from me in the day of my distress.
Turn Your Ear to me;
when I call, answer me quickly.
For my days vanish like smoke;
my bones burn away as in a furnace.
My heart is withered, dried up like grass, too wasted to eat my food.
From my loud groaning I become just skin and bones.
I am like a desert owl, like an owl among the ruins.
I lie awake and moan, like a lone sparrow on the roof.
All day long my enemies taunt me;
in their rage, they make my name a curse.
I eat ashes like bread, mingle my drink with tears.
Because of Your furious Wrath, You lifted me up just to cast me down.
My days are like a lengthening shadow;
I wither like the grass.

But You, Lord, are enthroned forever;
Your Renown is for all generations.
You will again show mercy to Zion;
now is the time for pity;
the appointed time has come.
Its stones are dear to Your servants;
its dust moves them to pity.
The nations shall fear Your Name, Lord,
all the kings of the earth, Your Glory.
Once the Lord has rebuilt Zion and appeared in glory, heeding the plea of the lowly, not scorning their prayer.
Let this be written for the next generation, for a people not yet born, that they may praise the Lord.
``The Lord looked down from the holy heights, viewed the earth from heaven, to attend to the groaning of the prisoners, to release those doomed to die.''
Then the Lord's Name will be declared on Zion, His praise in Jerusalem, when peoples and kingdoms gather to serve the Lord.

He has shattered my strength in mid-course, has cut short my days.
I plead, O my God, do not take me in the midst of my days.
Your years last through all generations.
Of old You laid the earth's foundations;
the heavens are the work of Your Hands.
They perish, but You remain;
they all wear out like a garment;
Like clothing You change them and they are changed, but You are the same, Your years have no end.
May the children of Your servants live on;
may their descendants live in Your Presence.

% http://www.usccb.org/bible/psalms/130
\indulgencedprayertitle{\foreign{De profundis} (Psalm 130)}
Out of the depths I call to You, Lord;
Lord, hear my cry!
May Your Ears be attentive to my cry for mercy.
If You, Lord, keep account of sins, Lord, who can stand?
But with You is forgiveness and so You are revered.

I wait for the Lord, my soul waits and I hope for His word.
My soul looks for the Lord more than sentinels for daybreak.
More than sentinels for daybreak, let Israel hope in the Lord, for with the Lord is mercy, with Him is plenteous redemption, and He will redeem Israel from all its sins.

% http://www.usccb.org/bible/psalms/143
\indulgencedprayertitle{Psalm 143}
Lord, hear my prayer;
in Your Faithfulness listen to my pleading;
answer me in Your Righteousness.
Do not enter into judgment with Your servant;
before You no one can be just.
The enemy has pursued my soul;
he has crushed my life to the ground.
He has made me dwell in darkness like those long dead.
My spirit is faint within me;
my heart despairs.
I remember the days of old;
I ponder all Your deeds;
the works of Your Hands I recall.
I stretch out my hands toward You, my soul to You like a parched land.

Hasten to answer me, Lord;
for my spirit fails me.
Do not hide Your Face from me,
lest I become like those descending to the pit.
In the morning let me hear of Your Mercy, for in You I trust.
Show me the path I should walk, for I entrust my life to You.
Rescue me, Lord, from my foes, for I seek refuge in You.
Teach me to do Your Will, for You are my God.
May Your kind Spirit guide me on ground that is level.
For Your Name's sake, Lord, give me life;
in Your Righteousness lead my soul out of distress.
In Your Mercy put an end to my foes;
all those who are oppressing my soul, for I am Your servant.

% TODO Add gradual psalms (119-133) since they are all indulgenced

\newpage