\documentclass[12pt]{article}

\usepackage{ifxetex, ifluatex}

% From https://tex.stackexchange.com/a/47579/61108
\newif\ifxetexorluatex
\ifxetex
	\xetexorluatextrue
\else
	\ifluatex
		\xetexorluatextrue
	\else
		\xetexorluatexfalse
	\fi
\fi

\ifxetexorluatex
	\usepackage{fontspec}
\else
	\usepackage[utf8]{inputenc}
	\usepackage{graphicx}% for versicle/response characters
\fi

\usepackage{etoolbox}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multicol}
%\usepackage{inconsolata}% URLs don't have line breaks with this
\usepackage{parskip}
\usepackage{wasysym}
%\usepackage[margin=0.5in]{geometry}
%\usepackage{biblatex}
\usepackage[hyphens]{url}% https://tex.stackexchange.com/a/175451/61108
\usepackage[colorlinks=true,urlcolor={red},linkcolor={black}]{hyperref}
\usepackage{comment}
\usepackage{xspace}

% Disable section numbering, but keep section numbers in the table of contents
\makeatletter
\renewcommand\@seccntformat[1]{}
\makeatother

\ifxetexorluatex
	\setmonofont{Consolas}
\fi

\newcommand{\prayersection}[1]{\section{#1}}
\newcommand{\prayertitle}[1]{\subsection{#1}}
\newcommand{\indulgencedprayertitle}[1]{\prayertitle{#1 \protect\kreuz}}

\newcommand{\insertname}{(N\dots)\xspace}

% \emph can detect nested emphasis but I prefer the slanted Computer/Latin Modern font to the italics font.
% The fontspec package, which requires XeLaTeX or LuaLaTeX, provides \emfontdeclare which sets the fonts for nested emphasis.
% If the fontspec package is not available then simply use \textsl for emphasis.
\ifxetexorluatex
	\emfontdeclare{\slshape,\upshape}
	\newcommand{\emphasis}[1]{\emph{#1}}
\else
	\newcommand{\emphasis}[1]{\textsl{#1}}
\fi

\newcommand{\foreign}[1]{\emphasis{#1}}

\newcommand{\note}[1]{{\small{\emphasis{#1}}}\newline}
\newcommand{\linkednote}[2]{\hyperlink{#1}{\note{#2}}}

\newcommand{\instruction}[1]{\emphasis{#1}}

% Unicode versicle character taken from https://unicode-table.com/en/2123/
% Unicode response character taken from https://unicode-table.com/en/211F/
% The fontspec package, for XeLaTeX or LuaLaTeX, is required to use Unicode characters.
\ifxetexorluatex%
	\newcommand{\versicle}{{\setmainfont{Times New Roman}\textbf{℣.}}\xspace}
	\newcommand{\response}{{\setmainfont{Times New Roman}\textbf{℟.}}\xspace}
\else
	% Adapted from https://tex.stackexchange.com/a/498283/61108 for pdfLaTeX
	\makeatletter
	\DeclareRobustCommand{\versicle}{\textbf{\vers@resp{-0.1em}{V}.}\xspace}
	\DeclareRobustCommand{\response}{\textbf{\vers@resp{0pt}{R}.}\xspace}
	
	\newcommand{\vers@resp@sym}{\raisebox{0.2ex}{\rotatebox[origin=c]{-20}{$\m@th\rceil$}}}
	
	\newcommand{\vers@resp}[2]{%
		{\ooalign{\hidewidth\kern#1\vers@resp@sym\hidewidth\cr#2\cr}}%
	}
	\makeatother
\fi

\newcommand{\sectionsign}{%
	\ifxetexorluatex%
		{\setmainfont{Times New Roman}§}%
	\else%
		§
	\fi
}

\newcommand{\degreesign}{%
	\ifxetexorluatex%
		{\setmainfont{Arial}°}%
	\else%
		$^\circ$
	\fi
}

% TODO add prayers from http://www.preces-latinae.org/preces.html
% TODO add prayers from https://www.ourcatholicprayers.com, continuing with prayers from https://www.ourcatholicprayers.com/prayers-for-the-sick.html
% TODO add a few more prayers from http://www.usccb.org/issues-and-action/human-life-and-dignity/assisted-suicide/to-live-each-day/upload/prayer-resources.pdf

% TODO Add citations. Use biblatex? See https://tex.stackexchange.com/questions/13509/biblatex-in-a-nutshell-for-beginners

\begin{document}
\title{\textbf{Prayers}\date{\vspace{-10ex}}}\maketitle
\tableofcontents\newpage

\prayersection{Prayers for Particular Times of the Day}
\indulgencedprayertitle{Morning Prayer (includes \foreign{Actiones nostras})}
% Combined from each of the morning prayers in My Prayer Book (p. 32)
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as \foreign{Actiones nostras} at the beginning and end of the day.}
Father, may all we do today be inspired by You and continue with Your saving help.
By Your guidance may we not fail today, but grant that all our thoughts, words, and activity may be in accord with Your Will.
Cast our darkness from our hearts and send us the light of Your Truth, so that we may be guided by You today and walk in Your Love.
Let our work always begin with Your blessing and through You reach completion.
We ask this through Christ our Lord.
Amen.

\indulgencedprayertitle{\foreign{Domine, Deus omnipotens}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day.}
Lord, God Almighty, You have brought us safely to the beginning of this day.
Defend us today by Your mighty Power, that we may not fall into any sin, but that all our words may so proceed and all our thoughts and actions be so directed, as to be always just in Your Sight.
Through Christ our Lord.
Amen.

\indulgencedprayertitle{Grace Before Meals (\foreign{Benedic, Domine})}
% Text from My Prayer Book p. 26
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of thanksgiving such as this one before and after meals.}
Bless us, O Lord, and these Your gifts which we are about to receive from Your bounty, through Christ Our Lord.
Amen.

\indulgencedprayertitle{Grace After Meals (\foreign{Agimus tibi gratias})}
% Text from My Prayer Book p. 26
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of thanksgiving such as this one before and after meals.}
We give You thanks, Almighty God, for these and all Your blessings;
You live and reign for ever and ever.
Amen.
\newpage
\indulgencedprayertitle{Evening Prayer from the Byzantine Tradition}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Byzantine Tradition.}
In the evening, in the morning, and at noon, we praise You, we bless You,
we give You thanks, and we beg You, Master of the universe, grant that our hearts not yield to evil words but free us from all who try to enslave our souls, because our eyes are turned to You, O Lord, and we have placed our hope in You.
Do not abandon us, O God!
For every glory, honor, and adoration is due to You, Father, Son, and Holy Spirit, now and always and for ever and ever.
Amen.

\prayertitle{Evening Prayer}
Almighty God, we thank You for bringing us safely to the end of this day.
We offer You the work of our hands as a sacrifice before Your Sight.
We make this prayer through Christ our Lord.
Amen.

\prayertitle{Prayer of a Lay Apostle}
\label{prayer:lay_apostle}
Thank You, my God, for the day that is ending, thank You for the coming night.
Bring sleep to the weary, bring repose to those I love, and give me rest until tomorrow.

All was not fine, perfect, and beautiful today.
Give me strength to do better tomorrow.

In this day that is ending I have not been what I should have been.
Make me better, my God, less harsh towards others, more gentle, more patient.
Make me, too, more determined, more demanding of myself, more truthful in speaking, more faithful in my promises, more active in my work, more obedient and more submissive;
let me be cheerful, too, and may tomorrow be a finer, fuller day than this.

Thank You, my God, for the day that is ending, thank You for the coming night.
Bring sleep to the weary, bring repose to those I love, and give me rest until tomorrow.

\prayersection{General Prayers}
\prayertitle{Jesus Prayer}
\label{prayer:Jesus}
Lord Jesus Christ, Son of God, have mercy on me, a sinner.

\prayertitle{The Grail Prayer}
% Given by many sources on the Internet, also listed as a ``Morning Prayer'' in the Laudate app.
Lord Jesus,
I give You my hands to do Your work.
I give You my feet to go Your way.
I give You my eyes to see as You do.
I give You my tongue to speak Your words.
I give You my mind that You may think in me.
I give You my spirit that You may pray in me.
Above all, I give You my heart that You may love in me Your Father and all mankind.
I give You my whole self that You may grow in me, so that it is You, Lord Jesus,
Who live and work and pray in me.

\prayertitle{\foreign{Aufer a me cor lapideum}}
\label{prayer:take_heart_of_stone}
O Lord, take away my heart of stone, my hardened heart, my uncircumcised heart and grant to me a new heart, a heart of flesh, a clean heart!
O You Who purify the heart and love the clean heart, possess my heart and dwell in it, containing it and filling it, higher than my highest and more intimate than my most intimate thoughts.
You Who are the Image of all beauty and the seal of all holiness, seal my heart in Your Image and seal my heart in Your Mercy, O God of my heart and the God of my portion in eternity.
Amen.

\prayertitle{Prayer for Goodness}
% My Prayer Book, p. 104
O Holy Spirit of God, take me as Your disciple.
Guide me, illuminate me, sanctify me.
Bind my hands that they may do no evil;
cover my eyes that they may see it no more;
sanctify my heart that evil may not dwell within me.
Be my guide;
wherever You lead me, I will go;
whatever You forbid me, I will renounce;
and whatever You command me in Your Strength, I will do.
Lead me then to the fullness of Your Truth.
Amen.

\prayertitle{Prayer for Love of God}
% My Prayer Book, p. 90
O great Lord of heaven and earth, infinite good and majesty, You Who have loved men so tenderly, how is it that You are despised by so many human beings?
You have loved me in a special manner and have bestowed many wonderful graces on me.
Yet I, too, have despised You by every sin through which I have turned against Your Law.
I resolve this day to love You with my whole heart and to love nothing unless it can be loved in You.
Grant me this gift of love:
a fervent love that will make me reject the appeal of sinful creatures;
a strong love that will make me conquer all difficulties to please You;
a persevering love that will never be dissolved.
Amen.

\prayertitle{Prayer for Grace}
\label{prayer:grace}
Oh my God, You know my weakness and failings, and that without Your help I can accomplish nothing for the good of souls, my own and others'.
Grant me, therefore, the help of Your Grace.
Grant it according to my particular needs this day.
Enable me to see the task You will set before me in the daily routine of my life, and help me work hard at my appointed tasks.
Teach me to bear patiently all the trials of suffering or failure that may come to me today. Amen.

\prayertitle{\foreign{Domine Iesu, noverim me}}
\label{prayer:noverim_me}
Lord Jesus, let me know myself and know You,
and desire nothing save only You.
Let me hate myself and love You.
Let me do everything for the sake of You.

Let me humble myself and exalt You.
Let me think of nothing except You.
Let me die to myself and live in You.
Let me accept whatever happens as from You.

Let me banish self and follow You,
and ever desire to follow You.
Let me fly from myself and take refuge in You,
that I may deserve to be defended by You.

Let me fear for myself, let me fear You,
and let me be among those who are chosen by You.
Let me distrust myself and put my trust in You.
Let me be willing to obey for the sake of You.

Let me cling to nothing save only to You,
and let me be poor because of You.
Look upon me, that I may love You.
Call me that I may see You,
and forever enjoy You.
Amen.

\prayertitle{Prayer of Resolution}
\label{prayer:resolution}
Adorable Jesus, my Savior and Master, model of all perfection, I resolve --- and will try this day \textemdash{} to imitate Your example, to be like You, mild, humble, chaste, zealous, charitable, and resigned.
I will redouble my efforts to see Your Image in all those I meet and deal with this day, and to be as helpful to them as I would be to You.
I resolve to avoid this day all those sins which I have committed heretofore and which I now sincerely desire to give up forever. Amen.

\prayertitle{\foreign{Pietate tua}}
\label{prayer:pietate_tua}
Of Your Tender Mercy, we beseech You, O Lord, loose the bonds of our sins, and through the intercession of Mary, the blessed and ever-Virgin Mother of God, together with that of Saint Joseph and Your blessed Apostles Peter and Paul, and of all Your Saints, keep us Your servants and our dwelling places in all holiness;
cleanse from sin and endow with virtue all those who are joined to us by kindred, affinity, and friendship;
grant to us peace and safety;
remove far from us our enemies, both visible and invisible;
repress all our carnal desires;
grant us wholesome air;
bestow Your Charity upon our friends and enemies;
guard Your city;
preserve our Pontiff \insertname;
defend all prelates and princes and Your entire Christian people from every adversity.
Let Your blessing be ever upon us, and grant to all the faithful departed rest everlasting.
Amen.

\indulgencedprayertitle{An Act of Faith}
\label{prayer:act_of_faith}
\linkednote{grant28}{A partial indulgence is granted for reciting an Act of Faith, Hope, and Charity.}
O God,
I firmly believe all the truths that You have revealed and that You teach us through Your Church, for You are truth itself and can neither deceive nor be deceived.

\indulgencedprayertitle{An Act of Hope}
\linkednote{grant28}{A partial indulgence is granted for reciting an Act of Faith, Hope, and Charity.}
O God,
I hope with complete trust that You will give me, through the merits of Jesus Christ, all the necessary grace in this world and everlasting life in the world to come, for this is what You have promised and You always keep Your promises.

\indulgencedprayertitle{An Act of Charity}
\linkednote{grant28}{A partial indulgence is granted for reciting an Act of Faith, Hope, and Charity.}
O God,
I love You with my whole heart above all things, because You are infinitely good; and for Your sake I love my neighbor as I love myself.

\indulgencedprayertitle{An Act of Spiritual Communion}
\linkednote{grant8}{A partial indulgence is granted for reciting this prayer.}
My Jesus, I believe that You are in the Blessed Sacrament.
I love You above all things, and I long for You in my soul.
Since I cannot now receive You sacramentally, come at least spiritually into my heart.
As though You have already come, I embrace You and unite myself entirely to You;
never permit me to be separated from You.
Amen.

% Is this indulgenced, too? See above.
\prayertitle{An Act of Spiritual Communion \#2}
% My Prayer Book, pp. 111-112
Jesus, my Savior and my God!
I am not worthy to be before You, for I am a poor sinner;
yet I approach You with confidence, for You have said, ``Come to Me, all you that labor and are heavy-laden, and I will refresh you.''
You will not despise a contrite and humble heart.
I am truly sorry for my sins, because by them I have offended You Who are infinitely good.
Whatever may have been my foolish transgressions in the past, I love You now above all things, and with all my heart.

Come, my Lord, my God, and my all!
Come to me, and let me never again be separated from You by sin.
Teach me Your blessed ways;
help me with Your Grace to imitate Your example;
to practice meekness, humility, charity, and all the virtues of Your Sacred Heart.
My divine Master, my desire is to do Your Will and to love You more and more;
help me that I may be faithful to the end in Your service.
Bless me in life and in death, that I may praise You forever in heaven.
Amen.

\prayertitle{An Act of Humility}
% My Prayer Book, p. 107, which cites "Eleventh-century Missal"
Devoutly kneeling before Your Majesty,
we earnestly pray that, since You see the limits of our human weakness, You would not in anger blame us for our disobedience, but with Your boundless pity cleanse us, teach us, and comfort us;
and since if You do not help us, we cannot do what is well-pleasing in Your Sight, let Your Grace come to help us, that we may live to our own well-being, ever friends with You.

\indulgencedprayertitle{Prayer of the Sanctuary}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Chaldean Tradition.}
Before the tremendous throne of Your Majesty, at the exalted place of Your Divinity, the majestic seat of Your Glory, and the sublime throne of Your Sovereignty, where Your servants the Cherubim continuously sing hymns and where Your glorifiers the Seraphim sing unceasingly the ``Sanctus,'' we bow down with fear, adore with trembling, give thanks, and glorify You without ceasing, at all times, O Lord of the universe, Father, Son, and Holy Spirit, for all ages.

\prayertitle{For the Missions}
% My Prayer Book, p. 262
God of truth, Father, Son, and Holy Spirit, hear our prayer for those who do not know You, that Your Name may be praised among all peoples of the world.
Sustain and inspire Your servants who bring them the Gospel.
Bring fresh vigor to wavering faith; sustain our faith when it is still fragile.
Renew our missionary zeal.
Make us witnesses to Your Goodness, full of love, of strength and of faith, for Your Glory and for the salvation of the world.
Amen.
\newpage
\prayertitle{For the New Evangelization}
\label{prayer:new_evangelization}
Heavenly Father, stir in my soul the desire to renew my faith and deepen my relationship with Your Son, our Lord Jesus Christ, so that I might truly believe in and live the Good News.   
Open my heart to hear the Gospel and grant me the confidence to proclaim the Good News to others.
Pour out Your Spirit, so that I might be strengthened to go forth and witness to the Gospel in my everyday life through my words and actions.  

In moments of hesitation, remind me:
If not me, then who will proclaim the Gospel?
If not now, then when will the Gospel be proclaimed?
If not the truth of the Gospel, then what shall I proclaim?

God, our Father, I pray that through the Holy Spirit I might hear the call of the New Evangelization to deepen my faith, grow in confidence to proclaim the Gospel and boldly witness to the saving Grace of Your Son, Jesus Christ, Who lives and reigns with You, in the unity of the Holy Spirit, one God, for ever and ever.
Amen.

\prayertitle{For the Sick}
% My Prayer Book, p. 262
Father, Your only Son took upon Himself the sufferings and weakness of all mankind; through His passion and cross He taught us how good can be brought out of suffering.
Look upon our brothers and sisters who are ill.
In the midst of illness and pain, may they be united with Christ, Who heals both body and soul; may they know the consolation promised to those who suffer and be fully restored to health.
Amen.

\prayertitle{For Those Who are Suffering}
% My Prayer Book, p. 263
Father, You are the unfailing refuge of those who suffer.
Bring peace and comfort to the sick and the infirm, to the aged and the dying.
Give all those who look after them knowledge, patience, and compassion.
Inspire them with actions which will bring relief, words which will enlighten, and love which will bring comfort.
We commend to You the disheartened, the rebellious, those torn by temptation or tormented by desire, and those wounded or abused by the ill will of men.
Lord, pour out on us Your Spirit of love, understanding, and sacrifice; may we then give effective help to the suffering we meet on our way.
Help us to answer their cry, for it is our own.
Amen.

\prayertitle{For Those with Profound Disabilities}
\label{prayer:profound_disabilities}
Lord Jesus Christ, 
You know the pain of brokenness, You took our weaknesses upon Your Shoulders and bore them to the wood of the cross.
Hear our prayers for our brothers and sisters whose bodies fail them and whose minds are crippled by the ravages of disease.
Implant a love for them deep within our hearts, that we, disfigured and disabled by our sin, may treasure and nurture the gifts of their lives.
May we find You in their weakness and console You in our care for them, for You are Lord forever and ever.
Amen.

\prayertitle{For the Aged}
% My Prayer Book, p. 264
Eternal Father, unchanged down the changing years, be near to those who are aged.
Even though their bodies weaken, grant that their spirit may be strong; may they bear weariness and affliction with patience, and, at the end, meet death with serenity.
Amen.

\prayertitle{Prayer to Overcome Indifference}
\label{prayer:indifference}
All too often, Lord, we turn away from the world's many problems, which seem too big, too complex, or too far away.
Forgive us our indifference.

It is easier, Lord, to see only what is around us:
our lives, our homes, our challenges.
Forgive us our isolation.

Help us to see with Your Eyes:
eyes which notice one another and help us understand.

Help us to dream Your dream:
of communities that reach out and dialogue and where diverse people creatively cooperate.

Help us to be people of solidarity and action, so moved by prayer, encounter, and understanding that peace can become a reality.
Amen.

\prayertitle{For the Poor}
\label{prayer:poor}
God of Justice, open our eyes to see You in the face of the poor.
Open our ears to hear You in the cries of the exploited.
Open our mouths to defend You in the public squares as well as in private deeds.
Remind us that what we do to the least ones, we do to You.
Amen.

\prayertitle{For the Marginalized}
\label{prayer:marginalized}
Lord, may those who are deprived of their human needs, and their human rights, be given the dignity which You confer on all Your people.
Change our hearts and move us to love as the Image of Christ those who are forgotten or thrown away, and especially the poor, the sick, and the aged.
May Christ lead us to all who are lonely or afraid: teenagers on the street, old people in nursing homes, prisoners with no one to visit them, and all whom the world has forgotten.
May we cherish the gifts God has given those who are mentally disabled,
and in their lives hear the Voice of our loving God.
May we value, as a priceless gift from God, each human life of all who are forgotten or cast off.

\prayertitle{Prayer to End Trafficking}
\label{prayer:trafficking}
Loving Father, we seek Your divine protection for all who are exploited and enslaved.
For those forced into labor, trafficked into sexual slavery, and denied freedom,
we beseech You to release them from their chains.
Grant them protection, safety, and empowerment.
Restore their dignity and provide them a new beginning.
Show us how we might end exploitation by addressing its causes.
Help us reach out in support of victims and survivors of human trafficking.
Make us instruments of Your Spirit for their liberation.
For this we pray through our Lord Jesus Christ, Who lives and reigns with You in the unity of the Holy Spirit, one God, forever and ever.
Amen.

\prayertitle{For Healing Victims of Abuse}
\label{prayer:healing_victims_abuse}
God of endless love, ever caring, ever strong, always present, always just:
You gave Your only Son to save us by the blood of His cross.

Gentle Jesus, shepherd of peace, join to Your own suffering the pain of all who have been hurt in body, mind, and spirit by those who betrayed the trust placed in them.

Hear the cries of our brothers and sisters who have been gravely harmed, and the cries of those who love them.
Soothe their restless hearts with hope, steady their shaken spirits with faith.
Grant them justice for their cause, enlightened by Your Truth.

Holy Spirit, comforter of hearts, heal Your people's wounds and transform brokenness into wholeness.
Grant us the courage and wisdom, humility and grace, to act with justice.
Breathe wisdom into our prayers and labors.
Grant that all harmed by abuse may find peace in justice.
We ask this through Christ, our Lord. Amen.

\prayertitle{For Charity in Truth}
\label{prayer:charity_truth}
Father, Your Truth is made known in Your Word.
Guide us to seek the truth of the human person.
Teach us the way to love because You are Love.

Jesus, You embody Love and Truth.
Help us to recognize Your Face in the poor.
Enable us to live out our vocation to bring love and justice to Your people.

Holy Spirit, You inspire us to transform our world.
Empower us to seek the common good for all persons.
Give us a spirit of solidarity and make us one human family.

We ask this through Christ our Lord. Amen.

\indulgencedprayertitle{For the Unity of Christians (\foreign{Omnipotens et misericors Deus})}
\linkednote{grant11}{A partial indulgence is granted for devoutly reciting this prayer.}
Almighty and merciful God, Who wished to gather the scattered nations into one people
through Your Son, grant that those who glory in the name of Christians may put aside
division and become one in truth and charity, and that all men may be illumined by the
true faith and brought together into the fraternal communion of one Church.
Through Christ our Lord. Amen.

\prayertitle{For the Unity of Christians \#2}
% My Prayer Book, p. 261
God our Father, bring the hearts of all believers together in praise of You and in seeking renewal and reconciliation.
May the divisions between Christians be overcome.
Make us one in faith and love as we walk with Christ to the joy of Your eternal kingdom.
Amen.

\prayertitle{Prayer to Live the Gospel}
Loving Father, open our hearts to hidden realities:
Your Love for all people,
Your Presence in the community,
Your call to justice and peace.
May the sacraments stir in us
that same love for those with whom we worship and all members of our human family.

Christ Jesus, help us to imitate Your example:
healing the sick,
welcoming the stranger,
assisting the poor and vulnerable.
May the sacraments remind us
of Your Love and Self-giving,
which we strive to imitate.

Holy Spirit, make visible to our eyes what is invisible:
Your call to Your people,
Your summons to live our faith daily
as witnesses of justice and peace.
May the sacraments move us to engage in love-inspired action that transforms us and the world.
Amen.

\indulgencedprayertitle{\foreign{Retribuere dignare, Domine}}
\linkednote{grant24}{A partial indulgence is granted for devoutly reciting this prayer.}
May it please You, O Lord, to reward with eternal life all those who do good to us for Your Name's sake. Amen.

\indulgencedprayertitle{\foreign{Veni, Sancte Spiritus}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Come, Holy Spirit, fill the hearts of Your faithful and enkindle in them the fire of Your Love.

\indulgencedprayertitle{\foreign{Veni, Creator}}
\linkednote{grant26}{A plenary indulgence is granted for devoutly assisting in the recitation or solemn singing of this prayer on the first day of the year or on the solemnity of Pentecost.
A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Come, Holy Spirit, Creator blest,
and in our souls take up Thy rest;
come with Thy Grace and heavenly aid
to fill the hearts which Thou hast made.

O comforter, to Thee we cry,
O heavenly Gift of God Most High,
O Fount of Life and Fire of Love,
and sweet anointing from above.

Thou in Thy sevenfold gifts are known;
Thou, Finger of God's Hand we own;
Thou, promise of the Father, Thou
Who dost the tongue with power imbue.

Kindle our sense from above,
and make our hearts o'erflow with love;
with patience firm and virtue high
the weakness of our flesh supply.

Far from us drive the foe we dread,
and grant us Thy Peace instead;
so shall we not, with Thee for guide,
turn from the path of life aside.

Oh, may Thy Grace on us bestow
the Father and the Son to know;
and Thee, through endless times confessed,
of both the eternal Spirit blest.

Now to the Father and the Son,
Who rose from death, be glory given,
with Thou, O Holy Comforter,
henceforth by all in earth and heaven.
Amen.

\prayertitle{Serenity Prayer}
God, grant me the serenity to accept the things I cannot change,
courage to change the things I can,
and wisdom to know the difference.

\prayertitle{Prayer of Thanksgiving}
% Combined multiple prayers from My Prayer Book, pp. 248-249
Father of all gifts, we praise You, the source of all we have and are.
Teach us to acknowledge always the good things Your infinite Love has given us.
Help us to love You with all our hearts and all our strength as our expression of thanksgiving for Your many blessings.
Fill our hearts with this spirit of gratitude.

Father of mercy, we thank You for Your kindness and ask You to free us from all evil that we may serve You with generous hearts and in happiness all our days.
Make us always aware of Your mercies that with truly thankful hearts, we may make known Your praise by giving wholeheartedly of ourselves, and by true holiness of lives all honor and glory will be Yours throughout all ages.

Almighty God, Father of all mercies, we Your unworthy servants give You humble thanks for all Your Goodness and loving kindness to us and to all men, particularly our families, friends, and loved ones.
We bless You for our creation and all the blessings of this life, but above all, for Your incomparable and undying love in the redemption of the world by Your Son, our Lord and Savior Jesus Christ.
Amen.

\indulgencedprayertitle{\foreign{Te Deum}}
\linkednote{grant26}{A plenary indulgence is granted for devoutly assisting in the recitation or solemn singing of this prayer on the final day of the year.
A partial indulgence is granted for devoutly offering a prayer of thanksgiving such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
% My Prayer Book, pp. 250-251
O God, we praise You, and acknowledge You to be the supreme Lord.
Everlasting Father, all the earth worships You.
All the angels, the heavens and all angelic powers, all the cherubim and seraphim, continually cry to You:
Holy, holy, holy, Lord God of Hosts!
Heaven and earth are full of the majesty of Your Glory.
The glorious choir of the apostles, the wonderful company of prophets, the white-robed army of martyrs, praise You.
Holy Church throughout the world acknowledges You:
the Father of infinite majesty;
Your adorable, true, and only Son;
also the Holy Spirit, the Comforter.

O Christ, You are the King of Glory!
You are the everlasting Son of the Father.
When You took it upon Yourself to deliver man, You did not disdain the Virgin's womb.
Having overcome the sting of death, You opened the kingdom of heaven to all believers.
You sit at the right Hand of God in the Glory of the Father.
We believe that You will come to be our Judge.
We therefore beg You to help Your servants whom You have redeemed with Your Precious Blood.
Let them be numbered with Your saints in everlasting glory.
Save Your people, O Lord, and bless Your inheritance!
Govern them, and raise them up forever.
Every day we thank You.
And we praise Your Name forever;
yes, forever and ever.

O Lord, deign to keep us from sin this day.
Have mercy on us, O Lord, have mercy on us.
Let Your Mercy, O Lord, be upon us, for we have hoped in You.
O Lord, in You I have put my trust;
let me never be put to shame.
\newpage
\indulgencedprayertitle{Thanksgiving for the Church}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Armenian Tradition.}
We thank You, Almighty Father, for having prepared the holy Church for us as a haven
of rest, a temple of holiness, where Your Holy Trinity is glorified. Alleluia.

We thank You, Christ our King, for having given us life through Your vivifying Body
and Your holy Blood; grant us expiation and great mercy. Alleluia.

We thank You, true Spirit, for having renewed the holy Church; preserve her immaculate, by means of faith in the Trinity, now and forever. Alleluia.

We thank You, O Christ our God, for having given us such a Food of goodness for
holiness of life.
By means of it preserve us holy and immaculate by living in us with Your divine care.
Lead us to the pastures of Your holy Will, O Effecter of good; by means of it fortify us against every snare of the calumniator.
Make us worthy to listen to Your Voice alone, to follow only You, true and victorious Shepherd, and to receive from You the place You prepared for us in Your heavenly kingdom, O God and Lord Jesus Christ our Savior, Who are blessed with the Father and Your Holy Spirit, now and always for ever and ever.
Amen.

\prayertitle{Prayer for Peace}
% Combined from multiple prayers in My Prayer Book, pp. 254-255
God, Creator of the world, You established the order which governs all ages.
Hear our prayer and give us peace in our time that we may rejoice in Your Mercy and praise You without end.

God of perfect peace, neither violence nor cruelty can be part of You;
bring peace into the world by bringing Your Peace into the hearts of all men throughout the world.

May those who are at peace with one another hold fast to the good will that unites them.
May those who are enemies forget their hatred and be healed.
Help us to turn away from sin, and to follow You in love and service.

God our Father, You reveal that those who work for peace will be called Your sons.
Help us to work without ceasing for that justice which brings true and everlasting peace.

\prayertitle{A Family's Prayer for World Peace}
% My Prayer Book, pp. 255-256
Lord Jesus Christ, Who said to Your apostles:
``Peace I leave with you, My peace I give to you;
not as the world gives, do I give to you,''
regard not our sins but Your merits.
Grant to all Your servants that they, whom the almighty Father has created and governs, and whom You have redeemed by Your precious Blood and destined for everlasting life, may love one another with all their hearts for Your sake and may be made one in spirit and rejoice in Your perpetual peace.

Lord Jesus Christ, concerning Whom the prophet has said:
``And all kings of the earth shall adore Him, all nations shall serve Him,''
extend Your reign over the whole human race.
Send upon all men the light of Your faith, deliver them from all the snares and bonds of passion and direct them to heavenly things.

Graciously grant that states and nations may be united through Your holy Church and through the intercession of the blessed virgin Mary, queen of peace, that they may serve You in all humility;
and that all tongues and peoples may form one great choir to praise You King and Ruler of the nations, Prince of Peace, immortal King of ages.
Amen.

\prayertitle{For Civic Leaders}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-civic-leaders.cfm which cites Catholic Household Blessings and Prayers book
God our Father, You guide everything in wisdom and love.
Accept the prayers we offer for our nation.
In Your Goodness, watch over those in authority so that people everywhere may enjoy freedom, security, and peace.
We ask this through Christ our Lord.
Amen.

\prayertitle{Prayer for Basic Rights}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-basic-rights.cfm which cites Being Neighbor: The Catechism and Social Justice, USCCB, April 1998
Lord of Wisdom, awaken us to our duty to care for the basic needs of all people.
Strengthen with hope people denied their human rights and freedoms.
Provide us all with the voice to cry out for justice for the poor and the oppressed.
Amen.

\prayertitle{Prayer in Times of Seeking God's Will}
% Partially from http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-in-times-of-seeking-the-will-of-god.cfm
Hear, O Lord, the sound of my call;
have pity on me, and answer me.
Of You my heart speaks;
You my glance seeks;
Your Presence, O Lord, I seek.
Hide not Your Face from me; 
do not in anger repel Your servant.
You are my helper: cast me not off;
forsake me not, O God my savior.

\prayertitle{For a Happy Death}
% My Prayer Book, p. 270
Lord Jesus, by Your agony and death, deliver me from a sudden and unexpected death.
I humbly beseech You to never let me die unexpectedly and pass from this life without the Sacraments.
Jesus, my Lord, by all Your labors and sorrows, by Your precious Blood and most holy Wounds, and by Your words on the cross:
``My God, my God, why have You forsaken me?''
and again:
``Father, into Your Hands I commend my spirit'',
I beseech You to save me from an unexpected death.
Give me, most merciful Jesus, time for penance;
and pray that I may pass from this life happily into Your Grace, that I may love You with my whole heart, and bless You for ever and ever.
Amen.

\prayertitle{Act of Resignation to the Divine Will}
% My Prayer Book, p. 270
O Lord, my God, I, now at this moment, readily and willingly accept at Your Hand whatever kind of death it may please You to send me, with all its pains, penalties, and sorrows.
Amen.

\prayertitle{Self-Dedication to Jesus Christ}
% My Prayer Book, p. 89
Lord Jesus Christ take all my freedom, my memory, my understanding, and my will.
All that I have and cherish You have given me.
I surrender it all to be guided by Your Will.
Your Grace and Your Love are wealth enough for me.
Give me these, Lord Jesus, and I ask for nothing more.

\prayertitle{The Lord's Prayer}
Our Father, Who art in heaven, hallowed be Thy Name.
Thy Will be done on earth as it is in heaven.
Give us this day our daily bread;
and forgive us our trespasses, as we forgive those who trespass against us;
and do not let us fall into temptation, but deliver us from evil.

\prayertitle{Gloria (Major Doxology)}
\label{prayer:gloria}
Glory to God in the highest, and peace on earth to men of good will.

We praise You, we bless You, we adore You, we glorify You, we give You thanks for Your great Glory, O Lord God, heavenly King, God the Father Almighty.

O Lord Jesus Christ, only begotten Son, Lord God, Lamb of God, Son of the Father, You Who take away the sins of the world, have mercy on us;
You Who take away the sins of the world, receive our prayer.
You Who sit at the right Hand of the Father, have mercy on us.

For You alone are the Holy One, You alone are the Lord, You alone are the Most High, Jesus Christ, with the Holy Spirit, in the Glory of God the Father.
Amen.

\prayertitle{Glory Be (Minor Doxology)}
\label{prayer:glory_be}
Glory be to the Father, and to the Son, and to the Holy Spirit, as it was in the beginning, is now, and will be forever.
Amen.

\prayertitle{\foreign{Omnipotentia Patris}}
\label{prayer:Omnipotentia_Patris}
Omnipotence of the Father, help my frailty and save me from the depths of misery.
Wisdom of the Son, direct all my thoughts, words, and deeds.
Love of the Holy Spirit, be the source of all the operations of my mind, that they may ever be conformed to God's good pleasure.
Amen.

\prayertitle{\foreign{Adoramus te}}
\label{prayer:adoramus_te}
We adore You, most holy Lord Jesus Christ, here and in all Your churches that are in the whole world, and we bless You;
because by Your Holy Cross You have redeemed the World.
Amen.

\prayertitle{\foreign{Sanctus}}
\label{prayer:sanctus}
Holy, holy, holy, Lord God of hosts.
Heaven and earth are full of Your Glory.
Hosanna in the highest.
Blessed is he who comes in the Name of the Lord.
Hosanna in the highest.

\prayertitle{Short Prayer}
\label{prayer:short}
Lord, help me to remember that nothing is going to happen to me today that You and I together can't handle. Amen.

\prayertitle{The Holy Face}
\label{prayer:holy_face}
O Blessed Face of my kind Savior, by the tender love and piercing sorrow of Our Lady as she beheld You in Your cruel Passion, grant us to share in this intense sorrow and love
so as to fulfill the holy Will of God to the utmost of our ability.
Amen.

\indulgencedprayertitle{\foreign{Angele Dei}}
\linkednote{grant18}{A partial indulgence is granted for devoutly invoking the care of one's guardian angel with this prayer.}
Angel of God, my guardian dear, to whom His love entrusts me here, enlighten and guard, rule and guide me. Amen.

\prayertitle{F\'{a}tima Theological Prayer}
% https://en.wikipedia.org/wiki/F%C3%A1tima_prayers
My God, I believe, I adore, I hope, and I love You. I ask pardon for all those who do not believe in You, do not adore You, do not hope in You, and do not love You.

\prayertitle{F\'{a}tima Trinitarian Prayer}
% https://en.wikipedia.org/wiki/F%C3%A1tima_prayers
Most Holy Trinity - Father, Son, and Holy Spirit - I adore You profoundly, and I offer You the Most Precious Body, Blood, Soul and Divinity of Jesus Christ, present in all the tabernacles of the world, in reparation for the outrages, sacrileges, and indifferences by which He is offended.
And by the infinite merits of His most Sacred Heart and the Immaculate Heart of Mary, I beg the conversion of poor sinners.

\prayertitle{F\'{a}tima Rosary Decade Prayer}
% https://en.wikipedia.org/wiki/F%C3%A1tima_prayers
O my Jesus, forgive us our sins and save us from the fires of Hell.
Lead all souls to heaven, especially those in most need of Your Mercy.

\indulgencedprayertitle{Act of Reparation (\foreign{Iesu dulcissime})}
\linkednote{grant3}{A plenary indulgence is granted for publicly reciting this prayer on the solemnity of the Most Sacred Heart of Jesus;
a partial indulgence is granted for its use in other circumstances.}
Most sweet Jesus, whose overflowing charity for men is requited by so much forgetfulness, negligence, and contempt, behold us prostrate before You, eager to repair by a special act of homage the cruel indifference and injuries to which Your loving Heart is everywhere subjected.
Mindful, alas! that we ourselves have had a share in such great indignities, which we now deplore from the depths of our hearts, we humbly ask Your pardon and declare our readiness to atone by voluntary expiation, not only for our own personal offenses, but also for the sins of those who, straying far from the path of salvation, refuse in their obstinate infidelity to follow You, their Shepherd and Leader, or, renouncing the promises of their Baptism, have cast off the sweet yoke of Your Law.

We are now resolved to expiate each and every deplorable outrage committed against You; we are determined to make amends for the manifold offenses against Christian modesty in indecent dress and behavior, for all the foul seductions laid to ensnare the feet of the innocent, for the frequent violations of Sundays and holydays, and for the shocking blasphemies uttered against You and Your Saints.
We wish also to make amends for the insults to which Your Vicar on earth and Your priests are subjected, for the profanation, by conscious neglect or terrible acts of sacrilege, of the very Sacrament of Your divine Love, and lastly for the public crimes of nations who
resist the rights and teaching authority of the Church which You have founded.

Would that we were able to wash away such abominations with our blood.
We now offer, in reparation for these violations of Your divine Honor, the satisfaction You once made to Your Eternal Father on the cross and which You continue to renew daily on our altars;
we offer it in union with the acts of atonement of Your Virgin Mother and all the saints and of the pious faithful on earth;
and we sincerely promise to make recompense, as far as we can with the help of Your Grace, for all neglect of Your great Love and for the sins we and others have committed in the past.
Henceforth, we will live a life of unswerving faith, of purity of conduct, of perfect observance of the precepts of the Gospel and especially that of charity.
We promise to the best of our power to prevent others from offending You and to bring as many as possible to follow You.

O loving Jesus, through the intercession of the Blessed Virgin Mother, our model in reparation, deign to receive the voluntary offering we make of this act of expiation;
and by the crowning gift of perseverance keep us faithful unto death in our duty and the allegiance we owe to You, that we may all one day come to that happy home, where with the Father and the Holy Spirit You live and reign, for ever and ever. Amen.

\indulgencedprayertitle{Act of Dedication of the Human Race to Christ the King (\foreign{Iesu dulcissime, Redemptor})}
\linkednote{grant2}{A plenary indulgence is granted for publicly reciting this prayer on the solemnity of Our Lord Jesus Christ, King of the Universe (on the last Sunday of Ordinary Time, i.e. the Sunday preceding the first Sunday of Advent);
a partial indulgence is granted for its use in other circumstances.}
Most sweet Jesus, Redeemer of the human race, look down upon us humbly prostrate before You.
We are Yours, and Yours we wish to be;
but to be more surely united with You, behold each one of us freely consecrates himself today to Your Most Sacred Heart.
Many indeed have never known You;
many, too, despising Your precepts, have rejected You.
Have mercy on them all, most merciful Jesus, and draw them to Your Sacred Heart.
Be King, O Lord, not only of the faithful who have never forsaken You, but also of the prodigal children who have abandoned You;
grant that they may quickly return to their Father's house, lest they die of wretchedness and hunger.
Be King of those who are deceived by erroneous opinions, or whom discord keeps aloof, and call them back to the harbor of truth and the unity of faith, so that soon there may be but one flock and one Shepherd.
Grant, O Lord, to Your Church assurance of freedom and immunity from harm;
give tranquility of order to all nations;
make the earth resound from pole to pole with one cry:
Praise to the divine Heart that wrought our salvation;
to it be glory and honor for ever.
Amen.

\newpage

\prayersection{Prayers to the Saints}
\indulgencedprayertitle{\foreign{Maria, Mater gratiae}}
\linkednote{grant17}{A partial indulgence is granted for devoutly addressing the Blessed Virgin Mary with this prayer.}
Mary, Mother of grace and Mother of mercy, shield me from the enemy and receive me at the hour of my death.

\prayertitle{The Hail Mary}
% My Prayer Book, p. 25
Hail Mary, full of grace, the Lord is with you.
Blessed are you among women, and blessed is the fruit of your womb, Jesus.
Holy Mary, Mother of God, pray for us sinners, now and at the hour of our death.
Amen.

\prayertitle{To Our Lady, Help Of Christians}
\label{prayer:Our_Lady_help_of_Christians}
\note{By St. John Bosco}
Most Holy Virgin Mary, Help of Christians, how sweet it is to come to your feet
imploring your perpetual help.
If earthly mothers cease not to remember their children, how can you, the most loving of all mothers, forget me?
Grant then to me, I implore you, your perpetual help in all my necessities, in every sorrow, and especially in all my temptations.
I ask for your unceasing help for all who are now suffering.
Help the weak, cure the sick, convert sinners.
Grant through your intercessions many vocations to the religious life.
Obtain for us, O Mary, Help of Christians, that having invoked you on earth we may love and eternally thank you in heaven.

\prayertitle{Pope St. John Paul II's Prayer to Our Lady of Lourdes}
\label{prayer:JPII_Lady_of_Lourdes}
Hail Mary, poor and humble woman, blessed by the Most High!
Virgin of hope, dawn of a new era, we join in your song of praise, to celebrate the Lord's Mercy, to proclaim the coming of the Kingdom and the full liberation of humanity.

Hail Mary, lowly handmaid of the Lord, Glorious Mother of Christ!
Faithful Virgin, holy dwelling-place of the Word, teach us to persevere in listening to the Word, and to be docile to the Voice of the Spirit, attentive to His promptings in the depths of our conscience and to His manifestations in the events of history.

Hail Mary, Woman of sorrows, Mother of the living!
Virgin spouse beneath the Cross, the new Eve, be our guide along the paths of the world.
Teach us to experience and to spread the Love of Christ, to stand with you before the innumerable crosses on which your Son is still crucified.

Hail Mary, woman of faith, first of the disciples!
Virgin Mother of the Church, help us always to account for the hope that is in us, with trust in human goodness and the Father's Love.
Teach us to build up the world beginning from within:
in the depths of silence and prayer, in the joy of fraternal love, in the unique fruitfulness of the Cross.

Holy Mary, Mother of believers, Our Lady of Lourdes, pray for us.

\indulgencedprayertitle{\foreign{Sancti Apostoli Petre et Paule}}
\linkednote{grant20}{A partial indulgence is granted for devoutly reciting this prayer.}
Holy Apostles Peter and Paul, intercede for us.
Guard Your people, who rely on the patronage of Your apostles Peter and Paul, O Lord, and keep them under Your continual protection.
Through Christ our Lord. Amen.

\indulgencedprayertitle{\foreign{Ad te, beate Ioseph}}
\linkednote{grant19}{A partial indulgence is granted for invoking St. Joseph with this prayer.}
To you, O blessed Joseph, do we come in our tribulation, and having implored the help of your most holy spouse, we confidently invoke your patronage also.
Through that charity which bound you to the Immaculate Virgin Mother of God and through the paternal love with which you embraced the Child Jesus, we humbly beg you graciously to regard the inheritance which Jesus Christ has purchased by His Blood, and with your power and strength to aid us in our necessities.
O most watchful Guardian of the Holy Family, defend the chosen children of Jesus Christ;
O most loving father, ward off from us every contagion of error and corrupting influence;
O our most mighty protector, be kind to us and from heaven assist us in our struggle with the power of darkness.
As once you rescued the Child Jesus from deadly peril, so now protect God's Holy Church from the snares of the enemy and from all adversity;
shield, too, each one of us by your constant protection, so that, supported by your example and your aid, we may be able to live piously, to die in holiness, and to obtain eternal happiness in heaven.
Amen.

\prayertitle{Prayer to St. Michael the Archangel}
\label{prayer:StMichael}
Saint Michael the Archangel, defend us in battle, be our protection against the wickedness and snares of the devil;
may God rebuke him, we humbly pray;
and do you, O Prince of the heavenly host, by the Power of God, cast into hell Satan and all the evil spirits who prowl through the world seeking the ruin of souls.
Amen.

\prayertitle{For Help Against Spiritual Enemies}
\label{prayer:help_against_spiritual_enemies}
Glorious Saint Michael, Prince of the heavenly hosts, who stands always ready to give assistance to the people of God;
who fought with the dragon, the old serpent, and cast him out of heaven, and now valiantly defends the Church of God that the gates of hell may never prevail against her, I earnestly entreat you to assist me also, in the painful and dangerous conflict which I sustain against the same formidable foe.

Be with me, O mighty Prince!
that I may courageously fight and vanquish that proud spirit, whom you, by the Divine Power, gloriously overthrew, and whom our powerful King, Jesus Christ, has, in our nature, completely overcome;
so having triumphed over the enemy of my salvation, I may with you and the holy angels, praise the Clemency of God Who, having refused mercy to the rebellious angels after their fall, has granted repentance and forgiveness to fallen man. Amen.

\newpage

\prayersection{For the Family}
\indulgencedprayertitle{\foreign{Exaudi Nos}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Hear us, Lord, holy Father, almighty and eternal God;
and graciously send Your holy angel from heaven to watch over, to cherish, to protect, to abide with, and to defend all who dwell in this house.
Through Christ our Lord. Amen.

\indulgencedprayertitle{\foreign{Visita, quaesumus, Domine}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day, when starting and completing work, or before and after meals.}
Visit, we beg You, O Lord, this dwelling, and drive from it all snares of the enemy:
let Your holy Angels dwell herein, to keep us in peace;
and let Your blessing be always upon us.
Through Christ our Lord.
Amen.

\prayertitle{For our Family}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-families.cfm which cites Catholic Household Blessings and Prayers
We bless Your Name, O Lord, for sending Your own incarnate Son, to become part of a family, so that, as He lived its life, He would experience its worries and its joys.

We ask You, Lord, to protect and watch over this family, so that in the strength of Your Grace its members may enjoy prosperity, possess the priceless gift of Your Peace, and, as the Church alive in the home, bear witness in this world to Your Glory.

We ask this through Christ our Lord.
Amen.
\newpage
\prayertitle{For Charity in the Family}
% My Prayer Book, p. 264
O Lord, our God, we offer You our hearts united in the strongest and most sincere love of brotherhood.
We pray that Jesus may be the daily food of our souls and bodies and that He may be the center of our affections even as He was for Mary and Joseph.
Finally, O Lord, may sin never disturb our union on earth.
May we be eternally united in heaven with You and Mary and Joseph and all Your saints.
Amen.

\prayertitle{Parents' Thanksgiving}
O God, we give You thanks for \insertname, whom You have welcomed into our family.
Bless this family.
Confirm a lively sense of Your Presence with us, and grant us patience and wisdom, that our lives may show forth the Love of Christ, as we bring \insertname\ up to love all that is good.
We ask this through Christ our Lord.
Amen.

\prayertitle{A Parent's Prayer}
\label{prayer:parent}
Loving God, You are the giver of all we possess, the source of all of our blessings.
We thank and praise You.

Thank You for the gift of our children.

Help us to set boundaries for them, and yet encourage them to explore.
Give us the strength and courage to treat each day as a fresh start.

May our children come to know You, the one true God, and Jesus Christ, Whom You have sent.

May Your Holy Spirit help them to grow in faith, hope, and love, so they may know peace, truth, and goodness.

May their ears hear Your Voice.
May their eyes see Your Presence in all things.
May their lips proclaim Your Word.
May their hearts be Your dwelling place.
May their hands do works of charity.
May their feet walk in the way of Jesus Christ, Your Son and our Lord.
Amen.

\prayertitle{For Safety for Children}
\label{prayer:safety_children}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-safety.cfm from Catholic Household Blessings and Prayers
Strong and faithful God, keep our children safe from injury and harm and make them blessings to all they meet today.

\prayertitle{Husband's Prayer for his Wife}
% My Prayer Book, p. 266
Lord Jesus, in the heart of my heart You know my desire is for my wife's happiness.
You know also I want her to share her love with me and I want to share my love with her.
May the good Grace of Your Spirit guide my uncertain ways that I may be the instrument of my wife's happiness.
Help me to express my love in big and little ways.
Help us to rejoice in each other, to be helpful and thoughtful, always to be aware of the mystery of each other's personality.
I believe we are joined to each other in You.
Show us Your favor, Lord Jesus.
Amen.

\prayertitle{Prayer in Defense of Marriage}
\label{prayer:defense_marriage}
God our Father, we give You thanks for the gift of marriage:
the bond of life and love, and the font of the family. 
The love of husband and wife enriches Your Church with children, fills the world with a multitude of spiritual fruitfulness and service,
and is the sign of the Love of Your Son, Jesus Christ, for His Church.

The Grace of Jesus flowed forth at Cana at the request of the Blessed Mother.
May Your Son, through the intercession of Mary, pour out upon us a new measure of the Gifts of the Holy Spirit as we join with all people of good will to promote and protect the unique beauty of marriage.

May Your Holy Spirit enlighten our society to treasure the heroic love of husband and wife, and guide our leaders to sustain and protect
the singular place of mothers and fathers in the lives of their children.

Father, we ask that our prayers be joined to those of the Virgin Mary, that Your Word may transform our service so as to safeguard the incomparable splendor of marriage.
We ask all these things through Christ our Lord,
Amen.

Saints Joachim and Anne, pray for us.

\newpage

\prayersection{For the Deceased}
\linkednote{grant29}{A plenary indulgence, applicable only to the souls in purgatory, is granted on any and each day from November 1 to 8 for devoutly visiting a cemetary and praying, if only mentally, for the departed.
A partial indulgence, applicable only to the souls in purgatory, is granted for devoutly visiting a cemetary and at least mentally praying for the dead.}
\prayertitle{For Departed Loved Ones}
% Laudate app, which cites ``Prayers for Today'', published by Leaflet Missal Co. Also can be found online, e.g. at https://www.catholicdoors.com/prayers/english3/p02468.htm.
Almighty God, Who by the love which You have for men, have willed to take our humanity, to live a life of hard work, to suffer a most cruel Passion, and finally to die on the Cross, I beseech You, by the infinite merits purchased for us with Your Precious Blood, look mercifully on the suffering  which is endured by the holy souls in Purgatory. 
Accept, O merciful God, the prayers which I offer for them, and call them to the glory of Heaven. 
I recommend to You the souls of my relatives, friends, and benefactors, and in a special manner of those to whom I may have been an occasion of sin by my bad example. 
Most Holy Virgin, Mother of Mercy, Comforter of the afflicted, intercede for those souls, that, by your powerful intercession, they may be admitted to enjoy that Kingdom which is prepared for them.

\prayertitle{\foreign{Requiem aeternam}}
\linkednote{grant29}{A partial indulgence, applicable only to the souls in purgatory, is granted for devoutly reciting this prayer.}
Eternal rest grant unto them, O Lord, and let perpetual light shine upon them.
May they rest in peace.

\prayertitle{For a Man Deceased}
% My Prayer Book, p. 267
Incline Your Ear, O Lord, to our prayers in which we humbly pray that You show Your Mercy to the soul of Your servant \insertname, whom You commanded to leave this world.
Place him in the region of peace and light and bid him share the company of Your saints.
Through Christ our Lord. Amen.

\prayertitle{For a Woman Deceased}
% My Prayer Book, p. 267
O Lord, we beg of You, through Your loving kindness, have mercy on the soul of Your servant \insertname, and now that she is set free from the defilements of this mortal flesh, restore her to her heritage of everlasting salvation.
Through Christ our Lord. Amen.

\indulgencedprayertitle{Prayer for the Faithful Departed}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Byzantine Tradition.}
God of the spirits and of all flesh, Who have destroyed death and annihilated the devil
and given life to Your world, may You Yourself, O Lord, grant to the soul of Your
deceased servant \insertname\ rest in a place of light, a verdant place, a place of freshness, from where suffering, pain, and cries are far removed.
Do You, O good and compassionate God, forgive every fault committed by him in word, work, or thought;
because there is no man who lives and does not sin.
You alone are without sin and Your Justice is justice throughout the ages and Your Word is truth.
Since You, O Christ our God, are the resurrection, the life, and the repose of Your
deceased servant \insertname, we give You glory together with Your un-begotten Father with
Your most holy, good, and vivifying Spirit, now and always and for ever and ever.

\indulgencedprayertitle{Intercession for the Deceased from the Liturgy of St. James}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Syro-Antiochian Tradition.}
Lord, O Lord, God of the pure spirits and of every flesh, be mindful of us all, of those we have remembered and of all we have not remembered and who have left this world with glorious faith.
Give repose to their souls, to their bodies, to their spirits.
Save them from future damnation and make them worthy of the joy, which is in the bosom of Abraham, Isaac, and Jacob, where the light of Your Countenance shines, where pain, anguish, and cries are banished.
Do not impute to them any fault;
do not enter into judgment with Your servants, because no living being is justified in Your Sight and because no man on earth is immune from sin and pure of every filth except for our Lord Jesus Christ, Your Son, through Whom we, too, hope to obtain mercy and the pardon of our sins and of those of our deceased.

Give rest to their souls;
cancel our faults and their faults committed before You willingly or unwillingly, consciously or unconsciously.

Grant them rest.
Forgive, O God, and pardon the voluntary and involuntary sins committed consciously or unconsciously by word, work, or omissions, by secret thoughts or publicly, deliberately or through error and which Your holy Name knows.
Grant us a Christian ending without sin and unite us at the feet of Your elect when You Will, where You Will, and how You Will, without us having to blush for our sins because in this as in all things Your holy and blessed Name, the Name of our Lord Jesus Christ and of the Holy Spirit, be praised and glorified now and for all ages. Amen.

\prayertitle{For the Dead}
\label{prayer:dead}
In Your Hands, O Lord, we humbly entrust our brothers and sisters.
In this life You embraced them with Your tender Love;
deliver them now from every evil and bid them eternal rest.

The old order has passed away:
welcome them into paradise, where there will be no sorrow, no weeping, or pain,
but fullness of peace and joy with Your Son and the Holy Spirit forever and ever.
Amen.

\prayertitle{For Deceased Parents}
O God, Who has commanded us to honor our father and our mother, in Your Mercy have pity on the souls of my father and mother, and forgive them their trespasses, and make me to see them again in the joy of everlasting brightness. Through Christ our Lord. Amen.

\prayertitle{For Mourners}
\label{prayer:mourners}
Lord God, You are attentive to the voice of our pleading.
Let us find in Your Son comfort in our sadness, certainty in our doubt, and courage to live through this hour.
Make our faith strong through Christ our Lord.

Lord, \insertname\ are gone now from this earthly dwelling, and have left behind those who mourn their absence.
Grant that we may hold their memory dear, never bitter for what we have lost
nor in regret for the past, but always in hope of the eternal Kingdom where You will bring us together again.

May the Love of God and the Peace of the Lord Jesus Christ bless and console us and gently wipe every tear from our eyes:
in the Name of the Father, and of the Son, and of the Holy Spirit.
Amen.

\prayertitle{For the Poor Souls in Purgatory}
\label{prayer:poor_souls_purgatory}
My Jesus, by the sorrows You suffered in Your agony in the Garden, in Your scourging and crowning with thorns, in Your journey to Calvary, in Your crucifixion and death, have mercy on the souls in purgatory, and especially on those who are most forsaken;
deliver them from the torments they endure;
call them and admit them to Your most sweet embrace in Paradise, where You live with the Father and the Holy Spirit, one God, for ever and ever.

Merciful Father, hear our prayers and console us, as we renew our faith in Your Son Whom You raised from the dead, strengthen our hope that all our departed brothers and sisters will share in His resurrection, Who lives and reigns with You and the Holy Spirit, one God for ever and ever.
Amen.

\prayertitle{For the Most Neglected and Most in Need in Purgatory}
\label{prayer:most_neglected_purgatory}
Lord, Almighty God, through the Sacred Blood which Your Divine Son shed in the Garden of Gethsemane and at the painful Crowning of Thorns, I ask You to free the souls in Purgatory, in particular those who are most neglected and those in most need of our intercession.
Please do not let them wait any longer in Purgatory, and lead them into Your Glory so that they may praise and glorify You throughout eternity.
Amen.

\prayertitle{For those in Purgatory Closest to the Entrance of Heaven}
\label{prayer:purgatory_closest_heaven}
Lord, Almighty God, through the Sacred Blood which Your Divine Son shed during the cruel Scourging, I ask You to free the Souls in Purgatory, in particular those who stand the closest to the entrance of Your Delight.
Let them begin to praise and glorify You from now throughout eternity.
Amen.

\prayertitle{Prayer at Graveside}
\label{prayer:graveside}
Lord Jesus Christ, by Your own three days in the tomb, You hallowed the graves of all who believe in You and so made the grave a sign of hope that promises resurrection even as it claims our mortal bodies.

Grant that our brother/sister, \insertname, may sleep here in peace until You awaken him/her to glory, for You are the resurrection and the life.
Then he/she will see You face to face and in Your Light will see light and know the splendor of God, for You live and reign forever and ever.
Amen.

\newpage

\prayersection{For the Church}
\prayertitle{For the Church Under Persecution}
% My Prayer Book, p. 259
Father, in the mystery of Your Providence the Church was to share in the sufferings of Christ Your Son.
Give those who suffer persecution for their faith a share also in the Patience and Love of Your Son, that they may be true and faithful witnesses to His promise of resurrection and eternal life.
Amen.

\prayertitle{For the Church}
% My Prayer Book, p. 258
Father, in the new covenant instituted by Christ Your Son, You gather Your people in the unity of Your Spirit from all the nations of the earth.
Keep Your Church faithful to her mission as a leaven in the world, renewing all peoples in Christ and transforming them into Your own family.
Amen.

\prayertitle{For our Parish}
O God, You have made us the Church of Your dear Son.
Make our parish a family of one heart and mind in love toward You.
Grant that our common life and world may be an example to all about us.
Guide our pastor and his assistants in their work.
Acknowledge the intercessions of our patron; and keep us secure in Your Love.
Amen.

\prayertitle{For the Pope}
% My Prayer Book, p. 258
Father, as successor to the Apostle Peter You have chosen Your servant \insertname\ to be the vicar of Christ on earth and shepherd of the whole flock.
May he strengthen his brothers, and may the whole Church be in communion with him in the bond of unity, love, and peace, that all men may receive from You, the shepherd and bishop of their souls, truth and eternal life.
Amen.
\newpage
\prayertitle{For the Bishop}
% My Prayer Book, p. 260
God our Father, You have entrusted to Your servant \insertname, as a successor to the Apostles, the care of the diocese of \insertname.
Give him Your Spirit of wisdom and courage, of understanding and love.
Keep him faithful to his mission that he may build up Your Church, the universal sacrament of salvation.
Amen.

\prayertitle{For Priests}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-priests.cfm
Gracious and loving God, we thank You for the gift of our priests.
Through them, we experience Your Presence in the sacraments.

Help our priests to be strong in their vocation.
Set their souls on fire with love for Your people.

Grant them the wisdom, understanding, and strength they need to follow in the footsteps of Jesus.
Inspire them with the vision of Your Kingdom.

Give them the words they need to spread the Gospel.
Allow them to experience joy in their ministry.

Help them to become instruments of Your divine Grace.

We ask this through Jesus Christ, Who lives and reigns as our Eternal Priest.
Amen.

\prayertitle{For Priests \#2}
% My Prayer Book, p. 260
Father, You appointed Your only Son as the eternal high priest.
Grant that those He has chosen to be ministers of word and sacrament may be faithful in their ministry until the day of His coming.
Amen.

\prayertitle{For Religious}
% My Prayer Book, p. 261
Father, every good intention has its origin and fulfillment in You.
Guide Your people along the path of salvation and look kindly on those who have left all things to follow Christ in chastity, poverty, and obedience, and to consecrate themselves to You.
In their service to You, Father, and to all their brothers and sisters, may they give faithful witness to Christ.
Amen.

\prayertitle{For Vocations}
% http://www.usccb.org/beliefs-and-teachings/vocations/upload/Prayer-for-Vocations-Card-2014.pdf
God our Father, we thank You for calling men and women to serve in Your Son's Kingdom as priests, deacons, and consecrated persons.
Send Your Holy Spirit to help others to respond generously and courageously to Your call.
May our community of faith support vocations of sacrificial love in our youth and young adults.
Through our Lord Jesus Christ, Who lives and reigns with You in the unity of the Holy
Spirit, one God, forever and ever.
Amen.

\newpage

\prayersection{Prayers of the Saints and Religious}
\prayertitle{The Universal Prayer (Pope Clement XI)}
% My Prayer Book, pp. 281-283
Lord, I believe in You: increase my faith.
I  trust in You: strengthen my trust.
I love You: let me love You more and more.
I am sorry for my sins: deepen my sorrow.

I worship You as my first beginning, I long for You as my last end, I praise You as my constant helper, and call on You as my loving protector.

Guide me by Your Wisdom,
correct me with Your Justice,
comfort me with Your Mercy,
protect me with Your Power.

I offer You, Lord, my thoughts: to be fixed on You;
my words: to have You for their theme;
my actions: to reflect my love for You;
my sufferings: to be endured for Your greater Glory.

I want to do what You ask of me:
in the way You ask,
for as long as You ask,
because You ask it.

Lord, enlighten my understanding,
strengthen my will,
purify my heart,
and make me holy.

Help me to repent of my past sins and to resist temptation in the future.
Help me to rise above my human weaknesses and to grow stronger as a Christian.

Let me love You, my Lord and my God, and see myself as I really am:
a pilgrim in this world,
a Christian called to respect and love all whose lives I touch,
those in authority over me or those under my authority,
my friends and my enemies.

Help me to conquer anger with gentleness,
greed by generosity,
apathy by favor.
Help me to forget myself and reach out toward others.
Make me prudent in planning, courageous in taking risks.
Make me patient in suffering, unassuming in prosperity.

Keep me, Lord, attentive at prayer,
temperate in food and drink,
diligent in my work,
firm in my good intentions.

Let my conscience be clear,
my conduct without fault,
my speech blameless,
my life well-ordered.
Put me on guard against my human weaknesses.
Let me cherish Your Love for me,
keep Your Law,
and come at last to Your salvation.

Teach me to realize that this world is passing,
that my true future is the happiness of heaven,
that life on earth is short,
and the life to come is eternal.

Help me to prepare for death with a proper fear of judgment, but a greater trust in Your Goodness.
Lead me safely through death to the endless joy of heaven.

Grant this through Christ our Lord. Amen.

\prayertitle{Thomas Merton}
% https://www.goodreads.com/quotes/80913-my-lord-god-i-have-no-idea-where-i-am
My Lord God, I have no idea where I am going. 
I do not see the road ahead of me.
I cannot know for certain where it will end.
Nor do I really know myself,  and the fact that I think that I am following Your Will does not mean that I am actually doing so.

But I believe that the desire to please You does in fact please You. 
And I hope I have that desire in all that I am doing. 
I hope that I will never do anything apart from that desire. 
And I know that if I do this, You will lead me by the right road though I may know nothing about it.

Therefore will I trust You always though I may seem to be lost and in the shadow of death.
I will not fear, for You are ever with me, and You will never leave me to face my perils alone. 
Amen.  

\prayertitle{St. Th\'{e}r\`{e}se of Lisieux}
% My Prayer Book, p. 280
O my God, I ask of You for myself and for those whom I hold dear, the grace to fulfill perfectly Your holy Will, to accept for love of You the joys and sorrows of this passing life, so that we may one day be united in Heaven for all eternity.

\prayertitle{St. Francis of Assisi}
% My Prayer Book, p. 275
Lord, make me an instrument of Your Peace.
Where there is hatred, let me sow love;
where there is injury, pardon;
where there is doubt, faith;
where there is despair, hope;
where there is darkness, light;
and where there is sadness, joy.

O Divine Master, grant that I may not so much seek to be consoled as to console, to be understood as to understand, to be loved as to love.

For it is in giving that we receive, it is in pardoning that we are pardoned, and it is in dying that we are born to eternal life.

\prayertitle{St. Gemma Galgani}
% http://www.stgemmagalgani.com/2008/09/prayer-of-st-gemma-galgani-to-obtain.html
O my crucified God, behold me at Your Feet;
do not cast me out, now that I appear before You as a sinner.
I have offended You exceedingly in the past, my Jesus, but it shall be so no longer.
Before You, O Lord, I place all my sins;
I have now considered Your own sufferings and see how great is the worth of that Precious Blood that flows from Your Veins.
O my God, at this hour close Your Eyes to my want of merit, and since You have been pleased to die for my sins, grant me forgiveness for them all, that I may no longer feel the burden of my sins, for this burden, dear Jesus, oppresses me beyond measure.
Assist me, my Jesus, for I desire to become good whatsoever it may cost;
take away, destroy, utterly root out all that You find in me contrary to Your holy Will.
At the same time, I pray to You, Lord Jesus, to enlighten me that I may be able to walk in Your holy Light.
Amen.

\prayertitle{St. Gemma Galgani (to obtain a desired grace)}
% http://www.stgemmagalgani.com/2008/09/prayer-of-st-gemma-galgani-to-obtain.html
Behold me at Your most holy Feet, O dear Jesus, to manifest to You my gratitude for the continual favors which You have bestowed upon me, and still wish to bestow upon me.
As many times as I have invoked You, O Jesus, You have made me content;
I have often had recourse to You and You have always consoled me.
How shall I express myself to You, dear Jesus?
I thank You!
Yet one more grace I desire of You, O my God, if it would be pleasing to You: \ldots


If You were not omnipotent, I would not make this request.
O Jesus, have pity on me.
May Your most holy Will be done in all things.

\prayertitle{St. Ephrem the Syrian \#1}
% My Prayer Book, p. 279
Have mercy on me:
I am a sinner, I am weak.
Be gracious, O God, to my weakness;
grant strength to me to pray a prayer that will be pleasing to Your Will.

\prayertitle{St. Ephrem the Syrian \#2}
\label{prayer:StEphrem2}
Lord Jesus Christ, King of Kings, You have power over life and death.
You know what is secret and hidden, and neither our thoughts nor our feelings are concealed from You.
Cure me of duplicity;
I have done evil before You.
Now my life declines from day to day and my sins increase.
O Lord, God of souls and bodies, You know the extreme frailty of
my soul and my flesh.
Grant me strength in my weakness, O Lord, and sustain me in my misery.
Give me a grateful soul that I may never cease to recall Your benefits, O Lord most bountiful.
Be not mindful of my many sins, but forgive me all my misdeeds.
O Lord, disdain not my prayer --- the prayer of a wretched sinner;
sustain me with Your Grace until the end, that it may protect me as in the past.
It is Your Grace which has taught me wisdom;
blessed are they who follow her ways, for they shall receive the crown of glory.
In spite of my unworthiness, I praise You and I glorify You, O Lord, for Your Mercy to me is without limit.
You have been my help and my protection.
May the Name of Your Majesty be praised forever. 
To You, our God, be glory.
Amen.

\prayertitle{St. Augustine}
% My Prayer Book, p. 276
Breathe in me, Holy Spirit, that all my thoughts may be holy.
Act in me, Holy Spirit, that my work too may be holy.
Draw my heart, Holy Spirit, that I may love only what is holy.
Strengthen me, Holy Spirit, to defend all that is holy.
Guard me, Holy Spirit, that I may always be holy.

\prayertitle{St. Thomas Aquinas}
Grant me, O Lord my God,
a mind to know You,
a heart to seek You,
wisdom to find You,
conduct pleasing to You,
faithful perseverance in waiting for You,
and a hope of finally embracing You.

\prayertitle{St. Ignatius Loyola}
% My Prayer Book, p. 278
Teach us, good Lord, to serve You as You deserve:
to give and not to count the cost;
to fight and not to heed the wounds;
to toil and not to seek for rest;
to labor and not ask for any reward save that of knowing that we do Your Will.

\prayertitle{Simon Patrick}
% My Prayer Book, p. 279
O Lord, endow me with more contentedness in what is present, and less solicitude about what is future;
with a patient mind to submit to any loss of what I have, or to  any disappointment of what I expect.

\prayertitle{St. Thomas More}
% My Prayer Book, pp]. 278-279
Good Lord, give me the grace so to spend my life, that when the day of my death shall come, though I feel pain in my body, I may feel comfort in soul;
and with faithful hope of Your Mercy, in due love towards You and charity towards the world, I may, through Your Grace, part hence into Your Glory.

\prayertitle{St. John Baptist de La Salle}
% My Prayer Book, p. 277
O my God, I beg of You to grant me peace with my neighbor, for I cannot enjoy Your favor if I do not live in union with my brothers and sisters.
I can preserve this union by mildness and patience.
Give me, then, I beseech You, these two virtues, and grant that I may always speak and act kindly to all;
that I may suffer patiently for love of You whatever wrongs, injuries, or insults may be done me;
that not only I may not be angered or displeased with anything but that I may patiently suffer all that happens to me from others.

\prayertitle{Sister Consolata Betrone}
% https://en.wikipedia.org/wiki/Consolata_Betrone
Jesus, Mary, I love you: Save souls.

\prayertitle{St. Elizabeth Ann Seton}
% My Prayer Book, p. 276
From eternity to eternity, You are my God.
All shall perish and pass away, but You remain forever.

\prayertitle{Columba Marmion}
% My Prayer Book, p. 278
Behold me, O my God, I give myself to You, to Your good pleasure.
Because I love You, I will give You the homage of submitting my whole being to Your Will, whatever it may be.

\prayertitle{St. Francis de Sales}
% My Prayer Book, p. 277
O God, You are my God, in You will I hope!
You will be my help and my refuge.
I shall not fear, for not only are You with me but You are in me and I in You.

\prayertitle{Bl. Jan Van Ruysbroeck}
% My Prayer Book, p. 276
Lord, I am willing to be poor in all those things of which I have been deprived as I am ready to be rich, O Lord, if it be Your Will and to Your Glory;
not my will according to nature, O Lord, but Your Will and my will according to spirit be done.

\newpage

\prayersection{Pro-Life}
\prayertitle{For Life and Dignity}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-life-and-dignity.cfm from Being Neighbor: The Catechism and Social Justice, USCCB, April 1998
Eternal God, creator and sustainer of life, bless us with the courage to defend all life from conception to natural death.
Bless us with the strength to respect all peoples from east to west, from north to south,
so that we may truly follow the call of Jesus to be neighbor.
We ask this in the Name of Jesus, Who lives and reigns with You and the Holy Spirit.
Amen.

\prayertitle{To End Abortion}
% http://www.priestsforlife.org/novenas/novena.aspx?id=10
Lord God, I thank You today for the gift of my life, and for the lives of all my brothers and sisters.
I know there is nothing that destroys more life than abortion, yet I rejoice that You have conquered death by the Resurrection of Your Son. 
I am ready to do my part in ending abortion. Today I commit myself 
never to be silent, 
never to be passive, 
never to be forgetful of the unborn. 
I commit myself to be active in the pro-life movement and never to stop defending life until all my brothers and sisters are protected, and our nation once again becomes a nation with liberty and justice not just for some, but for all.
Through Christ our Lord. Amen!

\prayertitle{For Pro-Life Advocates}
% Fr. Frank Pavone, National Director, Priests for Life, http://www.priestsforlife.org/pdf/prayer-for-prolife-advocates.pdf
% Changed "Planned Parenthood" to "the abortion industry"
Father of our Lord Jesus Christ,
You have filled us with Your Holy Spirit Who is our advocate in the heavens, and You have made us advocates for the weakest of all, the unborn.

Your Son has promised us that we will be hated on account of His Name and persecuted for the good that we do.
We ask You today to bless all of us who are advocates for life.
Bless every facet and activity of the pro-life movement, and grant us strength and perseverance in this cause, no matter what the obstacles.

Bless all those who have assisted in the effort to expose the abortion industry, through projects in the past and in the present.

Give them, and all of us who work in this great movement, the protection of Your Providence and the peace and joy that come only from You, and that nobody can take from us.

We pray in the Name of Jesus our Lord. Amen.

\prayertitle{For Public Officials}
% Fr. Frank Pavone, National Director, Priests for Life, http://www.priestsforlife.org/pdf/prayer-for-our-public-officials.pdf
Lord Jesus,
You are the King of Kings and Lord of Lords.
You are the Ruler of the kings of the earth, and the one through Whom and for Whom all things exist.

We pray today for those who serve in public office.
We ask that those who write and pass our laws may keep their eyes fixed on Your Law as their ultimate authority.
We ask that those who execute the laws may be filled with awe in Your Presence, as You govern the universe from end to end mightily.
And we ask that those who judge in human courts may know they are accountable to You, the Judge of all.

Lord, we pray that the tragedy of abortion, and the trade in baby body parts, may awaken the consciences of those in public office, and stir them to action to defend human rights and dignity.

Lord, so many have been asleep, and so many public servants have forgotten the difference between serving the public and killing the public.

Awaken them, enlighten them, and heal them.

And to those whose eyes are already fixed on Your Law of life, give unending courage and perseverance in the task of serving the common good and securing the right to life, which comes only from You and which no government can take away.

We ask this of You, Lord Jesus, Who lives and reigns forever and ever. Amen.

\prayertitle{Redeemer in the Womb}
% http://www.priestsforlife.org/prayers/prayerredeemerinwomb.html
Lord Jesus Christ, You took our human nature upon Yourself.
You shared our life and death, our childhood and adulthood.

You also shared our time in the womb. While still God, while worshiped and adored by the angels, while Almighty and filling every part of the universe, You dwelt for nine months in the womb of Mary.
You were our Redeemer in the womb, our God Who was a preborn child.

Lord Jesus, we ask You to bless and protect the children who today are in their mothers' womb.
Save them from the danger of abortion.
Give their mothers the grace to sacrifice themselves, in body and soul, for their children.
Help all people to recognize in the preborn child a brother, a sister, saved by You, our Redeemer in the womb.

\prayertitle{To the Holy Spirit, the Advocate}
% http://www.priestsforlife.org/prayers/prayerhsadvocate.html
O Holy Spirit of God, You were promised to us by the Lord Jesus as an Advocate, as one Who pleads our cause and speaks up for us in the heights of heaven.
``I will ask the Father, and He will give you another Advocate, to be with you forever...'' (John 14:16).

The apostle Paul has taught us that You intercede for us with groanings that cannot be expressed in speech (Rom. 8:26).

We praise You today for the gift of salvation, for we are deeply aware that we cannot save ourselves.
We have sinned, and we cannot win forgiveness on our own.
We need an Advocate.

We ask You, O Holy Spirit, to make us ever more aware of those who need us as advocates.
Grant that we may hear the cries of our youngest, smallest brothers and sisters, those still in the womb, who cannot speak or defend themselves, and who cannot even pray.

Holy Spirit, as You are the Advocate, so make us advocates.
As You hear our cries for mercy, so let us hear the cries of others for mercy.
Save us from the misfortune of seeking mercy only for ourselves, while being deaf to others.
As You loosened the tongues of the apostles at Pentecost, so grant us today a Pentecost for the unborn, that we may speak for them before the great and the small, before governments and institutions, and before all Your people.
Amen.

\prayertitle{To the Virgin Mary}
O Mary, Mother of Jesus and Mother of us all, we turn to you today as the one who said ``Yes'' to Life.
``You will conceive and bear a Son,'' the angel told you.
Despite the surprise and the uncertainty about how this could be, you said yes.
``Be it done unto me according to your word.''

Mary, we pray today for all mothers who are afraid to be mothers.
We pray for those who feel threatened and overwhelmed by their pregnancy.
Intercede for them, that God may give them the grace to say yes and the courage to go on.
May they have the grace to reject the false solution of abortion.
May they say with you, ``Be it done unto me according to your word.''
May they experience the help of Christian people, and know the peace that comes from doing God's Will.
Amen.

\prayertitle{For Protection of Conscience Rights in Health Care}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/protection-of-conscience-rights-healthcare.cfm
Father, in Jesus our Lord, we praise and thank You for Your most precious gift of human life and for forming us in Your divine Image.
Keep us, the dwelling place of Your most Holy Spirit, ever healthy in body and soul.

Jesus, Divine Healer, pour Your Grace upon all those afflicted with illness or disease.
Protect from all harm those who are vulnerable due to sickness, suffering, frailty, poverty, or age, whether elderly or unborn.

Holy Spirit, touch the hearts of all who serve human life in medicine and science, so they will protect the dignity of each person, from conception to natural death, and remain faithful advocates of all entrusted to their care.  

Grant those who are called to serve as health care providers renewed conviction in their ministry, and increased wisdom to treat the whole person, and not merely the illness.

Protect the right of health care providers to serve their patients without being forced to violate their moral and religious convictions.
Guard them against discrimination, that they might be free to follow You faithfully while fulfilling their professional duties.

Grant our lawmakers the wisdom and courage to uphold conscience rights for those called to the ministry of healing, and help them resist the pressure to become collaborators in the culture of death.

Give us strength to be bold and joyful witnesses to the truth that every human life is sacred.

In Your Goodness, guard our freedom to live out our faith and to follow You in all that we do.

Father, we ask this in Jesus' Name, through the Holy Spirit. Amen.

\prayertitle{Prayer to End the Use of the Death Penalty}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-to-end-the-use-of-the-death-penalty.cfm
Merciful Father, we ask Your blessing in all we do to build a culture of life.
Hear our prayers for those impacted by the death penalty.

We pray for all people, that their lives and dignity as children of a loving God may be respected and protected in all stages and circumstances.

We pray for victims of violence and their families, that they may experience our love and support and find comfort in Your Compassion and in the promise of eternal life.

We pray for those on death row, that their lives may be spared, that the innocent may be freed and that the guilty may come to acknowledge their faults and seek reconciliation with You.

We pray for the families of those who are facing execution, that they may be comforted by Your Love and Compassion.

We pray for civic leaders, that they may commit themselves to respecting every human life and ending the use of the death penalty in our land.

Compassionate Father, give us wisdom and hearts filled with Your Love.
Guide us as we work to end the use of the death penalty and to build a society that truly chooses life in all situations.

We ask this, Father, through Your Son Jesus Christ, Who lives and reigns with the Holy Spirit, one God forever and ever.
Amen.

\prayertitle{For Life}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-life.cfm
Father and maker of all, You adorn all creation with splendor and beauty, and fashion human lives in Your Image and Likeness.
Awaken in every heart reverence for the work of Your Hands, and renew among Your people
a readiness to nurture and sustain Your precious gift of life.

Grant this through our Lord Jesus Christ, Your Son, Who lives and reigns with You in 
the unity of the Holy Spirit, God forever and ever.
Amen.

\prayertitle{Pope Benedict XVI's Prayer For The Unborn}
\label{prayer:benedict_xvi_unborn}
Lord Jesus, 
You Who faithfully visit and fulfill with Your Presence the Church and the history of men;
You Who in the miraculous Sacrament of Your Body and Blood render us participants in divine Life and allow us a foretaste of the joy of eternal Life;
we adore and bless You.

Prostrated before You, source and lover of Life, truly present and alive among us, we beg You:

Reawaken in us respect for every unborn life, make us capable of seeing in the fruit of the maternal womb the miraculous work of the Creator, open our hearts to generously welcoming every child who comes into life.

Bless all families, sanctify the union of spouses, render fruitful their love.

Accompany the choices of legislative assemblies with the light of Your Spirit, so that peoples and nations may recognize and respect the sacred nature of life, of every human life.

Guide the work of scientists and doctors, so that all progress contributes to the integral well-being of the person, and no one endures suppression or injustice.

Give creative charity to administrators and economists, so they may realize and promote sufficient conditions so that young families can serenely embrace the birth of new children.

Console the married couples who suffer because they are unable to have children and in Your goodness provide for them.

Teach us all to care for orphaned or abandoned children, so they may experience the warmth of Your Charity, the consolation of Your divine Heart.

Together with Mary, Your Mother, the great believer, in whose womb You took on our human nature, we wait to receive from You, our Only True Good and Savior, the strength to love and serve life, in anticipation of living forever in You, in communion with the Blessed Trinity.

\prayertitle{Lenten Prayer for Life}
% Bishop James D. Conley, Auxiliary Bishop of Denver http://www.priestsforlife.org/prayers/bishop-conley-lenten-prayer.htm
Almighty Father and Lord of Life,
You have entrusted to men the noble mission of safeguarding and protecting human life with the utmost care from the moment of conception to natural death (\textit{Gaudium et Spes}, No. 51).

During this holy season of Lent, a time of both penance and great hope, stir in our hearts a greater love for You and for each other.
During these 40 days of spiritual renewal, lead us to a deeper conversion so that by living in Your Light and Love we may bear witness to the gift of life.

Lord Jesus, the firstborn of all creation, have mercy on us. 
Accept our prayers and our fasting in atonement for the tragic sin of abortion. 
By the merits of Your precious Blood, shed for our redemption, instill in all hearts a profound respect for the gift of life and bring about an end to abortion, euthanasia, and every other assault on innocent human life.

Reawaken in the heart of every pregnant mother a profound love for the life growing in her womb and grant to her unfailing courage to choose life for her child.

Come Holy Spirit, strengthen us and give us fortitude to work tirelessly to promote a true Culture of Life, a culture that recognizes the dignity and sanctity of every person.
Raise up men and women to serve in public office who will enact laws which will safeguard and protect all human life.

Blessed Mary, Mother of God, you bore the Author of Life in your womb. 
Through your intercession may our hearts be conformed to yours so that we might accept, nurture, and cherish all human life.

Sacred Heart of Jesus, have mercy on us. Amen.

\newpage

\prayersection{Litanies}
\prayertitle{Litany for Life}
\label{prayer:litany_for_life}
\note{Based on 1 Corinthians 12:31-13:8.}
Lord, love is patient.
Give to the mother who is tempted to abort her child the patience to endure the suffering that will bring forth new life.

Lord, love is kind.
Give to the new father whose friends tell him to abort his child the gentleness, compassion and courage to support his wife and child, protect them from all that could harm them, and sustain them against selfishness and hate.

Lord, love is not jealous.
Remove from all human hearts the temptation to trade human life for advantage, convenience, or personal benefit.
Deliver us from the expediency that values personal gain and pleasure over the dignity of human life.

Lord, love is not pompous.
Deliver us from the arrogance that sees our needs or wants as superior to the rights of others.
Help us to see all our brothers and sisters as worthy of all of our love.

Lord, love is not inflated.
Grant us a share in the Humility of Your Son, Who sought not to be served, but to serve. Help us to see in every human life, rich or poor, young or old, guilty or innocent, a reflection of Your Image and Likeness. 

Lord, love is not rude.
Implant a spirit of gentle compassion in the hearts of each of Your sons and daughters, Lord, that no person may ever be treated as less than the child of God which You have made them, through the Paschal Death and Resurrection of Your only-begotten Son.

Lord, love does not seek its own interests.
Give to all who govern us, Lord, a generous spirit, that our country may not so much seek to be great as to be good, to be rich in possessions as to be rich in mercy, or to be renowned as to be renowned for justice and truth for all.

Lord, love is not quick-tempered.
Grant that by our prudence and patience we might learn to live that sacrificial love by which Your Son died for us on the Cross, that all men and women might know our kindness and willingness to love them unto death after the model of our Lord and Savior.

Lord, love does not brood over injury.
Give us the grace of mercy, Lord, that like Your Son we might forgive those who sin against us, seeking only their redemption and eternal happiness.
Forgive the abortionist who takes the life of an unborn child.
Move his heart, grant him the grace of repentance, and give us a full share in Your Mercy.

Lord, love does not rejoice over wrongdoing.
Help us to seek only the redemption of wrongdoers, Lord, and remove from our hearts all desire for vengeance and hate.
Help us to desire not revenge, even for the horrors of abortion, but the repentance and happiness of all Your children.

Lord, love rejoices with the truth.
Implant deep within our hearts a sense of the joy of the Gospel of Life, and make us joy-filled evangelists of Your great gift of life.

Lord, love bears all things.
When we are insulted or reviled for the sake of the Gospel of Life, give us the courage and the innocence of the children of God.
Help us, Lord, to suffer for the sake of Your Truth, and never to seek our own good, even in the good work we do.

Lord, love believes all things.
Deliver us from every temptation to despair, Lord. When we are discouraged, give us the grace to trust in Your Mercy and to know that Your Love is ever victorious, even in the face of darkness, death, and hate.

Lord, love hopes all things.
As we trust in Your infinite Love, O Lord, give us the trust that comes from the Gospel, and help us to cling to that sure and certain hope that for those who love God all things come to good.

Lord, love endures all things.
In the face of death, destruction, and a culture of death, never let us lose sight of the beauty of the face of Your only-begotten Son, Our Lord, Who suffered the torments of His Passion and Death for the sake of our sins.
Let us trust that through His Passion we will have the strength to do Your Will and to carry each cross that comes our way for the Glory of God and the love of His little ones.

Lord, love never fails.
When the crusade for life seems unending and our latest initiatives have failed, when our hearts are filled with sadness or anger or fear, come to our aid, O Lord, and give us the assurance that You are ever with us, that Your Mercies will not end, and that You, our Creator and our God, will bring victory to all who seek to love as You have commanded them.

\prayertitle{Litany of Humility}
% TODO make sure the bold text is easily noticeable. If not find a better way to typeset it to highlight it.
\label{prayer:litany_of_humility}
O Jesus! meek and humble of heart, hear me.

From the desire of being esteemed, \textbf{deliver me, Jesus}.\\
From the desire of being loved\ldots\\
From the desire of being extolled\ldots\\
From the desire of being honored\ldots\\
From the desire of being praised\ldots\\
From the desire of being preferred to others\ldots\\
From the desire of being consulted\ldots\\
From the desire of being approved\ldots\\
From the fear of being humiliated\ldots\\
From the fear of being despised\ldots\\
From the fear of suffering rebukes\ldots\\
From the fear of being calumniated\ldots\\
From the fear of being forgotten\ldots\\
From the fear of being ridiculed\ldots\\
From the fear of being wronged\ldots\\
From the fear of being suspected\ldots\\

That others may be loved more than I, \textbf{Jesus, grant me the grace to desire it}.

That others may be esteemed more than I\ldots\\
That, in the opinion of the world, others may increase and I may decrease\ldots\\
That others may be chosen and I set aside\ldots\\
That others may be praised and I unnoticed\ldots\\
That others may be preferred to me in everything\ldots\\
That others may become holier than I, provided that I may become as holy as I should\ldots\\

\newpage

\prayersection{Sacrament of Reconciliation}
\prayertitle{Preparation for the Sacrament of Reconciliation}
% My Prayer Book, p. 93
Holy Spirit,
You came down upon the Apostles to enlighten their minds and strengthen their ministry.
Come down upon me at this important moment.
Help me to see my life in the light of Jesus Christ.
Renew my love as I am reconciled to God and His people.

\prayertitle{Prayer to the Holy Spirit before Confession}
% https://www.ourcatholicprayers.com/prayers-before-confession.html
O Holy Spirit, Source of all light, Spirit of wisdom, of understanding, and of knowledge, come to my assistance and enable me to make a good confession.
Enlighten me, and help me now to know my sins as one day I shall be forced to recognize them before Your judgment seat.
Bring to my mind the evil which I have done and the good which I have neglected.
Permit me not to be blinded by self-love.
Grant me, moreover, heartfelt sorrow for my transgressions, and the grace of a sincere confession, so that I may be forgiven and admitted into Your Friendship.

\prayertitle{Prayer Before Confession for Heavenly Aid}
% https://www.ourcatholicprayers.com/prayer-for-heavenly-aid.html
Father in heaven, most merciful God, relying on Your Goodness and Mercy, I come to You with childlike confidence to confess my sins and to beg Your Forgiveness.
You will not reject a contrite and humble heart.
Bless me and receive me again into Your Favor.
I realize that I have been most ungrateful to You, but I desire henceforth to keep Your commandments and to do Your Will in all things.

Jesus my Savior, my Good Shepherd, I did not follow in Your footsteps but have strayed far from the path that You have marked out for me.
Repentant and sorrowful, I beg to be admitted again into the fold of Your faithful followers.
I want to confess my sins with the same sincerity as I should wish to confess at the moment of my death.
My Jesus, I beg You for the grace to examine my conscience well.

Holy Spirit, come into my soul.
Enlighten my mind and strengthen my will that I may know my sins, humbly confess them, and sincerely amend my life.

Mary, my Mother, Immaculate Spouse of the Holy Spirit, refuge of sinners, help me by your kind prayers. Amen.

% Is this indulgenced? See Confiteor below.
\prayertitle{Act of Contrition}
% My Prayer Book, p. 30
My God,
I am sorry for my sins with all my heart.
In choosing to do wrong and failing to do good, I have sinned against You Whom I should love above all things.
I firmly intend, with Your help, to do penance, to sin no more, and to avoid whatever leads me to sin.
Our Savior Jesus Christ suffered and died for us.
In His Name, my God, have mercy.

\indulgencedprayertitle{The Confiteor}
\linkednote{grant9}{A partial indulgence is granted for devoutly reciting this prayer, especially in preparation for sacramental confession.}
I confess to almighty God and to you, my brothers and sisters, that I have greatly sinned, in my thoughts and in my words, in what I have done and in what I have failed to do, through my fault, through my fault, through my most grievous fault;
therefore I ask blessed Mary, ever Virgin, all the angels and saints, and you, my brothers and sisters, to pray for me to the Lord our God.

\prayertitle{Prayer After Confession to Strengthen Resolutions}
% https://www.ourcatholicprayers.com/prayer-for-resolutions-after-confession.html
Almighty and most merciful God, because of Your great Mercy You have been pleased to admit me once more to this Sacrament of forgiveness.
You have received me, though I have often gone astray from You.
I was an outcast, but You welcomed me back as a friend.
I thank You with all my heart for Your infinite Mercy and Kindness towards me, an ungrateful sinner.
In union with the Blessed Virgin Mary, the Refuge of sinners, I thank You for all the graces and blessings You have bestowed upon me in this Sacrament of Penance.

My dear God, I now renew the promises I have made in Baptism, and I give myself eternally to Your Love and service.
Give me the grace in the future to hate sin more than death itself and to avoid all such occasions and company as have in the past unhappily brought me to it.
Help me, O Lord, for I am weak.
Strengthen my resolutions and give me sufficient grace to overcome the evil promptings of my nature.
Never permit me to wound You again by my sins.
Refresh my soul that I may become strong in my determination to perform the duties of my state of life properly and fearlessly.
Through Your divine Grace, without which I can do nothing, help me to live a good life, die a happy death, save my immortal soul, and be happy with You for all eternity in heaven. Amen.

\prayertitle{Thanksgiving After Confession}
I return unto You, O Lord Jesus, and give You thanks that You have been pleased to cleanse me from the foul leprosy of my sins.
Blessed be Your Name, O Lord, forever and ever.
Truly You are a Savior Who rejects none that come unto You seriously desiring to repent, but receives them into Your favor, and numbers them with Your children.
I acknowledge and adore Your Mercy, and dedicate myself wholly to Your service hereafter.
Assist my weakness and suffer me not again to fall into my past sins and to be separated from You;
but so bind my heart and soul to You with the cords of Your Love, that I may say with the Apostle ``Who shall separate me from the Love of Christ?''

\prayertitle{Prayer After Confession by St. Frances Xavier Cabrini}
My dearest Jesus, I have told all my sins as well as I could.
I tried hard to make a good confession.
I feel sure that You have forgiven me.
I thank You.
It is only because of all Your sufferings that I can go to confession and free myself from my sins.
Your Heart is full of love and mercy for poor sinners.
I love You because You are so good to me.
My loving Savior, I shall try to keep from sin and to love You more each day.
My dear Mother Mary, pray for me and help me to keep my promises.
Protect me and do not let me fall back into sin.
Almighty God, kneeling before Your Divine Majesty, I adore You and because You command me, I dare approach Your divine Heart.
But what shall I say if You do not enlighten me with a ray of Your divine Light?

Speak to my soul, O Lord, and command me to listen to Your Voice.
Enlighten my will to put Your words into practice.
Pour Your Grace into my heart;
lift up my soul weighed down by my sins;
raise my mind to heavenly things, so that earthly desires may no longer appeal to me.
Speak to my soul with Your divine Omnipotence, for You are my salvation, my life, and my peace, in time and in eternity.
Strengthen me with the Grace of Your Holy Spirit and give Your Peace to my soul that I may be free from all needless worry and care.
Help me to desire always that which is pleasing and acceptable to You so that Your Will may be my will.
Grant that I may rid myself of all unholy desires, and that for Your Love I may remain unknown in this world, and be known only to You.

Do not permit me to attribute to myself the good that You perform in me and through me, but rather, referring all honor to Your Majesty, may I glory only in my weakness, so that renouncing sincerely all vain glory which comes from the world, I may aspire to the true and lasting glory which comes from You. Amen.

\newpage

\prayersection{Sacrament of Holy Communion}
% My Prayer book, p. 78
\prayertitle{Prayer of St. Thomas Aquinas before Holy Communion}
Almighty and ever-living God, I approach the sacrament of Your only-begotten Son, our Lord Jesus Christ.

I come sick to the doctor of life, unclean to the foundation of mercy, blind to the radiance of eternal light, and poor and needy to the Lord of heaven and earth.

Lord, in Your great Generosity, heal my sickness, wash away my defilement, enlighten my blindness, enrich my poverty, and clothe my nakedness.

May I receive the bread of angels, the King of Kings and Lord of Lords, with humble reverence, with the purity and faith, the repentance and love, and the determined purpose that will help to bring me to salvation.

May I receive the sacrament of the Lord's Body and Blood, and its reality and power.

Kind God, may I receive the body of Your only begotten Son, our Lord Jesus Christ, born from the womb of the Virgin Mary, and so be received into His mystical body and numbered among His members.

Loving Father, as on my earthly pilgrimage I now receive Your beloved Son under the veil of a sacrament, may I one day see Him face to face in glory, Who lives and reigns with You for ever.
Amen.

% My Prayer book, p. 80
%\begin{minipage}{\textwidth}
\prayertitle{Prayer of St. Ambrose before Holy Communion}
Lord Jesus Christ, I approach Your banquet table in fear and trembling, for I am a sinner, and dare not rely on my own worth but only on Your Goodness and Mercy.

I am defiled by many sins in body and soul, and by my unguarded thoughts and words.

Gracious God of majesty and awe, I seek Your Protection, I look for Your healing.

Poor troubled sinner that I am, I appeal to You, the fountain of all mercy.

I cannot bear Your Judgment, but I trust in Your salvation.

Lord, I show my wounds to You and uncover my shame before You.

I know my sins are many and great, and they fill me with fear, but I hope in Your Mercies, for they cannot be numbered.

Lord Jesus Christ, eternal King, God and man, crucified for mankind, look upon me with mercy and hear my prayer, for I trust in You.

Have mercy on me, full of sorrow and sin, for the depth of Your Compassion never ends.

Praise to You, saving sacrifice, offered on the wood of the cross for me and for all mankind.

Praise to the noble and precious Blood, flowing from the Wounds of my crucified Lord Jesus Christ and washing away the sins of the whole world.

Remember, Lord, Your creature, whom You have redeemed with Your Blood.

I repent my sins, and I long to put right what I have done.

Merciful Father, take away all my offenses and sins;
purify me in body and soul, and make me worthy to taste the holy of holies.

May Your Body and Blood, which I intend to receive, although I am unworthy, be for me the remission of my sins, the washing away of my guilt, the end of my evil thoughts, and the rebirth of my better instincts.

May it incite me to do the works pleasing to You and profitable to my health in body and soul, and be a firm defense against the wiles of my enemies.
Amen.
\newpage
\indulgencedprayertitle{\foreign{Anima Christi}}
\linkednote{grant8}{A partial indulgence is granted for making an act of thanksgiving after Communion using this prayer.}
Soul of Christ, sanctify me.
Body of Christ, save me.
Blood of Christ, inebriate me.
Water from the Side of Christ, wash me.
Passion of Christ, strengthen me.
O good Jesus, hear me.
Within Thy Wounds hide me.
Suffer me not to be separated from Thee.
From the malicious enemy defend me.
In the hour of my death call me.
And bid me come to Thee,
that with Thy saints I may praise Thee for ever and ever.
Amen.

\indulgencedprayertitle{\foreign{En ego, O bone et dulcissime Iesu}}
\linkednote{grant8}{A plenary indulgence is granted for devoutly reciting this prayer after Communion on any of the Fridays in Lent. A partial indulgence is granted for making an act of thanksgiving after Communion using this prayer.}
Behold, O kind and most sweet Jesus, I cast myself upon my knees in Thy Sight, and with the most fervent desire of my soul, I pray and beseech Thee that Thou wouldst impress upon my heart lively sentiments of faith, hope, and charity, with true contrition for my sins and a firm purpose of amendment;
while with deep affection and grief of soul I ponder within myself and mentally contemplate Thy five Wounds, having before my eyes the words which David the prophet put on Thy Lips concerning Thee:
``My Hands and My Feet they have pierced, they have numbered all My Bones.''

% My Prayer book, p. 86
\prayertitle{Prayer of St. Thomas Aquinas after Holy Communion}
Lord, Father all-powerful and ever-living God,

I thank You, for even though I am a sinner, Your unprofitable servant, not because of my worth but in the kindness of Your Mercy, You have fed me with the precious Body and Blood of Your Son, our Lord Jesus Christ.

I pray that this holy communion may not bring me condemnation and punishment but forgiveness and salvation.

May it be a helmet of faith and a shield of good will.

May it purify me from evil ways and put an end to my evil passions.

May it bring me charity and patience, humility and obedience, and growth in the power to do good.

May it be my strong defense against all my enemies, visible and invisible, and the perfect calming of all my evil impulses, bodily and spiritual.

May it unite me more closely to You, the one true God, and lead me safely through death to everlasting happiness with You.

And I pray that You will lead me, a sinner, to the banquet where You, with Your Son and Holy Spirit, are true and perfect light, total fulfillment, everlasting joy, gladness without end, and perfect happiness to Your saints.

Grant this through Christ our Lord. Amen.

\prayertitle{To our Redeemer after Holy Communion}
% My Prayer Book, p. 84
Jesus, may all that is You flow into me.
May Your Body and Blood be my food and drink.
May Your Passion and death be my strength and life.
Jesus, with You by my side enough has been given.
May the shelter I seek be the shadow of Your cross.
Let me not run from the love which You offer, but hold me safe from the forces of evil.
On each of my dyings shed Your Light and Your Love.
Keep calling to me until that day comes when, with Your saints, I may praise You for ever.
Amen.

\prayertitle{Act of Thanksgiving after Holy Communion}
% My Prayer Book, p. 87-89
From the depths of my heart I thank You, Lord, for Your infinite Kindness in coming to me.
How good You are to me!
With Your most holy Mother and all the angels, I praise Your Mercy and Generosity toward me.
I thank You for nourishing my soul with Your Sacred Body and Precious Blood.
I will try to show my gratitude to You in the Sacrament of Your Love, by loving obedience to Your holy commandments, by fidelity to my duties, by kindness to my neighbor, and by an earnest endeavor to become more like You in my daily conduct.

Grant that I may spend the hours of the day gladly working with You according to Your Will.

May I not lose my enthusiasm in serving You.
May my conversations be occasions of charity.
May I be patient with myself and those around me in the day's disappointments.
May I be mindful of others rather than myself in moments of fatigue and illness.
May I be generous and faithful so that when this day is over I may feel that life is really meaningful and peaceful, for it has been spent in Your loving company.
Amen.

\newpage

\prayersection{Eucharistic Adoration}
\indulgencedprayertitle{\foreign{O sacrum convivium}}
\linkednote{grant7}{A partial indulgence is granted for offering this prayer to Jesus present in the Blessed Sacrament.}
O sacred banquet, in which Christ is received, the memory of His Passion is renewed, the mind is filled with grace, and a pledge of future glory is given to us.

\indulgencedprayertitle{\foreign{Tantum ergo}}
\linkednote{grant7}{A plenary indulgence is granted for piously reciting the verses of this prayer after the Mass of the Lord's Supper on Holy Thursday during the solemn reposition of the Most Blessed Sacrament.
A partial indulgence is granted for offering this prayer to Jesus present in the Blessed Sacrament.}
Down in adoration falling,
Lo! the sacred Host we hail;
Lo! o'er ancient forms departing,
newer rites of grace prevail;
Faith for all defects supplying,
where the feeble senses fail.
To the everlasting Father,
and the Son Who reigns on high,
with the Holy Spirit proceeding
forth from each eternally
be salvation, honor, blessing,
might and endless majesty.
Amen.

\versicle\ You have given them bread from heaven,

\response\ Having all delight within it.

\versicle\ Let us pray.
O God, Who in this wonderful Sacrament left us a memorial of Your Passion:
grant, we implore You, that we may so venerate the sacred mysteries of Your Body and Blood, as always to be conscious of the fruit of Your Redemption.
You Who live and reign forever and ever.

\response\ Amen.

\prayertitle{Aspirations to Our Lord in the Blessed Sacrament}
% https://www.ourcatholicprayers.com/aspirations.html. Also in Laudate app under the same name.
Jesus, my God, here present in the Sacrament of Your Love, I adore You. 
O Jesus in the Blessed Sacrament, have mercy on us. 
O Jesus, in the most holy Sacrament, have mercy on us. 
Praised and adored forever be the most holy Sacrament. 
We adore You, true Bread of angels. 

\newpage

\prayersection{Penitential Psalms}
\linkednote{grant9}{A partial indulgence is granted for devoutly reciting any of the penitential psalms, especially in preparation for sacramental confession.}
% http://www.usccb.org/bible/psalms/6
\indulgencedprayertitle{Psalm 6}
Do not reprove me in Your Anger, Lord,
nor punish me in Your Wrath.
Have pity on me, Lord, for I am weak;
heal me, Lord, for my bones are shuddering.
My soul too is shuddering greatly -- and You, Lord, how long?
Turn back, Lord, rescue my soul;
save me because of Your Mercy.

For in death there is no remembrance of You.
Who praises You in Sheol?

I am wearied with sighing;
all night long I drench my bed with tears;
I soak my couch with weeping.
My eyes are dimmed with sorrow, worn out because of all my foes.

Away from me, all who do evil!
The Lord has heard the sound of my weeping.
The Lord has heard my plea;
the Lord will receive my prayer.
My foes will all be disgraced and will shudder greatly;
they will turn back in sudden disgrace.

% http://www.usccb.org/bible/psalms/32
\indulgencedprayertitle{Psalm 32}
Blessed is the one whose fault is removed, whose sin is forgiven.
Blessed is the man to whom the Lord imputes no guilt, in whose spirit is no deceit.

Because I kept silent, my bones wasted away;
I groaned all day long.
For day and night Your Hand was heavy upon me;
my strength withered as in dry summer heat.

Then I declared my sin to You;
my guilt I did not hide.
I said, ``I confess my transgression to the Lord,'' and You took away the guilt of my sin.

Therefore every loyal person should pray to You in time of distress.
Though flood waters threaten, they will never reach Him.
You are my shelter; You guard me from distress;
with joyful shouts of deliverance You surround me.

I will instruct you and show you the way you should walk, give you counsel with my eye upon you.
Do not be like a horse or mule, without understanding;
with bit and bridle their temper is curbed, else they will not come to you.

Many are the sorrows of the wicked one, but mercy surrounds the one who trusts in the Lord.
Be glad in the Lord and rejoice, you righteous;
exult, all you upright of heart.

% http://www.usccb.org/bible/psalms/38
\indulgencedprayertitle{Psalm 38}
Lord, do not punish me in Your Anger;
in Your Wrath do not chastise me!
Your arrows have sunk deep in me;
Your Hand has come down upon me.
There is no wholesomeness in my flesh because of Your Anger;
there is no health in my bones because of my sin.
My iniquities overwhelm me, a burden too heavy for me.

Foul and festering are my sores because of my folly.
I am stooped and deeply bowed;
every day I go about mourning.
My loins burn with fever;
there is no wholesomeness in my flesh.
I am numb and utterly crushed;
I wail with anguish of heart.
My Lord, my deepest yearning is before You;
my groaning is not hidden from You.
My heart shudders, my strength forsakes me;
the very light of my eyes has failed.
Friends and companions shun my disease;
my neighbors stand far off.

Those who seek my life lay snares for me;
they seek my misfortune, they speak of ruin;
they plot treachery every day.

But I am like the deaf, hearing nothing, like the mute, I do not open my mouth;
I am even like someone who does not hear, who has no answer ready.
Lord, it is for You that I wait;
O Lord, my God, You respond.
For I have said that they would gloat over me, exult over me if I stumble.

I am very near to falling;
my wounds are with me always.
I acknowledge my guilt
and grieve over my sin.
My enemies live and grow strong, those who hate me grow numerous fraudulently.
Repaying me evil for good,
accusing me for pursuing good.
Do not forsake me, O Lord;
my God, be not far from me!
Come quickly to help me, my Lord and my salvation!

% http://www.usccb.org/bible/psalms/51
\indulgencedprayertitle{\foreign{Miserere} (Psalm 51)}
Have mercy on me, God, in accord with Your merciful Love;
in Your abundant Compassion blot out my transgressions.
Thoroughly wash away my guilt;
and from my sin cleanse me.
For I know my transgressions;
my sin is always before me.
Against You, You alone have I sinned;
I have done what is evil in Your Eyes;
so that You are just in Your Word, and without reproach in Your Judgment.
Behold, I was born in guilt, in sin my mother conceived me.
Behold, You desire true sincerity;
and secretly You teach me wisdom.
Cleanse me with hyssop, that I may be pure;
wash me, and I will be whiter than snow.
You will let me hear gladness and joy;
the bones You have crushed will rejoice.

Turn away Your Face from my sins;
blot out all my iniquities.
A clean heart create for me, God;
renew within me a steadfast spirit.
Do not drive me from before Your Face, nor take from me Your Holy Spirit.
Restore to me the gladness of Your salvation;
uphold me with a willing spirit.
I will teach the wicked Your ways, that sinners may return to You.
Rescue me from violent bloodshed, God, my saving God, and my tongue will sing joyfully of Your Justice.
Lord, You will open my lips;
and my mouth will proclaim Your praise.
For You do not desire sacrifice or I would give it;
a burnt offering You would not accept.
My sacrifice, O God, is a contrite spirit;
a contrite, humbled heart, O God, You will not scorn.

% http://www.usccb.org/bible/psalms/102
\indulgencedprayertitle{Psalm 102}
Lord, hear my prayer;
let my cry come to You.
Do not hide Your Face from me in the day of my distress.
Turn Your Ear to me;
when I call, answer me quickly.
For my days vanish like smoke;
my bones burn away as in a furnace.
My heart is withered, dried up like grass, too wasted to eat my food.
From my loud groaning I become just skin and bones.
I am like a desert owl, like an owl among the ruins.
I lie awake and moan, like a lone sparrow on the roof.
All day long my enemies taunt me;
in their rage, they make my name a curse.
I eat ashes like bread, mingle my drink with tears.
Because of Your furious Wrath, You lifted me up just to cast me down.
My days are like a lengthening shadow;
I wither like the grass.

But You, Lord, are enthroned forever;
Your Renown is for all generations.
You will again show mercy to Zion;
now is the time for pity;
the appointed time has come.
Its stones are dear to Your servants;
its dust moves them to pity.
The nations shall fear Your Name, Lord,
all the kings of the earth, Your Glory.
Once the Lord has rebuilt Zion and appeared in glory, heeding the plea of the lowly, not scorning their prayer.
Let this be written for the next generation, for a people not yet born, that they may praise the Lord.
``The Lord looked down from the holy heights, viewed the earth from heaven, to attend to the groaning of the prisoners, to release those doomed to die.''
Then the Lord's Name will be declared on Zion, His praise in Jerusalem, when peoples and kingdoms gather to serve the Lord.

He has shattered my strength in mid-course, has cut short my days.
I plead, O my God, do not take me in the midst of my days.
Your years last through all generations.
Of old You laid the earth's foundations;
the heavens are the work of Your Hands.
They perish, but You remain;
they all wear out like a garment;
Like clothing You change them and they are changed, but You are the same, Your years have no end.
May the children of Your servants live on;
may their descendants live in Your Presence.

% http://www.usccb.org/bible/psalms/130
\indulgencedprayertitle{\foreign{De profundis} (Psalm 130)}
Out of the depths I call to You, Lord;
Lord, hear my cry!
May Your Ears be attentive to my cry for mercy.
If You, Lord, keep account of sins, Lord, who can stand?
But with You is forgiveness and so You are revered.

I wait for the Lord, my soul waits and I hope for His word.
My soul looks for the Lord more than sentinels for daybreak.
More than sentinels for daybreak, let Israel hope in the Lord,
For with the Lord is mercy, with Him is plenteous redemption, and He will redeem Israel from all its sins.

% http://www.usccb.org/bible/psalms/143
\indulgencedprayertitle{Psalm 143}
Lord, hear my prayer;
in Your Faithfulness listen to my pleading;
answer me in Your Righteousness.
Do not enter into judgment with Your servant;
before You no one can be just.
The enemy has pursued my soul;
he has crushed my life to the ground.
He has made me dwell in darkness like those long dead.
My spirit is faint within me;
my heart despairs.
I remember the days of old;
I ponder all Your deeds;
the works of Your Hands I recall.
I stretch out my hands toward You, my soul to You like a parched land.

Hasten to answer me, Lord;
for my spirit fails me.
Do not hide Your Face from me,
lest I become like those descending to the pit.
In the morning let me hear of Your Mercy, for in You I trust.
Show me the path I should walk, for I entrust my life to You.
Rescue me, Lord, from my foes, for I seek refuge in You.
Teach me to do Your Will, for You are my God.
May Your kind Spirit guide me on ground that is level.
For Your Name's sake, Lord, give me life;
in Your Righteousness lead my soul out of distress.
In Your Mercy put an end to my foes;
all those who are oppressing my soul, for I am Your servant.

% Add gradual psalms (119-133) since they are all indulgenced

\newpage

\prayersection{Prayers for Seasons of the Liturgical Year}
\prayertitle{Advent}
Father of our Lord Jesus Christ, ever faithful to Your promises and ever close to Your Church: the earth rejoices in hope of the Savior's coming and looks forward with longing to His return at the end of time.
Prepare my heart during this Advent Season.
Increase my longing for Christ my Savior and give me the strength to grow in love.

Jesus, my Lord, save me from my sins.
Come, protect me from all dangers and lead me to salvation.

Sanctify me in mind and body, Lord, keep me without sin until the coming of Your Son.
Make me walk these days in holiness, Lord, and live an upright and devout life in this world.
Prepare a path in my heart for the coming of Your Word and let His glory be revealed through my good works.

Bring low the mountains of my pride, Lord, and fill up the valleys of my weakness.

Keep me in the Love of Your Spirit, Lord, that I may receive the Mercy of Your Son Who is to come.

I long for the grace of Your coming, Lord, console me with the gift of Your own divine Life.

\prayertitle{Christmas}
God of love the darkness that covered the earth has given way to the bright dawn of Your Word made flesh.
Help me to walk in this light.
May I be faithful to Your Word and bring Your Life to the waiting world.

At this time of Your holy birth, Lord Jesus, I pray that my life may give glory to You.
Since Your birth was here on earth, I hope You will someday give me my own birth in heaven.

You saved me by Your birth, Lord Jesus, help me to be faithful to the promises of my baptism.

Increase the hope of the weak, the poor and the aged, give relief to the oppressed and consolation to those who mourn.

You are the Prince of peace, Lord Jesus, grant the world that peace which the angels proclaimed.

Give me a heart that is upright and sincere so that I may listen to Your Word.

You shine on those who dwell in darkness, give me holiness, justice, and peace.

You became our brother by being born of the Virgin Mary, teach me to love all as my brothers and sisters.

\prayertitle{Lent}
Heavenly Father, I am called to walk by the Light of Christ, Your Son, and to trust in His wisdom.
During Lent, I submit my self to Him more and more and am striving to believe in Him with all my heart.
I enter on this path of repentance so that in dying to self I might rise to new life.

Lord Jesus, You spoke peace to a sinful world and brought mankind the gift of reconciliation by the suffering and death You endured.
I love You and joyfully bear the name `Christian'.
Teach me to follow Your example.
Increase my faith, hope, and charity so that I may struggle to turn hatred to love and conflict to peace.

Loving Redeemer, through Your Passion teach me self-denial, strengthen me against evil and adversity and so make me ready to celebrate Your Resurrection.

Healer of body and soul, cure the sickness in my spirit so that I may grow in holiness through Your constant care.

Forgive my sins against the unity of Your family, make me love as You loved me.

Good Master, make me mindful of the dignity You gave me in Baptism, may I live for You at every moment.

Give me a perfect heart to receive Your work, that I may bring forth fruit in patience.

Renew my eagerness to work with You in building a better world, so that my friends may hear Your gospel of peace and justice.

\prayertitle{Easter}
Heavenly Father and God of Mercy, I believe that Jesus is alive and has become the Lord of life.
From the waters of Baptism You have raised me with Him and renewed Your gift of life within me.
Increase in my mind and heart the risen life I share with Christ and help me to grow in Your Wisdom and Grace.

Lord Jesus, You appeared to Your apostles after the resurrection and filled their hearts with joy when You said to them, ``Peace be with you''.
May the peace of Your Presence abide with me and make each day You give me the most beautiful day of my life.

Lord Jesus, You triumphed over death and destroyed the power of death in me, may I live only for You.

Risen Lord, You brought confusion on the guards at Your tomb but joy to Your disciples, grant me the fullness of joy as I serve You in spirit and truth.

You promised to be with Your disciples, Lord, to the end of the world, stay with me today and remain with me always.

King of glory, center of my life, grant that when You come again, I may be one with You in glory.

Lord, remember me as in my own way I minister to Your people, may my life be holy and an example to Your people.

Lord Jesus, purify my heart with Your Truth and guide me in the way of holiness, so that I may always do what is pleasing in Your Sight.

\prayertitle{Pentecost}
Father of Light, from Whom every good gift comes, send Your Spirit into my life with the power of a mighty wind.
May He recall to my memory the words of Jesus and keep them in my heart.

Jesus, Your Spirit renews the face of the earth and fills the whole universe.
May it renew the depth of my heart so that You may always find in my heart and on my lips a prayer pleasing to You.

Lord Jesus, when You were raised high upon the cross, streams of living water flowed from Your pierced Side, pour out on me Your life-giving Spirit.

You promised to send the Holy Spirit to bear witness to Yourself, renew Your Spirit within me to make me Your faithful witness.

You desire the whole world to be filled with Your Spirit, help me to build a world of justice and peace.

You desire the unity of all Christians through one baptism in the Spirit, make all who believe one in heart and soul.

Lord Jesus, You gave Your Spirit to the apostles with the power to forgive sins, destroy all sin in the world.

You promised the Holy Spirit to teach and remind Your followers of all You have said, send me that Spirit to enlighten my mind in faith.

\newpage

\prayersection{Creeds}
% TODO Note that a plenary indulgence is granted on All Souls' Day for devoutly visiting a church or an oratory and reciting an Our Father and the Creed.
\linkednote{grant28}{A partial indulgence is granted for devoutly reciting either the Apostles' Creed or the Niceno-Constantinopolitan Creed.}
\indulgencedprayertitle{The Nicene Creed}
I believe in one God, the Father almighty, maker of heaven and earth, of all things visible and invisible.
I believe in one Lord Jesus Christ, the Only Begotten Son of God, born of the Father before all ages.
God from God, Light from Light, true God from true God, begotten, not made, consubstantial with the Father;
through Him all things were made.
For us men and for our salvation He came down from heaven, and by the Holy Spirit was incarnate of the Virgin Mary, and became man.
For our sake He was crucified under Pontius Pilate, He suffered death and was buried, and rose again on the third day in accordance with the Scriptures.
He ascended into heaven and is seated at the right Hand of the Father.
He will come again in glory to judge the living and the dead and His kingdom will have no end.
I believe in the Holy Spirit, the Lord, the giver of life, Who proceeds from the Father and the Son, Who with the Father and the Son is adored and glorified, Who has spoken through the prophets.
I believe in one, holy, catholic and apostolic Church.
I confess one Baptism for the forgiveness of sins and I look forward to the resurrection of the dead and the life of the world to come.
Amen.

\indulgencedprayertitle{The Apostles' Creed}
I believe in God, the Father almighty, Creator of heaven and earth.
I believe in Jesus Christ, His only Son, our Lord.
He was conceived by the Power of the Holy Spirit and born of the Virgin Mary.
He suffered under Pontius Pilate, was crucified, died, and was buried.
He descended to the dead.
On the third day He rose again.
He ascended into heaven, and is seated at the right Hand of the Father.
He will come again to judge the living and the dead.
I believe in the Holy Spirit, the holy catholic Church, the communion of saints, the forgiveness of sins, the resurrection of the body, and life everlasting.
Amen.

\newpage

\prayersection{Blessings}
\note{Blessings for children may be said by the parent at various times, such as when a child is going to play or to school, but especially when the child is going to bed each night.
The parent makes the sign of the cross on the child's forehead or heart and says the blessing.}

\prayertitle{Blessing of a Child}
\label{prayer:blessing_child}
May almighty God, Father, Son, and Holy Spirit, bless you, my child, for time and eternity, and may this blessing remain forever with you.

\prayertitle{Blessing of the Patriarchs}
\label{prayer:blessing_patriarchs}
\note{From Numbers 6:24-26.}
The Lord bless you and keep you;
the Lord make His face to shine upon you, and be gracious to you;
the Lord lift up His countenance upon you, and give you peace.

\prayertitle{Blessing on a Child's Birthday}
\label{prayer:blessing_child_birthday}
\note{From Jeremiah 1:5.}
The Lord said to Jeremiah:
Before I formed you in the womb I knew you, before you were born I dedicated you.

May God, in whose presence our ancestors walked, bless you.

\response Amen.

May God, Who has been your shepherd from birth until now, keep you.

\response Amen.

May God, Who saves you from all harm, give you peace.

\response Amen.
\newpage
\prayertitle{Travel Blessing}
\label{prayer:travel_blessing}
\note{Based on Tobit's blessing of Tobias (Tobit 5).}
May God in heaven bring you safely there and return you in good health;
and may His angel accompany you for your safety.

\prayertitle{Blessing of Parents Before the Birth of Their Child}
\label{prayer:parents_before_birth_of_child}
Gracious Father, Your Word, spoken in love, created the human family and, in the fullness of time, Your Son, conceived in love, restored it to Your friendship.
Hear the prayers of parents awaiting the birth of a child, calm their fears when they are anxious.
Watch over and support these parents and bring their child into this world safely and in good health, so that as members of Your family they may praise You and glorify You through Your Son, our Lord Jesus Christ, now and forever.
Amen.

\prayertitle{Blessing of a Mother Before Childbirth}
\label{prayer:mother_before_childbirth}
God has brought gladness and light to the world through the Virgin Mary's delivery of her child.
May Christ fill your heart with His holy joy and keep you and your baby safe from harm. 
In the Name of the Father, and of the Son, and of the Holy Spirit.

\newpage

% TODO Add group prayers. Some prayers suitable for groups are indulgenced (see, e.g., Grant 25).

\prayersection{For Particular Occasions}
\indulgencedprayertitle{\foreign{Adsumus}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering prayer of supplication such as this one when starting and completing work, which is said before a meeting dealing with matters of common interest.}
We have come, O Lord, Holy Spirit, we have come before You, hampered indeed by our many and grievous sins, but for a special purpose gathered together in Your Name.
Come to us, be with us, and enter our hearts.
Teach us what we are to do and what ought to concern us;
show us what we must accomplish, in order that, with Your help, we may be able to please You in all things.
May You alone be the author and the finisher of our judgments, Who alone with God the Father and His Son possess a glorious Name.
Do not allow us to disturb the order of justice, You Who love equity above all things.
Let not ignorance draw us into devious paths.
Let not partiality sway our minds or respect of riches or persons pervert our judgment.
But unite our hearts to You by the gift of Your Grace alone, that we may be one in You and never forsake the truth;
as we are gathered together in Your Name, so may we in all things hold fast to justice tempered by mercy, that in this life our judgment may never be at variance with You and in the life to come we may attain to everlasting rewards for deeds well done.
Amen.

\prayertitle{Prayer of a Couple on the Anniversary of Marriage}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/anniversary-of-marriage.cfm Text adapted from the English translation of The Order of Celebrating Matrimony © 2013, International Commission on English in the Liturgy Corporation. All rights reserved. This form is not approved for liturgical use.
We praise You, O God, we bless You, Creator of all things, Who in the beginning made man and woman that they might form a communion of life and love.

We also give You thanks for graciously blessing our family life so that it might present an Image of Christ's union with the Church.

Therefore look with kindness upon us today, and as You have sustained our communion amid joys and struggles, renew our Marriage covenant each day, increase our charity, and strengthen in us the bond of peace, so that we may for ever enjoy Your blessing.
Through Christ our Lord. Amen.

\prayertitle{For Babies About to Be Born}
\label{prayer:babies_about_to_be_born}
Heavenly Father, from the moment these children were conceived, You knew their names.
In the silent first hours of their lives, as cells divided and their living flesh quickened, Your Love breathed deep within and they began to grow in Your Image and Likeness.
May our prayers be accompanied by choirs of angels as we await their births.
We ask this through Your Child Who was formed in the Virgin's womb and Who lived and died for us, Lord, forever and ever. Amen.

\prayertitle{Thanksgiving for a Newborn or Newly Adopted Young Child}
\label{prayer:thanksgiving_newborn}
God, our Creator, cherish this child.
Jesus, our Savior; protect him/her.
Holy Spirit, our comforter, strengthen him/her.

Source of all blessings, protector of infants, look with favor on this child, \insertname.

Hold him/her gently in your hands.
When he/she is reborn of water and the Holy Spirit, bring him/her into the Church, there to share in your kingdom and with us to bless Your Name forever.
We ask this through Christ our Lord.

\response Amen.

\instruction{The parents trace the sign of the cross on the child's forehead.}

\insertname, may the Lord Jesus, Who loved children, bless you and keep you in His love, now and forever.

\response Amen.

\prayertitle{Prayer on Bringing a Child into the Home}
\label{prayer:bringing_child_into_home}
Good Lord, You have tenderly loved us, and given us this home and good friends.
May we make a true home for this child, where he/she will learn trust in us and in You.
May his/her brothers and sisters rejoice in their own growing up as they help to care for this child.
We ask this through Christ our Lord.

\response Amen.

\prayertitle{For Travelers}
\label{prayer:travelers}
O Almighty and merciful God, Who has commissioned Your angels to guide and protect us, command them to be our assiduous companions from our setting out until our return;
to clothe us with their invisible protection;
to keep from us all danger of collision, of fire, of explosion, of fall and bruises, and finally, having preserved us from all evil, and especially from sin, to guide us to our heavenly home.
Through Jesus Christ, our Lord. Amen.

\prayertitle{For a Safe Flight}
Dear God, please watch over me as I fly out today.
May Your Hand be on the pilot and crew, Your Strength be in the engineers that prepare the plane, and Your Wisdom over the control teams on the ground.

I choose to trust in You, and give You my fears and anxieties.
May I find peace as I travel.
Take my heart on a journey of trust and hope as I look out over the beautiful world You have made.

I travel with You.
Calm me and cover me,
Amen.

\prayertitle{For Times of Trouble}
\label{prayer:times_of_trouble}
Praised be God, the Father of our Lord Jesus Christ, the Father of mercies and the God of all consolation, Who comforts us in all our afflictions.

May God, the source of all patience and encouragement, enable us to live in perfect harmony with one another according to the Spirit of Christ Jesus.

\response Amen.

May the Lord make us overflow with love for one another and for all.
May God strengthen our hearts.

\response Amen

God of all our days: like a parent you forgive us, and like a child you love us.
May we love and forgive one another.

\prayertitle{Prayer to St. Peregrine for Those Sick with Cancer}
O great St. Peregrine, you have been called ``The Mighty,'' ``The Wonder-Worker,'' because of the numerous miracles which you have obtained from God for those who have had recourse to you.
For so many years you bore in your own flesh this cancerous disease that destroys the very fiber of our being, and who had recourse to the source of all grace when the power of man could do no more.
You were favored with the vision of Jesus coming down from His Cross to heal your affliction.
Ask of God and Our Lady, the cure of the sick whom we entrust to you: \insertname.
Aided in this way by your powerful intercession, we shall sing to God, now and for all eternity, a song of gratitude for His great Goodness and Mercy.
Amen.

\prayertitle{Prayer to St. Peregrine for Help with Cancer}
St. Peregrine, whom Holy Mother Church has declared Patron of those suffering from cancer, I confidently turn to you for help in my present sickness.
I beg your kind intercession.
Ask God to relieve me of this sickness, if it be His Holy Will.
Plead with the Blessed Virgin Mary, the Mother of Sorrows, whom you loved so tenderly and in union with whom you have suffered the pains of cancer, that she may help me with her powerful prayers and loving consolation.

But if it should be God's Holy Will that I bear this sickness, obtain for me courage and strength to accept these trials from the loving Hand of God with patience and resignation, because He knows what is best for the salvation of my soul.
St. Peregrine, be my friend and patron.
Help me to imitate you in accepting suffering, and to unite myself with Jesus Crucified and the Mother of Sorrows, as you did.
I offer my pains to God with all the love of my heart, for His glory and the salvation of souls, especially my own.
Amen.

\prayertitle{For All about to Die}
% http://www.usccb.org/issues-and-action/human-life-and-dignity/assisted-suicide/to-live-each-day/upload/prayer-resources.pdf
Lord Jesus Christ, as You stood by the bed of good Saint Joseph and gently led him home to heaven, so shepherd every soul about to die to a paradise of perfect peace.
Let the tears we shed upon their passing stand witness to our love for them and the depth of our thanksgiving for the gift of their lives and the grace of a good death.
For You are Lord, forever and ever.
Amen.

\prayertitle{Prayer of Commendation}
% http://www.usccb.org/prayer-and-worship/bereavement-and-funerals/prayers-for-death-and-dying.cfm
\note{Said as the time of death approaches.}
Go forth, Christian soul, from this world in the Name of God the almighty Father, Who created you, in the Name of Jesus Christ, Son of the living God, Who suffered for you, in the Name of the Holy Spirit, Who was poured out upon you, go forth, faithful Christian.

May you live in peace this day, may your home be with God in Zion, with Mary, the Virgin Mother of God, with Joseph, and all the Angels and Saints.

\prayertitle{Aspiration of the Dying}
% https://www.ourcatholicprayers.com/aspirations-for-the-dying.html. Also from the Laudate app under ``Aspirations for the Dying''
Good Jesus, give me a deep love for You, that nothing may be too hard for me to bear from You.

You know Lord, that I am all weakness; teach me to bear my cross.
Bear it for me, bear it in me.

O Good Jesus, my God and my All, keep me ever near You, let nothing for a moment separate me from You

Good Jesus, to You I flee;
hide me in Your sacred Side.

O Good Jesus, shelter me from the evil one, shed Your dew upon me to calm my soul, and dwell in me fully, that I may wholly love You.

Good Jesus, Who has borne so patiently with me;
make me wholly patient for love of You.

Good Jesus, lead me that I may follow You; hold me that I may cling fast to You;
teach me, that I may choose You alone; keep me that I may be Yours for ever.

\prayertitle{Prayer of Those in Their Last Agony}
% https://www.ourcatholicprayers.com/aspirations-for-the-dying.html. Also from the Laudate app under ``Aspirations for the Dying''
Jesus, Mary, and Joseph, I give you my heart and my soul.
Jesus, Mary, and Joseph, assist me in my last agony.
Jesus, Mary, and Joseph, may I breathe forth my soul in peace with you.

Into Your Hands, O Lord, I commend my spirit.
O Lord Jesus Christ, receive my spirit.

Holy Mary, pray for me.
O Mary, mother of grace, mother of mercy, protect me from the enemy, and receive me at the hour of death.

St. Joseph, pray for me.
St. Joseph, with the Blessed Virgin, your Spouse, open to me the bosom of divine mercy.

% Prayers in times of war: http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-troops.cfm

\newpage
\appendix
\section{References to the Manual of Indulgences}
\subsection{Relevant Norms}
\newcommand{\norm}[1]{\textbf{N#1.}\newline}
\newcommand{\subnorm}[1]{\sectionsign{}#1.}
\norm{1}
An indulgence is a remission before God of the temporal punishment for sins, whose guilt is forgiven, which a properly disposed member of the Christian faithful obtains under certain and clearly defined conditions through the intervention of the Church, which, as the minister of Redemption, dispenses and applies authoritatively the treasury of the expiatory works of Christ and the saints.

\norm{3}
The faithful can obtain partial or plenary indulgences for themselves, or they can apply them to the dead by way of suffrage.

\norm{17}
\subnorm{1} In order to be capable of gaining indulgences one must be baptized, not excommunicated, and in the state of grace at least at the completion of the prescribed works.

\subnorm{2} To gain an indulgence, one must have at least the general intention of doing so and must carry out the enjoined works at the stated time and in due fashion, according to the sense of the grant.

\norm{18}
\subnorm{1} A plenary indulgence can be acquired only once in the course of a day; a partial indulgence can be acquired multiple times.

\subnorm{2} The faithful however can obtain the plenary indulgence at the hour of death, even if they have already gained one on the same day.

\norm{20}
\subnorm{1} To gain a plenary indulgence, in addition to excluding all attachment to sin, even venial sin, it is necessary to perform the indulgenced work and fulfill the following three conditions:
sacramental confession, Eucharistic Communion, and prayer for the intention of the Sovereign Pontiff.

\subnorm{2} A single sacramental confession suffices for gaining several plenary indulgences;
but Holy Communion must be received and prayer for the intention of the Holy Father must be recited for the gaining of each plenary indulgence.

\subnorm{3} The three conditions may be fulfilled several days before or after the performance of the prescribed work;
it is, however, fitting that Communion be received and the prayer for the intention of the Holy Father be said on the same day the work is performed.

\subnorm{4} If the full disposition is lacking, or if the work and the three prescribed conditions are not fulfilled, saving the provisions given in Norm 24 and in Norm 25 regarding those who are ``impeded,'' the indulgence will only be partial.

\subnorm{5} The condition of praying for the intention of the Holy Father is fully satisfied by reciting one Our Father and one Hail Mary;
nevertheless, one has the option of reciting any other prayer according to individual piety and devotion, if recited for this intention.

\norm{22} An indulgence attached to a prayer can be acquired by reciting the prayer in any language, provided that the translation is approved by the competent ecclesiastical authority.

\norm{23} To gain an indulgence it is sufficient to recite the prayer alternately with a companion or to follow it mentally while it is being recited by another.

\subsection{Grants for Prayers}
% Consider indenting subgrants and subsubgrants using a method described at:
% https://tex.stackexchange.com/questions/35933/indenting-a-whole-paragraph
% package enumitem might be useful here too
\newcommand{\grant}[2]{\subsubsection*{#1 #2}}
\newcommand{\subgrant}[1]{\sectionsign{}#1.}
\newcommand{\subsubgrant}[1]{#1\degreesign{}}
\hypertarget{grant2}{\grant{2}{Act of Dedication of the Human Race to Jesus Christ the King}}
A plenary indulgence is granted to the faithful who on the solemnity of Our Lord Jesus Christ, King of the Universe, publicly recite the act of dedication of the human race to Christ the King (\foreign{Iesu dulcissime, Redemptor});
a partial indulgence is granted for its use in other circumstances.

\hypertarget{grant3}{\grant{3}{Act of Reparation}}
A plenary indulgence is granted to the faithful who, on the solemnity of the Most Sacred Heart of Jesus, publicly recite the act of reparation (\foreign{Iesu dulcissime}); a partial indulgence is granted for its use in other circumstances.

\hypertarget{grant7}{\grant{7}{Eucharistic Adoration and Procession}}
\subgrant{1} A plenary indulgence is granted to the faithful who \subsubgrant{2} piously recite the verses of the \foreign{Tantum ergo} after the Mass of the Lord's Supper on Holy Thursday during the solemn reposition of the Most Blessed Sacrament.

\subgrant{2} A partial indulgence is granted to the faithful who \subsubgrant{2} offer any duly approved prayer to Jesus present in the Blessed Sacrament (e.g., the \foreign{Adoro te devote}, the prayer \foreign{O sacrum convivium}, or the \foreign{Tantum ergo}).

\hypertarget{grant8}{\grant{8}{Eucharistic and Spiritual Communion}}

\subgrant{1} A plenary indulgence is granted to the faithful who \subsubgrant{2} on any of the Fridays of Lent devoutly recite after Communion the prayer \foreign{En ego, O bone et dulcissime Iesu} before a crucifix.

\subgrant{2} A partial indulgence is granted to the faithful who, using any duly approved pious formula, make

\subsubgrant{1} an act of spiritual communion;

\subsubgrant{2} an act of thanksgiving after Communion (e.g., \foreign{Anima Christi}; \foreign{En ego, O bone et dulcissime Iesu}).

\hypertarget{grant9}{\grant{9}{Examination of Conscience and Act of Contrition}}
A partial indulgence is granted to the faithful who, especially in preparation for sacramental confession,

\subgrant{1} examine their conscience with the purpose of amendment;

\subgrant{2} devoutly recite an act of contrition, according to any legitimate formula (e.g., the \foreign{Confiteor}, the psalm \foreign{De profundis}, or the psalm \foreign{Miserere}, or any of the gradual or penitential psalms).

\hypertarget{grant11}{\grant{11}{Week of Prayer for Christian Unity}}
\subgrant{2} A partial indulgence is granted to the faithful who devoutly recite an appropriately approved prayer for the unity of Christians (e.g. \foreign{Omnipotens et misericors Deus}).

\grant{15}{Mental Prayer}
A partial indulgence is granted to the faithful who for their personal edification devoutly spend time in mental prayer.

\hypertarget{grant17}{\grant{17}{Prayers to the Blessed Virgin Mary}}
\subgrant{1} A plenary indulgence is granted to the faithful who

\subsubgrant{1} devoutly recite the Marian rosary in a church or oratory, or in a family, a religious community, or an association of the faithful, and in general when several of the faithful gather for some honest purpose;

\subsubgrant{2} devoutly join in the recitation of the rosary while it is being recited by the Supreme Pontiff and broadcast live by radio or television.

In other circumstances, the indulgence will be partial.

The rosary is a prayer formula consisting of fifteen decades of Hail Marys preceded by the Our Father, during the recitation of which we piously meditate on the corresponding mysteries of our redemption.
Regarding the plenary indulgence for the recitation of the Marian rosary, the following is prescribed:
\begin{enumerate}
	\item The recitation of a third part of the rosary is sufficient, but the five decades must be recited without interruption.
	\item Devout meditation on the mysteries is to be added to the vocal prayer.
	\item In its public recitation the mysteries must be announced in accord with approved local custom, but in its private recitation it is sufficient for the faithful simply to join meditation on the mysteries to the vocal prayer.
\end{enumerate}

\subgrant{2} A partial indulgence is granted to the faithful who

\subsubgrant{1} devoutly recite the canticle of the \foreign{Magnificat};

\subsubgrant{2} either at dawn, noon, or evening devoutly recite the \foreign{Angelus} with its accompanying versicles and prayer or, during the Easter season, the \foreign{Regina caeli} antiphon with its usual prayer;

\subsubgrant{3} devoutly address the Blessed Virgin Mary with some approved prayer (e.g., \foreign{Maria, Mater gratiae}; the \foreign{Memorare}; the \foreign{Salve Regina}; the \foreign{Sancta Maria, succurre miseris}; or the \foreign{Sub tuum praesidium}.)

\hypertarget{grant18}{\grant{18}{Prayers to One's Guardian Angel}}
A partial indulgence is granted to the faithful who devoutly invoke the care of their guardian Angel with a duly approved prayer (e.g. \foreign{Angele Dei}).

\hypertarget{grant19}{\grant{19}{Prayers in Honor of St. Joseph}}
A partial indulgence is granted to the faithful who invoke St. Joseph, spouse of the Blessed Virgin Mary, with a duly approved prayer (e.g., \foreign{Ad te, beate Ioseph}).

\hypertarget{grant20}{\grant{20}{Prayers in Honor the Apostles Peter and Paul}}
A partial indulgence is granted to the faithful who devoutly recite the prayer \foreign{Sancti Apostoli Petre et Paule}.

\hypertarget{grant23}{\grant{23}{Prayers of the Eastern Churches}}
\subgrant{2} A partial indulgence is granted to the faithful who, in accordance with particular times and circumstances, devoutly recite one of the following prayers: a Prayer of Thanksgiving (from the Armenian tradition); Evening Prayer, Prayer for the Faithful Departed (from the Byzantine Tradition); the Prayer of the Shrine, the Prayer \foreign{``Lakhu Mara''} known as To You, O Lord, (from the Chaldean Tradition); a Prayer for the Offering of Incense, Prayer to Glorify Mary, the Mother of God (from the Coptic Tradition); Prayer for the Remission of Sins, Prayer for Following in the Footsteps of Christ (from the Ethiopian Tradition); Prayer for the Church, Prayer After the Celebration of the Liturgy (from the Maronite Tradition), and the Intercessions for the Faithful Departed from the Liturgy of St. James (from the Syro-Antiochian Tradition).

\hypertarget{grant24}{\grant{24}{Prayers for Benefactors}}
A partial indulgence is granted to the faithful who, moved by supernatural gratitude, devoutly recite a duly approved prayer for benefactors (e.g., \foreign{Retribuere dignare, Domine}).

\hypertarget{grant26}{\grant{26}{Prayers of Supplication and Acts of Thanksgiving}}
\subgrant{1} A plenary indulgence is granted to the faithful who devoutly assist either at the recitation or solemn singing of

\subsubgrant{1} the \foreign{Veni Creator}, either on the first day of the year to implore divine assistance for the course of the whole year, or on the solemnity of Pentecost;

\subsubgrant{2} the \foreign{Te Deum}, on the final day of the year, to offer thanks to God for gifts received throughout the course of the entire year.

\subgrant{2} A partial indulgence is granted to the faithful who,

\subsubgrant{1} at the beginning and the end of the day,

\subsubgrant{2} in starting and completing their work,

\subsubgrant{3} before and after meals,

devoutly offer some legitimately approved prayer of supplication and act of thanksgiving (e.g., \foreign{Actiones nostras}; \foreign{Adsumus}; \foreign{Agimus Tibi gratias}; \foreign{Benedic, Domine}; \foreign{Domine, Deus Omnipotens}; \foreign{Exaudi nos}; the \foreign{Te Deum}; the \foreign{Veni Creator}; the \foreign{Veni Sancte Spiritus}; \foreign{Visita, quaesumus, Domine}).

\hypertarget{grant28}{\grant{28}{Profession of Faith and Acts of the Theological Virtues}}
\subgrant{2} A partial indulgence is granted to the faithful who

\subsubgrant{1} renew their baptismal vows in any formula;

\subsubgrant{2} devoutly sign themselves with the sign of the cross, using the customary words: ``In the Name of the Father and of the Son and of the Holy Spirit. Amen'';

\subsubgrant{3} devoutly recite either the Apostles' Creed or the Niceno-Constantinopolitan Creed;

\subsubgrant{4} recite an Act of Faith, Hope, and Charity in any legitimate formula.

\hypertarget{grant29}{\grant{29}{For the Faithful Departed}}
\subgrant{1} A plenary indulgence, applicable only to the souls in purgatory, is granted to the faithful who,

\subsubgrant{1} on any and each day from November 1 to 8, devoutly visit a cemetery and pray, if only mentally, for the departed;

\subsubgrant{2} on All Souls' Day (or, according to the judgment of the ordinary, on the Sunday preceding or following it, or on the solemnity of All Saints), devoutly visit a church or an oratory and recite an Our Father and the Creed.

\subgrant{2} A partial indulgence, applicable only to the souls in purgatory, is granted to the faithful who

\subsubgrant{1} devoutly visit a cemetery and at least mentally pray for the dead;

\subsubgrant{2} devoutly recite lauds or vespers from the Office of the Dead or the prayer ``Eternal rest''.

\newpage
\section{Prayer Sources}
% TODO It would be nice to be able to include the label as an argument to this command, but there are problems with underscores.
\newcommand{\urlsource}[1]{:\\{\footnotesize\url{#1}}}

\nameref{prayer:lay_apostle}\urlsource{https://www.ourcatholicprayers.com/prayer-of-a-lay-apostle.html}

\nameref{prayer:Jesus}\urlsource{https://en.wikipedia.org/wiki/Jesus_Prayer}

\nameref{prayer:take_heart_of_stone}\urlsource{http://www.preces-latinae.org/thesaurus/Filius/Aufer.html} (which cites the \foreign{Liturgia Horarum})

\nameref{prayer:grace}\urlsource{https://www.ourcatholicprayers.com/prayers-for-grace-and-guidance.html}

\nameref{prayer:noverim_me}\urlsource{http://www.preces-latinae.org/thesaurus/Filius/NoverimMe.html} (which cites \foreign{Raccolta} \#88 (Apostolic Brief, Sept. 25, 1883; S. P. Ap. Dec. 17, 1932) and \foreign{Manuale Christianum})

\nameref{prayer:resolution}\urlsource{https://www.ourcatholicprayers.com/prayer-of-resolution.html}

\nameref{prayer:pietate_tua}\urlsource{http://www.preces-latinae.org/thesaurus/Trinitas/Pietate.html} (which cites \foreign{Raccolta} \#50, Leo XII, Rescript in his own hand, July 9, 1828; S. P. Ap. Dec. 9, 1932)

\nameref{prayer:new_evangelization} modified slightly from\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-the-new-evangelization.cfm}

\nameref{prayer:profound_disabilities}\urlsource{https://www.ewtn.com/Devotionals/prayers/PrayerForLife.htm}

\nameref{prayer:indifference}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-to-overcome-indifference.cfm}

\nameref{prayer:poor}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-the-poor.cfm} (which cites \textit{Being Neighbor, the Catechism and Social Justice}, Catholic Campaign for Human Development, ©1998 United States Conference of Catholic Bishops)

\nameref{prayer:marginalized} modified from\urlsource{http://www.usccb.org/about/pro-life-activities/prayers/intercessory-prayers-the-marginalized.cfm}

\nameref{prayer:trafficking}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-to-end-trafficking.cfm}

\nameref{prayer:healing_victims_abuse}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-healing-victims-of-abuse.cfm}

\nameref{prayer:charity_truth}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-charity-in-truth.cfm}

\nameref{prayer:gloria}\urlsource{http://www.preces-latinae.org/thesaurus/Trinitas/Gloria.html}

\nameref{prayer:glory_be}\urlsource{http://www.preces-latinae.org/thesaurus/Basics/GloriaPatri.html}

\nameref{prayer:Omnipotentia_Patris}\urlsource{http://www.preces-latinae.org/thesaurus/Trinitas/Omnipotentia.html} (which cites \foreign{Raccolta}, \#53; S. C. Ind. March 15, 1890; S. P. Ap., Sept. 12, 1936.)

\nameref{prayer:adoramus_te}\urlsource{http://www.preces-latinae.org/thesaurus/Filius/Adoramus.html}

\nameref{prayer:sanctus}\urlsource{http://www.preces-latinae.org/thesaurus/Trinitas/Sanctus.html}

\nameref{prayer:short}\urlsource{https://www.ewtn.com/Devotionals/prayers/short.htm}

\nameref{prayer:holy_face}\urlsource{https://www.ewtn.com/Devotionals/prayers/shroud2.htm}

\nameref{prayer:Our_Lady_help_of_Christians}\urlsource{https://www.ewtn.com/Devotionals/prayers/Bosco_prayer.htm}

\nameref{prayer:JPII_Lady_of_Lourdes}\urlsource{https://www.ewtn.com/Devotionals/prayers/Lourdes_2004.htm}

\nameref{prayer:StMichael}\urlsource{https://www.ewtn.com/Devotionals/prayers/index.asp}

\nameref{prayer:help_against_spiritual_enemies}\urlsource{https://www.ewtn.com/Devotionals/prayers/Spiritual_Enemies.htm}

\nameref{prayer:parent}\urlsource{https://www.loyolapress.com/our-catholic-faith/prayer/family-prayers/a-parents-prayer}

\nameref{prayer:safety_children}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-safety.cfm} which cites the book \textit{Catholic Household Blessings and Prayers}.

\nameref{prayer:defense_marriage}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-defense-of-marriage.cfm}

\nameref{prayer:dead}\urlsource{http://www.usccb.org/prayer-and-worship/bereavement-and-funerals/prayers-for-death-and-dying.cfm}

\nameref{prayer:mourners} combined from multiple prayers given at\urlsource{http://www.usccb.org/prayer-and-worship/bereavement-and-funerals/prayers-for-death-and-dying.cfm}

\nameref{prayer:poor_souls_purgatory}\urlsource{https://www.purgatorypeople.com/wp-content/uploads/2017/09/english_poorsoulscard.jpg}

\nameref{prayer:most_neglected_purgatory} combined from two prayers from\urlsource{https://www.purgatorypeople.com/wp-content/uploads/2017/09/english_poorsoulscard.jpg}

\nameref{prayer:purgatory_closest_heaven}\urlsource{https://www.purgatorypeople.com/wp-content/uploads/2017/09/english_poorsoulscard.jpg}

\nameref{prayer:graveside}\urlsource{http://www.usccb.org/prayer-and-worship/bereavement-and-funerals/prayers-for-death-and-dying.cfm}

\nameref{prayer:StEphrem2}\urlsource{https://www.ewtn.com/Devotionals/prayers/Ephrem.htm}

\nameref{prayer:benedict_xvi_unborn}\urlsource{https://www.ewtn.com/Devotionals/prayers/b16_unborn.htm}

\nameref{prayer:litany_for_life}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/litanies/a-litany-for-life.cfm}

\nameref{prayer:litany_of_humility}\urlsource{https://www.ewtn.com/Devotionals/prayers/humility.htm}

\nameref{prayer:blessing_child}\urlsource{https://aleteia.org/2017/01/03/blessing-your-children-its-not-just-for-sneezes/} which cites the book \textit{The Catholic Gentleman}.

\nameref{prayer:blessing_child_birthday}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/child-birthday-blessing.cfm} which cites the book \textit{Catholic Household Blessings and Prayers}.

\nameref{prayer:travel_blessing}\urlsource{https://aleteia.org/2017/01/03/blessing-your-children-its-not-just-for-sneezes/}

\nameref{prayer:babies_about_to_be_born}, \nameref{prayer:parents_before_birth_of_child}, \nameref{prayer:mother_before_childbirth}\urlsource{https://www.ewtn.com/Devotionals/prayers/PrayerForLifeThroughouttheYear.htm}

\nameref{prayer:thanksgiving_newborn}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/thanksgiving-for-a-newborn-or-newly-adopted-young-child.cfm} which cites the book \textit{Catholic Household Blessings and Prayers}.

\nameref{prayer:bringing_child_into_home}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-on-bringing-a-child-into-the-home.cfm}

\nameref{prayer:travelers}\urlsource{https://www.ewtn.com/Devotionals/prayers/travelers.htm}

\nameref{prayer:times_of_trouble}\urlsource{http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayers-for-times-of-trouble.cfm} which cites the book \textit{Catholic Household Blessings and Prayers}.
\end{document}