\prayersection{Pro-Life}
\prayertitle{For Life and Dignity}
\label{prayer:life-dignity}
Eternal God, creator and sustainer of life, bless us with the courage to defend all life from conception to natural death.
Bless us with the strength to respect all peoples from east to west, from north to south,
so that we may truly follow the call of Jesus to be neighbor.
We ask this in the Name of Jesus, Who lives and reigns with You and the Holy Spirit.
Amen.

\prayertitle{To End Abortion}
% http://www.priestsforlife.org/novenas/novena.aspx?id=10
Lord God, I thank You today for the gift of my life, and for the lives of all my brothers and sisters.
I know there is nothing that destroys more life than abortion, yet I rejoice that You have conquered death by the Resurrection of Your Son. 
I am ready to do my part in ending abortion. Today I commit myself 
never to be silent, 
never to be passive, 
never to be forgetful of the unborn. 
I commit myself to be active in the pro-life movement and never to stop defending life until all my brothers and sisters are protected, and our nation once again becomes a nation with liberty and justice not just for some, but for all.
Through Christ our Lord. Amen!

\prayertitle{For Pro-Life Advocates}
% Fr. Frank Pavone, National Director, Priests for Life, http://www.priestsforlife.org/pdf/prayer-for-prolife-advocates.pdf
% Changed "Planned Parenthood" to "the abortion industry"
Father of our Lord Jesus Christ,
You have filled us with Your Holy Spirit Who is our advocate in the heavens, and You have made us advocates for the weakest of all, the unborn.

Your Son has promised us that we will be hated on account of His Name and persecuted for the good that we do.
We ask You today to bless all of us who are advocates for life.
Bless every facet and activity of the pro-life movement, and grant us strength and perseverance in this cause, no matter what the obstacles.

Bless all those who have assisted in the effort to expose the abortion industry, through projects in the past and in the present.

Give them, and all of us who work in this great movement, the protection of Your Providence and the peace and joy that come only from You, and that nobody can take from us.

We pray in the Name of Jesus our Lord. Amen.

\prayertitle{For Public Officials}
% Fr. Frank Pavone, National Director, Priests for Life, http://www.priestsforlife.org/pdf/prayer-for-our-public-officials.pdf
Lord Jesus,
You are the King of Kings and Lord of Lords.
You are the Ruler of the kings of the earth, and the one through Whom and for Whom all things exist.

We pray today for those who serve in public office.
We ask that those who write and pass our laws may keep their eyes fixed on Your Law as their ultimate authority.
We ask that those who execute the laws may be filled with awe in Your Presence, as You govern the universe from end to end mightily.
And we ask that those who judge in human courts may know they are accountable to You, the Judge of all.

Lord, we pray that the tragedy of abortion, and the trade in baby body parts, may awaken the consciences of those in public office, and stir them to action to defend human rights and dignity.

Lord, so many have been asleep, and so many public servants have forgotten the difference between serving the public and killing the public.

Awaken them, enlighten them, and heal them.

And to those whose eyes are already fixed on Your Law of life, give unending courage and perseverance in the task of serving the common good and securing the right to life, which comes only from You and which no government can take away.

We ask this of You, Lord Jesus, Who lives and reigns forever and ever. Amen.

\prayertitle{Redeemer in the Womb}
% http://www.priestsforlife.org/prayers/prayerredeemerinwomb.html
Lord Jesus Christ, You took our human nature upon Yourself.
You shared our life and death, our childhood and adulthood.

You also shared our time in the womb. While still God, while worshiped and adored by the angels, while Almighty and filling every part of the universe, You dwelt for nine months in the womb of Mary.
You were our Redeemer in the womb, our God Who was a preborn child.

Lord Jesus, we ask You to bless and protect the children who today are in their mothers' womb.
Save them from the danger of abortion.
Give their mothers the grace to sacrifice themselves, in body and soul, for their children.
Help all people to recognize in the preborn child a brother, a sister, saved by You, our Redeemer in the womb.

\prayertitle{To the Holy Spirit, the Advocate}
% http://www.priestsforlife.org/prayers/prayerhsadvocate.html
O Holy Spirit of God, You were promised to us by the Lord Jesus as an Advocate, as one Who pleads our cause and speaks up for us in the heights of heaven.
``I will ask the Father, and He will give you another Advocate, to be with you forever...'' (John 14:16).

The apostle Paul has taught us that You intercede for us with groanings that cannot be expressed in speech (Rom. 8:26).

We praise You today for the gift of salvation, for we are deeply aware that we cannot save ourselves.
We have sinned, and we cannot win forgiveness on our own.
We need an Advocate.

We ask You, O Holy Spirit, to make us ever more aware of those who need us as advocates.
Grant that we may hear the cries of our youngest, smallest brothers and sisters, those still in the womb, who cannot speak or defend themselves, and who cannot even pray.

Holy Spirit, as You are the Advocate, so make us advocates.
As You hear our cries for mercy, so let us hear the cries of others for mercy.
Save us from the misfortune of seeking mercy only for ourselves, while being deaf to others.
As You loosened the tongues of the apostles at Pentecost, so grant us today a Pentecost for the unborn, that we may speak for them before the great and the small, before governments and institutions, and before all Your people.
Amen.

\prayertitle{To the Virgin Mary}
O Mary, Mother of Jesus and Mother of us all, we turn to you today as the one who said ``Yes'' to Life.
``You will conceive and bear a Son,'' the angel told you.
Despite the surprise and the uncertainty about how this could be, you said yes.
``Be it done unto me according to your word.''

Mary, we pray today for all mothers who are afraid to be mothers.
We pray for those who feel threatened and overwhelmed by their pregnancy.
Intercede for them, that God may give them the grace to say yes and the courage to go on.
May they have the grace to reject the false solution of abortion.
May they say with you, ``Be it done unto me according to your word.''
May they experience the help of Christian people, and know the peace that comes from doing God's Will.
Amen.

\prayertitle{For Protection of Conscience Rights in Health Care}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/protection-of-conscience-rights-healthcare.cfm
Father, in Jesus our Lord, we praise and thank You for Your most precious gift of human life and for forming us in Your divine Image.
Keep us, the dwelling place of Your most Holy Spirit, ever healthy in body and soul.

Jesus, Divine Healer, pour Your Grace upon all those afflicted with illness or disease.
Protect from all harm those who are vulnerable due to sickness, suffering, frailty, poverty, or age, whether elderly or unborn.

Holy Spirit, touch the hearts of all who serve human life in medicine and science, so they will protect the dignity of each person, from conception to natural death, and remain faithful advocates of all entrusted to their care.  

Grant those who are called to serve as health care providers renewed conviction in their ministry, and increased wisdom to treat the whole person, and not merely the illness.

Protect the right of health care providers to serve their patients without being forced to violate their moral and religious convictions.
Guard them against discrimination, that they might be free to follow You faithfully while fulfilling their professional duties.

Grant our lawmakers the wisdom and courage to uphold conscience rights for those called to the ministry of healing, and help them resist the pressure to become collaborators in the culture of death.

Give us strength to be bold and joyful witnesses to the truth that every human life is sacred.

In Your Goodness, guard our freedom to live out our faith and to follow You in all that we do.

Father, we ask this in Jesus' Name, through the Holy Spirit. Amen.

\prayertitle{Prayer to End the Use of the Death Penalty}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-to-end-the-use-of-the-death-penalty.cfm
Merciful Father, we ask Your blessing in all we do to build a culture of life.
Hear our prayers for those impacted by the death penalty.

We pray for all people, that their lives and dignity as children of a loving God may be respected and protected in all stages and circumstances.

We pray for victims of violence and their families, that they may experience our love and support and find comfort in Your Compassion and in the promise of eternal life.

We pray for those on death row, that their lives may be spared, that the innocent may be freed and that the guilty may come to acknowledge their faults and seek reconciliation with You.

We pray for the families of those who are facing execution, that they may be comforted by Your Love and Compassion.

We pray for civic leaders, that they may commit themselves to respecting every human life and ending the use of the death penalty in our land.

Compassionate Father, give us wisdom and hearts filled with Your Love.
Guide us as we work to end the use of the death penalty and to build a society that truly chooses life in all situations.

We ask this, Father, through Your Son Jesus Christ, Who lives and reigns with the Holy Spirit, one God forever and ever.
Amen.

\prayertitle{For Life}
% http://www.usccb.org/prayer-and-worship/prayers-and-devotions/prayers/prayer-for-life.cfm
Father and maker of all, You adorn all creation with splendor and beauty, and fashion human lives in Your Image and Likeness.
Awaken in every heart reverence for the work of Your Hands, and renew among Your people
a readiness to nurture and sustain Your precious gift of life.

Grant this through our Lord Jesus Christ, Your Son, Who lives and reigns with You in 
the unity of the Holy Spirit, God forever and ever.
Amen.

\prayertitle{Pope Benedict XVI's Prayer For The Unborn}
\label{prayer:benedict_xvi_unborn}
Lord Jesus, 
You Who faithfully visit and fulfill with Your Presence the Church and the history of men;
You Who in the miraculous Sacrament of Your Body and Blood render us participants in divine Life and allow us a foretaste of the joy of eternal Life;
we adore and bless You.

Prostrated before You, source and lover of Life, truly present and alive among us, we beg You:

Reawaken in us respect for every unborn life, make us capable of seeing in the fruit of the maternal womb the miraculous work of the Creator, open our hearts to generously welcoming every child who comes into life.

Bless all families, sanctify the union of spouses, render fruitful their love.

Accompany the choices of legislative assemblies with the light of Your Spirit, so that peoples and nations may recognize and respect the sacred nature of life, of every human life.

Guide the work of scientists and doctors, so that all progress contributes to the integral well-being of the person, and no one endures suppression or injustice.

Give creative charity to administrators and economists, so they may realize and promote sufficient conditions so that young families can serenely embrace the birth of new children.

Console the married couples who suffer because they are unable to have children and in Your goodness provide for them.

Teach us all to care for orphaned or abandoned children, so they may experience the warmth of Your Charity, the consolation of Your divine Heart.

Together with Mary, Your Mother, the great believer, in whose womb You took on our human nature, we wait to receive from You, our Only True Good and Savior, the strength to love and serve life, in anticipation of living forever in You, in communion with the Blessed Trinity.

\newpage