\prayersection{Sacrament of Reconciliation}
\prayertitle{Preparation for the Sacrament of Reconciliation}
% My Prayer Book, p. 93
Holy Spirit,
You came down upon the Apostles to enlighten their minds and strengthen their ministry.
Come down upon me at this important moment.
Help me to see my life in the light of Jesus Christ.
Renew my love as I am reconciled to God and His people.

\prayertitle{Prayer to the Holy Spirit before Confession}
% https://www.ourcatholicprayers.com/prayers-before-confession.html
O Holy Spirit, Source of all light, Spirit of wisdom, of understanding, and of knowledge, come to my assistance and enable me to make a good confession.
Enlighten me, and help me now to know my sins as one day I shall be forced to recognize them before Your judgment seat.
Bring to my mind the evil which I have done and the good which I have neglected.
Permit me not to be blinded by self-love.
Grant me, moreover, heartfelt sorrow for my transgressions, and the grace of a sincere confession, so that I may be forgiven and admitted into Your Friendship.

\prayertitle{Prayer Before Confession for Heavenly Aid}
% https://www.ourcatholicprayers.com/prayer-for-heavenly-aid.html
Father in heaven, most merciful God, relying on Your Goodness and Mercy, I come to You with childlike confidence to confess my sins and to beg Your Forgiveness.
You will not reject a contrite and humble heart.
Bless me and receive me again into Your Favor.
I realize that I have been most ungrateful to You, but I desire henceforth to keep Your commandments and to do Your Will in all things.

Jesus my Savior, my Good Shepherd, I did not follow in Your footsteps but have strayed far from the path that You have marked out for me.
Repentant and sorrowful, I beg to be admitted again into the fold of Your faithful followers.
I want to confess my sins with the same sincerity as I should wish to confess at the moment of my death.
My Jesus, I beg You for the grace to examine my conscience well.

Holy Spirit, come into my soul.
Enlighten my mind and strengthen my will that I may know my sins, humbly confess them, and sincerely amend my life.

Mary, my Mother, Immaculate Spouse of the Holy Spirit, refuge of sinners, help me by your kind prayers. Amen.

% Is this indulgenced? See Confiteor below.
\prayertitle{Act of Contrition}
% My Prayer Book, p. 30
My God,
I am sorry for my sins with all my heart.
In choosing to do wrong and failing to do good, I have sinned against You Whom I should love above all things.
I firmly intend, with Your help, to do penance, to sin no more, and to avoid whatever leads me to sin.
Our Savior Jesus Christ suffered and died for us.
In His Name, my God, have mercy.

\indulgencedprayertitle{The Confiteor}
\linkednote{grant9}{A partial indulgence is granted for devoutly reciting this prayer, especially in preparation for sacramental confession.}
I confess to almighty God and to you, my brothers and sisters, that I have greatly sinned, in my thoughts and in my words, in what I have done and in what I have failed to do, through my fault, through my fault, through my most grievous fault;
therefore I ask blessed Mary, ever Virgin, all the angels and saints, and you, my brothers and sisters, to pray for me to the Lord our God.

\prayertitle{Prayer After Confession to Strengthen Resolutions}
% https://www.ourcatholicprayers.com/prayer-for-resolutions-after-confession.html
Almighty and most merciful God, because of Your great Mercy You have been pleased to admit me once more to this Sacrament of forgiveness.
You have received me, though I have often gone astray from You.
I was an outcast, but You welcomed me back as a friend.
I thank You with all my heart for Your infinite Mercy and Kindness towards me, an ungrateful sinner.
In union with the Blessed Virgin Mary, the Refuge of sinners, I thank You for all the graces and blessings You have bestowed upon me in this Sacrament of Penance.

My dear God, I now renew the promises I have made in Baptism, and I give myself eternally to Your Love and service.
Give me the grace in the future to hate sin more than death itself and to avoid all such occasions and company as have in the past unhappily brought me to it.
Help me, O Lord, for I am weak.
Strengthen my resolutions and give me sufficient grace to overcome the evil promptings of my nature.
Never permit me to wound You again by my sins.
Refresh my soul that I may become strong in my determination to perform the duties of my state of life properly and fearlessly.
Through Your divine Grace, without which I can do nothing, help me to live a good life, die a happy death, save my immortal soul, and be happy with You for all eternity in heaven. Amen.

\prayertitle{Thanksgiving After Confession}
I return unto You, O Lord Jesus, and give You thanks that You have been pleased to cleanse me from the foul leprosy of my sins.
Blessed be Your Name, O Lord, forever and ever.
Truly You are a Savior Who rejects none that come unto You seriously desiring to repent, but receives them into Your favor, and numbers them with Your children.
I acknowledge and adore Your Mercy, and dedicate myself wholly to Your service hereafter.
Assist my weakness and suffer me not again to fall into my past sins and to be separated from You;
but so bind my heart and soul to You with the cords of Your Love, that I may say with the Apostle ``Who shall separate me from the Love of Christ?''

\prayertitle{Prayer After Confession by St. Frances Xavier Cabrini}
My dearest Jesus, I have told all my sins as well as I could.
I tried hard to make a good confession.
I feel sure that You have forgiven me.
I thank You.
It is only because of all Your sufferings that I can go to confession and free myself from my sins.
Your Heart is full of love and mercy for poor sinners.
I love You because You are so good to me.
My loving Savior, I shall try to keep from sin and to love You more each day.
My dear Mother Mary, pray for me and help me to keep my promises.
Protect me and do not let me fall back into sin.
Almighty God, kneeling before Your Divine Majesty, I adore You and because You command me, I dare approach Your divine Heart.
But what shall I say if You do not enlighten me with a ray of Your divine Light?

Speak to my soul, O Lord, and command me to listen to Your Voice.
Enlighten my will to put Your words into practice.
Pour Your Grace into my heart;
lift up my soul weighed down by my sins;
raise my mind to heavenly things, so that earthly desires may no longer appeal to me.
Speak to my soul with Your divine Omnipotence, for You are my salvation, my life, and my peace, in time and in eternity.
Strengthen me with the Grace of Your Holy Spirit and give Your Peace to my soul that I may be free from all needless worry and care.
Help me to desire always that which is pleasing and acceptable to You so that Your Will may be my will.
Grant that I may rid myself of all unholy desires, and that for Your Love I may remain unknown in this world, and be known only to You.

Do not permit me to attribute to myself the good that You perform in me and through me, but rather, referring all honor to Your Majesty, may I glory only in my weakness, so that renouncing sincerely all vain glory which comes from the world, I may aspire to the true and lasting glory which comes from You. Amen.

\newpage