\prayersection{Prayers for Seasons of the Liturgical Year}
\prayertitle{Advent}
Father of our Lord Jesus Christ, ever faithful to Your promises and ever close to Your Church: the earth rejoices in hope of the Savior's coming and looks forward with longing to His return at the end of time.
Prepare my heart during this Advent Season.
Increase my longing for Christ my Savior and give me the strength to grow in love.

Jesus, my Lord, save me from my sins.
Come, protect me from all dangers and lead me to salvation.

Sanctify me in mind and body, Lord, keep me without sin until the coming of Your Son.
Make me walk these days in holiness, Lord, and live an upright and devout life in this world.
Prepare a path in my heart for the coming of Your Word and let His Glory be revealed through my good works.

Bring low the mountains of my pride, Lord, and fill up the valleys of my weakness.

Keep me in the Love of Your Spirit, Lord, that I may receive the Mercy of Your Son Who is to come.

I long for the grace of Your coming, Lord, console me with the gift of Your own divine Life.

\prayertitle{Christmas}
God of love, the darkness that covered the earth has given way to the bright dawn of Your Word made flesh.
Help me to walk in this light.
May I be faithful to Your Word and bring Your Life to the waiting world.

At this time of Your holy birth, Lord Jesus, I pray that my life may give glory to You.
Since Your birth was here on earth, I hope You will someday give me my own birth in heaven.

You saved me by Your birth, Lord Jesus, help me to be faithful to the promises of my baptism.

Increase the hope of the weak, the poor, and the aged, give relief to the oppressed and consolation to those who mourn.

You are the Prince of Peace, Lord Jesus, grant the world that peace which the angels proclaimed.

Give me a heart that is upright and sincere so that I may listen to Your Word.

You shine on those who dwell in darkness, give me holiness, justice, and peace.

You became our brother by being born of the Virgin Mary, teach me to love all as my brothers and sisters.

\prayertitle{Lent}
Heavenly Father, I am called to walk by the Light of Christ, Your Son, and to trust in His Wisdom.
During Lent, I submit my self to Him more and more and am striving to believe in Him with all my heart.
I enter on this path of repentance so that in dying to self I might rise to new life.

Lord Jesus, You spoke peace to a sinful world and brought mankind the gift of reconciliation by the suffering and death You endured.
I love You and joyfully bear the name `Christian'.
Teach me to follow Your example.
Increase my faith, hope, and charity so that I may struggle to turn hatred to love and conflict to peace.

Loving Redeemer, through Your Passion teach me self-denial, strengthen me against evil and adversity and so make me ready to celebrate Your Resurrection.

Healer of body and soul, cure the sickness in my spirit so that I may grow in holiness through Your constant care.

Forgive my sins against the unity of Your family, make me love as You loved me.

Good Master, make me mindful of the dignity You gave me in Baptism, may I live for You at every moment.

Give me a perfect heart to receive Your work, that I may bring forth fruit in patience.

Renew my eagerness to work with You in building a better world, so that my friends may hear Your gospel of peace and justice.

\prayertitle{Orthodox Lenten Prayer}
% https://orthodoxprayer.org/OtherPrayers.html#lenten
Almighty Master, who created all things in wisdom, by Your Providence and great Goodness, You have led us to this lenten season for purification of our souls and bodies, and for control of our passions in the hope of the resurrection;
You, Who after forty days gave Moses the tablets of the law inscribed by Your divine Hand, grant to us the strength to fight the good fight, to fast, to keep the faith, to crush under foot all evil demons, and to become victorious over sin and to celebrate Your holy Resurrection.
For blessed and glorified is Your most honored and majestic Name of the Father and the Son and the Holy Spirit, both now and forever and to the ages of ages.
Amen.

\prayertitle{Lenten Prayer for Life}
% Bishop James D. Conley, Auxiliary Bishop of Denver http://www.priestsforlife.org/prayers/bishop-conley-lenten-prayer.htm
Almighty Father and Lord of Life,
You have entrusted to men the noble mission of safeguarding and protecting human life with the utmost care from the moment of conception to natural death (\textit{Gaudium et Spes}, No. 51).

During this holy season of Lent, a time of both penance and great hope, stir in our hearts a greater love for You and for each other.
During these 40 days of spiritual renewal, lead us to a deeper conversion so that by living in Your Light and Love we may bear witness to the gift of life.

Lord Jesus, the firstborn of all creation, have mercy on us. 
Accept our prayers and our fasting in atonement for the tragic sin of abortion. 
By the merits of Your precious Blood, shed for our redemption, instill in all hearts a profound respect for the gift of life and bring about an end to abortion, euthanasia, and every other assault on innocent human life.

Reawaken in the heart of every pregnant mother a profound love for the life growing in her womb and grant to her unfailing courage to choose life for her child.

Come Holy Spirit, strengthen us and give us fortitude to work tirelessly to promote a true Culture of Life, a culture that recognizes the dignity and sanctity of every person.
Raise up men and women to serve in public office who will enact laws which will safeguard and protect all human life.

Blessed Mary, Mother of God, you bore the Author of Life in your womb. 
Through your intercession may our hearts be conformed to yours so that we might accept, nurture, and cherish all human life.

Sacred Heart of Jesus, have mercy on us. Amen.

\prayertitle{Easter}
Heavenly Father and God of Mercy, I believe that Jesus is alive and has become the Lord of life.
From the waters of Baptism You have raised me with Him and renewed Your gift of life within me.
Increase in my mind and heart the risen life I share with Christ and help me to grow in Your Wisdom and Grace.

Lord Jesus, You appeared to Your apostles after the resurrection and filled their hearts with joy when You said to them, ``Peace be with you''.
May the peace of Your Presence abide with me and make each day You give me the most beautiful day of my life.

Lord Jesus, You triumphed over death and destroyed the power of death in me, may I live only for You.

Risen Lord, You brought confusion on the guards at Your tomb but joy to Your disciples, grant me the fullness of joy as I serve You in spirit and truth.

You promised to be with Your disciples, Lord, to the end of the world, stay with me today and remain with me always.

King of glory, center of my life, grant that when You come again, I may be one with You in glory.

Lord, remember me as in my own way I minister to Your people, may my life be holy and an example to Your people.

Lord Jesus, purify my heart with Your Truth and guide me in the way of holiness, so that I may always do what is pleasing in Your Sight.

\prayertitle{Pentecost}
Father of Light, from Whom every good gift comes, send Your Spirit into my life with the power of a mighty wind.
May He recall to my memory the words of Jesus and keep them in my heart.

Jesus, Your Spirit renews the face of the earth and fills the whole universe.
May it renew the depth of my heart so that You may always find in my heart and on my lips a prayer pleasing to You.

Lord Jesus, when You were raised high upon the cross, streams of living water flowed from Your pierced Side, pour out on me Your life-giving Spirit.

You promised to send the Holy Spirit to bear witness to Yourself, renew Your Spirit within me to make me Your faithful witness.

You desire the whole world to be filled with Your Spirit, help me to build a world of justice and peace.

You desire the unity of all Christians through one baptism in the Spirit, make all who believe one in heart and soul.

Lord Jesus, You gave Your Spirit to the apostles with the power to forgive sins, destroy all sin in the world.

You promised the Holy Spirit to teach and remind Your followers of all You have said, send me that Spirit to enlighten my mind in faith.

\newpage