\prayersection{Prayers for Particular Times of the Day}
\indulgencedprayertitle{Morning Prayer (includes \foreign{Actiones nostras})}
% Combined from each of the morning prayers in My Prayer Book (p. 32)
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as \foreign{Actiones nostras} at the beginning and end of the day.}
Father, may all we do today be inspired by You and continue with Your saving help.
By Your guidance may we not fail today, but grant that all our thoughts, words, and activity may be in accord with Your Will.
Cast our darkness from our hearts and send us the light of Your Truth, so that we may be guided by You today and walk in Your Love.
Let our work always begin with Your blessing and through You reach completion.
We ask this through Christ our Lord.
Amen.

\indulgencedprayertitle{\foreign{Domine, Deus omnipotens}}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of supplication such as this one at the beginning and end of the day.}
Lord, God Almighty, You have brought us safely to the beginning of this day.
Defend us today by Your mighty Power, that we may not fall into any sin, but that all our words may so proceed and all our thoughts and actions be so directed, as to be always just in Your Sight.
Through Christ our Lord.
Amen.

\indulgencedprayertitle{Grace Before Meals (\foreign{Benedic, Domine})}
\label{prayer:grace_before_meals}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of thanksgiving such as this one before and after meals.}
Bless us, O Lord, and these Your gifts which we are about to receive from Your bounty, through Christ Our Lord.
Amen.

\indulgencedprayertitle{Grace After Meals (\foreign{Agimus tibi gratias})}
\label{prayer:grace_after_meals}
\linkednote{grant26}{A partial indulgence is granted for devoutly offering a prayer of thanksgiving such as this one before and after meals.}
We give You thanks, Almighty God, for these and all Your blessings;
You live and reign for ever and ever.
Amen.

\newpage

\prayertitle{Prayer Before Starting a Task}
% Combined from multiple prayers from https://orthodoxprayer.org/OtherPrayers.html#task
Lord Jesus Christ, my God, You have said, ``Apart from me You can do nothing.''
In faith I embrace Your words, Lord, and I entreat Your Goodness.
Help me to carry out the work I am about to begin and to bring it to completion.
Direct me by Your Wisdom and Power, that I may accomplish this task and whatever I do according to Your divine Will, so that it may be beneficial to me and others and to the Glory of Your Holy Name.
To You I give glory, Father, Son, and Holy Spirit.
Amen.

\indulgencedprayertitle{Evening Prayer from the Byzantine Tradition}
\linkednote{grant23}{A partial indulgence is granted for devoutly reciting this prayer from the Byzantine Tradition.}
In the evening, in the morning, and at noon, we praise You, we bless You,
we give You thanks, and we beg You, Master of the universe, grant that our hearts not yield to evil words but free us from all who try to enslave our souls, because our eyes are turned to You, O Lord, and we have placed our hope in You.
Do not abandon us, O God!
For every glory, honor, and adoration is due to You, Father, Son, and Holy Spirit, now and always and for ever and ever.
Amen.

\prayertitle{Evening Prayer}
Almighty God, we thank You for bringing us safely to the end of this day.
We offer You the work of our hands as a sacrifice before Your Sight.
We make this prayer through Christ our Lord.
Amen.

\prayertitle{Prayer of a Lay Apostle}
\label{prayer:lay_apostle}
Thank You, my God, for the day that is ending, thank You for the coming night.
Bring sleep to the weary, bring repose to those I love, and give me rest until tomorrow.

All was not fine, perfect, and beautiful today.
Give me strength to do better tomorrow.

In this day that is ending I have not been what I should have been.
Make me better, my God, less harsh towards others, more gentle, more patient.
Make me, too, more determined, more demanding of myself, more truthful in speaking, more faithful in my promises, more active in my work, more obedient and more submissive;
let me be cheerful, too, and may tomorrow be a finer, fuller day than this.

Thank You, my God, for the day that is ending, thank You for the coming night.
Bring sleep to the weary, bring repose to those I love, and give me rest until tomorrow.

\newpage