\prayersection{Prayers to the Saints}
\indulgencedprayertitle{\foreign{Maria, Mater gratiae}}
\linkednote{grant17}{A partial indulgence is granted for devoutly addressing the Blessed Virgin Mary with this prayer.}
Mary, Mother of Grace and Mother of Mercy, shield me from the enemy and receive me at the hour of my death.

\prayertitle{Hail Mary}
% My Prayer Book, p. 25
Hail Mary, full of grace, the Lord is with you.
Blessed are you among women, and blessed is the fruit of your womb, Jesus.
Holy Mary, Mother of God, pray for us sinners, now and at the hour of our death.
Amen.

\prayertitle{Memorare}
% https://www.loyolapress.com/our-catholic-faith/prayer/traditional-catholic-prayers/prayers-honoring-mary/memorare-marian-prayer
Remember, most loving Virgin Mary, never was it heard that anyone who turned to you for help
was left unaided.
Inspired by this confidence, though burdened by my sins, I run to your protection, for you are my mother.
Mother of the Word of God, do not despise my words of pleading but be merciful and hear my prayer.
Amen.

\prayertitle{Hail, Holy Queen}
% https://www.loyolapress.com/our-catholic-faith/prayer/traditional-catholic-prayers/prayers-honoring-mary/hail-holy-queen-prayer
Hail, holy Queen, Mother of mercy, hail, our life, our sweetness, and our hope.
To you we cry, the children of Eve;
to you we send up our sighs, mourning and weeping in this land of exile.
Turn, then, most gracious advocate, your eyes of mercy toward us;
lead us home at last and show us the blessed fruit of your womb, Jesus:
O clement, O loving, O sweet Virgin Mary.
\newpage
\prayertitle{To Our Lady, Help Of Christians}
\label{prayer:Our_Lady_help_of_Christians}
%\note{By St. John Bosco}
Most Holy Virgin Mary, Help of Christians, how sweet it is to come to your feet
imploring your perpetual help.
If earthly mothers cease not to remember their children, how can you, the most loving of all mothers, forget me?
Grant then to me, I implore you, your perpetual help in all my necessities, in every sorrow, and especially in all my temptations.
I ask for your unceasing help for all who are now suffering.
Help the weak, cure the sick, convert sinners.
Grant through your intercessions many vocations to the religious life.
Obtain for us, O Mary, Help of Christians, that having invoked you on earth we may love and eternally thank you in heaven.

\prayertitle{Pope St. John Paul II's Prayer to Our Lady of Lourdes}
\label{prayer:JPII_Lady_of_Lourdes}
Hail Mary, poor and humble woman, blessed by the Most High!
Virgin of hope, dawn of a new era, we join in your song of praise, to celebrate the Lord's Mercy, to proclaim the coming of the Kingdom and the full liberation of humanity.

Hail Mary, lowly handmaid of the Lord, Glorious Mother of Christ!
Faithful Virgin, holy dwelling-place of the Word, teach us to persevere in listening to the Word, and to be docile to the Voice of the Spirit, attentive to His promptings in the depths of our conscience and to His manifestations in the events of history.

Hail Mary, Woman of sorrows, Mother of the living!
Virgin spouse beneath the Cross, the new Eve, be our guide along the paths of the world.
Teach us to experience and to spread the Love of Christ, to stand with you before the innumerable crosses on which your Son is still crucified.

Hail Mary, woman of faith, first of the disciples!
Virgin Mother of the Church, help us always to account for the hope that is in us, with trust in human goodness and the Father's Love.
Teach us to build up the world beginning from within:
in the depths of silence and prayer, in the joy of fraternal love, in the unique fruitfulness of the Cross.

Holy Mary, Mother of believers, Our Lady of Lourdes, pray for us.

\indulgencedprayertitle{\foreign{Sancti Apostoli Petre et Paule}}
\linkednote{grant20}{A partial indulgence is granted for devoutly reciting this prayer.}
Holy Apostles Peter and Paul, intercede for us.
Guard Your people, who rely on the patronage of Your apostles Peter and Paul, O Lord, and keep them under Your continual protection.
Through Christ our Lord. Amen.

\indulgencedprayertitle{\foreign{Ad te, beate Ioseph}}
\linkednote{grant19}{A partial indulgence is granted for invoking St. Joseph with this prayer.}
To you, O blessed Joseph, do we come in our tribulation, and having implored the help of your most holy spouse, we confidently invoke your patronage also.
Through that charity which bound you to the Immaculate Virgin Mother of God and through the paternal love with which you embraced the Child Jesus, we humbly beg you graciously to regard the inheritance which Jesus Christ has purchased by His Blood, and with your power and strength to aid us in our necessities.
O most watchful Guardian of the Holy Family, defend the chosen children of Jesus Christ;
O most loving father, ward off from us every contagion of error and corrupting influence;
O our most mighty protector, be kind to us and from heaven assist us in our struggle with the power of darkness.
As once you rescued the Child Jesus from deadly peril, so now protect God's Holy Church from the snares of the enemy and from all adversity;
shield, too, each one of us by your constant protection, so that, supported by your example and your aid, we may be able to live piously, to die in holiness, and to obtain eternal happiness in heaven.
Amen.

\prayertitle{Prayer to St. Michael the Archangel}
\label{prayer:StMichael}
Saint Michael the Archangel, defend us in battle, be our protection against the wickedness and snares of the devil;
may God rebuke him, we humbly pray;
and do you, O Prince of the heavenly host, by the Power of God, cast into hell Satan and all the evil spirits who prowl through the world seeking the ruin of souls.
Amen.
\newpage
\prayertitle{For Help Against Spiritual Enemies}
\label{prayer:help_against_spiritual_enemies}
Glorious Saint Michael, Prince of the heavenly hosts, who stands always ready to give assistance to the people of God;
who fought with the dragon, the old serpent, and cast him out of heaven, and now valiantly defends the Church of God that the gates of hell may never prevail against her, I earnestly entreat you to assist me also, in the painful and dangerous conflict which I sustain against the same formidable foe.

Be with me, O mighty Prince!
that I may courageously fight and vanquish that proud spirit, whom you, by the Divine Power, gloriously overthrew, and whom our powerful King, Jesus Christ, has, in our nature, completely overcome;
so having triumphed over the enemy of my salvation, I may with you and the holy angels, praise the Clemency of God Who, having refused mercy to the rebellious angels after their fall, has granted repentance and forgiveness to fallen man. Amen.

\newpage