\prayersection{For Travel}
\prayertitle{Prayer Before Travel}
% https://orthodoxprayer.org/OtherPrayers.html#travel
Lord Jesus, You traveled with the two disciples after the resurrection and set their hearts on fire with Your Grace.
Travel also with me and gladden my heart with Your Presence.
I know, Lord, that I am a pilgrim on this earth, seeking the citizenship which is in heaven.
During my journey surround me with Your holy angels and keep me safe from seen and unseen dangers.
Grant that I may carry out my plans and fulfill my expectations according to Your Will.
Help me to see the beauty of creation and to comprehend the wonder of Your Truth in all things.
For You are the Way, the Truth, and the Life, and to You I give thanks, praise, and glory forever.
Amen.

\prayertitle{For Travelers}
\label{prayer:travelers}
O Almighty and merciful God, Who has commissioned Your angels to guide and protect us, command them to be our assiduous companions from our setting out until our return;
to clothe us with their invisible protection;
to keep from us all danger of collision, of fire, of explosion, of fall and bruises, and finally, having preserved us from all evil, and especially from sin, to guide us to our heavenly home.
Through Jesus Christ, our Lord. Amen.

\prayertitle{For a Safe Flight}
Dear God, please watch over me as I fly out today.
May Your Hand be on the pilot and crew, Your Strength be in the engineers that prepare the plane, and Your Wisdom over the control teams on the ground.

I choose to trust in You, and give You my fears and anxieties.
May I find peace as I travel.
Take my heart on a journey of trust and hope as I look out over the beautiful world You have made.

I travel with You.
Calm me and cover me,
Amen.